### 2022-05-06 All_EDA.Rmd
Thesis Code Backup

---
output:
  html_document:
    theme: flatly
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    df_print: paged
    code_folding: show
---

```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(AER)

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8)

```

```{r}
## Laptop Data

files <- dir()

files <- files[str_detect(dir(), "all_laptop_reviews.+")]

laptop_data <- map_dfr(files, read_csv)

laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  )) %>% 
  mutate(Product_Type = "Laptop")

laptop_data <- laptop_data %>%
  mutate(Total_Vote = Helpful + Unhelpful) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Helpfulness = Helpful / Total_Vote) %>% 
  mutate(is_Exp = 0)
```

```{r}
movies_data <- read_csv("homecoming15-02-22.csv") %>% 
  mutate(Movie = "Homecoming") %>% 
  bind_rows(read_csv("far_from_home15-02-22.csv") %>% 
              mutate(Movie = "Far From Home")) %>% 
  bind_rows(read_csv("no_way_home19-02-22.csv") %>% 
              mutate(Movie = "No Way Home"))
```

```{r}
movies_data <- movies_data %>% 
  filter(!is.na(Rating))

movies_data <- movies_data %>% 
  separate(Rating, into = c("Rating", "Total"), sep = "/", ) %>% 
  select(-Total) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Rating = as.double(Rating)) %>% 
  mutate(Helpfulness = Helpful_Vote / Total_Vote) %>% 
  mutate(Rating = Rating/2) %>% 
  mutate(is_Exp = 1)

# In this case I am removing every duplicated review.

movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)
```

```{r}
laptop_data %>% names
```

```{r}
movies_data %>% names
```

```{r}
all_data <- laptop_data %>% 
  rename(Helpful_Vote = Helpful) %>% 
  select(-Unhelpful, -Product_Name, -Page) %>% 
  bind_rows(movies_data %>% select(-Movie))
```

```{r}
all_data <- all_data %>% 
  mutate(Doc_ID = row_number())
```

```{r}
all_data <- all_data %>% 
  mutate(Review = str_to_lower(Review, locale = "en"))
```

```{r}
words_agg <- all_data %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  anti_join(stop_words) %>% 
  count(Doc_ID)
```

```{r}
all_data <- words_agg %>% 
  inner_join(all_data, by = "Doc_ID") 
```

```{r}
summary(lm(Helpfulness ~ Rating*is_Exp + I(Rating^2)*is_Exp + log10(n)*is_Exp + log10(Total_Vote), data = all_data))
```

```{r}
summary(tobit(Helpfulness ~ Rating*is_Exp + I(Rating^2)*is_Exp + log10(n)*is_Exp + log10(Total_Vote), data = all_data, left = 0, right = 1))
```

```{r}
all_data %>% 
  ggplot(aes(n, Helpfulness))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~is_Exp)
```

### 2022-05-06 Laptop_EDA.Rmd
Thesis Code Backup

---
output:
  html_document:
    theme: flatly
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    df_print: paged
    code_folding: show
---

```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(AER)
library(lubridate)

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8)

```

```{r}
files <- dir()

files <- files[str_detect(dir(), "all_laptop_reviews.+")]
```

```{r}
laptop_data <- map_dfr(files, read_csv)
```

```{r}

# Filtering out missed duplicated products

laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  ))
```

```{r}
laptop_data_filtered <- laptop_data %>%
  mutate(Total_Vote = Helpful + Unhelpful) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Helpfulness = Helpful / Total_Vote)

laptop_data_filtered <- laptop_data_filtered %>% 
  mutate(Rev_dup = duplicated(Review)) %>% 
  filter(Rev_dup == 0)
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white")
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(Rating))+
  geom_bar()
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point()+
  geom_smooth(method = "loess")
```

```{r}
laptop_data_filtered <- laptop_data_filtered %>% 
  mutate(Doc_ID = row_number())
```

```{r}
laptop_data_filtered <- laptop_data_filtered %>% 
  mutate(Review = str_to_lower(Review, locale = "en"))
```

```{r}
words_agg <- laptop_data_filtered %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  anti_join(stop_words) %>% 
  count(Doc_ID)
```

```{r}
laptop_data_filtered <- words_agg %>% 
  inner_join(laptop_data_filtered, by = "Doc_ID") 
```

```{r}
laptop_data_filtered <- laptop_data_filtered %>% 
  mutate(Date = as_date(mdy_hm(Date, locale = "english"))) 
```

```{r}
first_dates <- laptop_data_filtered %>% 
  group_by(Product_Name) %>% 
  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
  select(Product_Name, Date) %>% 
  rename(First_Date = Date)
```

```{r}
laptop_data_filtered <- full_join(laptop_data_filtered, first_dates, by = "Product_Name") %>% 
  mutate(Timeline = as.integer(Date - First_Date))
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(Timeline))+
  geom_histogram()

laptop_data_filtered %>% 
  ggplot(aes(Timeline, Helpfulness))+
  geom_point()+
  geom_smooth(method = "lm")
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(n))+
  geom_histogram(color = "white")+
  scale_x_log10()
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(n, Helpfulness))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~Product_Name)+
  scale_x_continuous(n.breaks = 10)+
  coord_cartesian(ylim = c(0,1))
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(n, Rating))+
  geom_point()+
  geom_smooth()
```

```{r}
sent_scores <- laptop_data_filtered %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  inner_join(get_sentiments("afinn")) %>% 
  group_by(Doc_ID) %>% 
  summarise(Total_Sent = sum(value))
```

```{r}
laptop_data_filtered %>% 
  inner_join(sent_scores, by = "Doc_ID") %>% 
  ggplot(aes(Total_Sent, Helpfulness))+
  geom_point()+
  geom_smooth()
```

```{r}
laptop_data_filtered %>% 
  inner_join(sent_scores, by = "Doc_ID") %>% 
  ggplot(aes(Total_Sent, Rating))+
  geom_point()+
  geom_smooth()
```

```{r}
laptop_sents <- laptop_data_filtered %>% 
  inner_join(sent_scores, by = "Doc_ID")
```

```{r}
laptop_sents %>% 
  ggplot(aes(Total_Sent))+
  geom_histogram()
```

```{r}
laptop_data_filtered %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white")+
  scale_x_log10(breaks = scales::log_breaks(12))
```

```{r}
summary(lm(Helpfulness ~ Rating + I(Rating^2) + log10(n) + log10(Total_Vote) + Timeline,
           data = laptop_data_filtered))
```

```{r}
lm(Helpfulness ~ Rating + I(Rating^2) + log10(n) + log10(Total_Vote) + Timeline, data = laptop_data_filtered) %>% 
  autoplot(which = 1:6)
```

```{r}
laptop_data_filtered
```

```{r}
summary(tobit(Helpfulness ~ Rating + I(Rating^2) + log10(n)  + log10(Total_Vote) + Timeline,
              data = laptop_data_filtered,
              left = 0, right = 1))
```

```{r}
laptop_data_filtered %>% 
  mutate(n = log10(n)) %>% 
  select(Helpfulness, Rating, Total_Vote, n,Timeline) %>% 
  GGally::ggpairs()
```

```{r}
model <- tobit(Helpfulness ~ Rating + I(Rating^2) + log10(n) + log10(Total_Vote), data = laptop_data_filtered, left = 0, right = 1)
model2 <- tobit(Helpfulness ~ Rating + I(Rating^2) + I(Rating^3) + log10(n) + log10(Total_Vote), data = laptop_data_filtered, left = 0, right = 1)

summary(model)
summary(model2)

anova(model2)
```

```{r}
summary(model)

preds <-  predict(model2, newdata = tibble(Rating = seq(0.5, 5, 0.5),
                                    n = rep(100,10),
                                    Total_Vote = rep(50,10)))

qplot(x = seq(0.5, 5, 0.5), preds)
```

### 2022-05-06 Movies_EDA.Rmd
Thesis Code Backup

---
output:
  html_document:
    theme: flatly
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    df_print: paged
    code_folding: show
---

```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(AER)
library(ggfortify)
library(lubridate)
library(koRpus.lang.en)

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8)

```

```{r}
files <- dir()

files <- files[str_detect(files, "movie_.+")]

#movies_data <- movies_data %>% 
#  bind_rows(map_dfr(files, read_csv))

movies_data <- map_dfr(files, read_csv, show_col_types = FALSE)
```

```{r}
movies_data <- movies_data %>% 
  filter(!is.na(Rating))

movies_data <- movies_data %>% 
  #filter(Movie != "Midsommar") %>% 
  separate(Rating, into = c("Rating", "Total"), sep = "/", ) %>% 
  select(-Total) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Rating = as.double(Rating)) %>% 
  mutate(Helpfulness = Helpful_Vote / Total_Vote) %>% 
  mutate(Rating = Rating/2)
```

```{r}
## Removing All the Duplicated Reviews including the original
movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)
```

```{r}
## Word Count

movies_data <- movies_data %>% 
  mutate(Doc_ID = row_number())
## Words
movies_agg <- movies_data %>% 
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  #anti_join(stop_words) %>% 
  count(Doc_ID, name = "Word_Count")

movies_data <- movies_data %>% 
  inner_join(movies_agg, by = "Doc_ID")

## Sentences

movies_sentence_agg <- movies_data %>% 
  unnest_tokens(output = Sentence, input = Review, to_lower = FALSE, token = "sentences") %>% 
  count(Doc_ID,name = "n_Sentence")

movies_data <- movies_data %>% 
  inner_join(movies_sentence_agg, by = "Doc_ID")

## Emotion Sentiments (EmoLex)

sentiments_agg <- movies_data %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  inner_join(get_sentiments("nrc") %>% filter(word != "spider")) %>% 
  count(Doc_ID, sentiment, name = "Sent_Count") %>% 
  pivot_wider(names_from = sentiment, values_from = Sent_Count, values_fill = 0)

movies_data <- movies_data %>% 
  full_join(sentiments_agg, by = "Doc_ID")

variables <- names(sentiments_agg)[-1]

movies_data <- movies_data %>% 
  mutate(across(.cols = all_of(variables), .fns = ~ifelse(is.na(.), 0, .) ))

movies_data <- movies_data %>% 
  mutate(across(.cols = all_of(variables), .fns = function(.) ./Word_Count*100))

movies_data <- movies_data %>% 
  mutate(across(.cols = variables, .fns = function(.) log10(. + 1)))

```

```{r}
# 
# review_vec <-  movies_data %>%
#   pull(Review)
# 
# 
# SMOG_grade <- vector(mode = "double")
# SMOG_age <- vector(mode = "double")
# Flesch_raw <- vector(mode = "double")
# ARI_grade <- vector(mode = "double")
# 
# ## ARI Index
# # for (i in seq_len(length(review_vec))) {
# #   ARI_Index <- readability(tokenize(review_vec[i], lang = "en", format = "obj"),index = "ARI", quiet = TRUE)
# #
# #   ARI_grade <- append(ARI_grade, summary(ARI_Index) %>% pull(grade))
# # }
# 
# # length(ARI_grade)
# 
# ## Flesch Ease of Reading
# 
# # for (i in seq_len(length(review_vec))) {
# #   flesch_reading_ease <- readability(tokenize(review_vec[i], lang = "en", format = "obj"),index = "Flesch", quiet = TRUE)
# #
# #   Flesch_raw <- append(Flesch_raw, summary(flesch_reading_ease) %>% pull(raw))
# # }
# #
# # length(Flesch_raw)
# 
# ## SMOG
# 
# capture.output(
# for (i in seq_len(length(review_vec))) {
#   SMOG <-  readability(tokenize(review_vec[i], lang = "en", format = "obj"),index = "SMOG")
# 
#   SMOG_grade <- append(SMOG_grade, summary(SMOG) %>% pull(grade))
#   SMOG_age <-  append(SMOG_age, summary(SMOG) %>% pull(age))
# }
# ,file = nullfile()
# )
# length(SMOG_grade)
```

```{r}
# movies_data <- movies_data %>% 
#   bind_cols(tibble(
#     SMOG_grade = as.double(SMOG_grade),
#     SMOG_age = as.double(SMOG_age)))

# movies_data <- movies_data %>% 
#   bind_cols(tibble(
#     Flesch_raw = as.double(Flesch_raw)
#   ))
# 
# movies_data <- movies_data %>% 
#   bind_cols(tibble(
#     ARI_grade = as.double(ARI_grade)
#   ))
```

```{r}
## Timeline

movies_data <- movies_data %>% 
  mutate(Date = dmy(Date, locale = "english"))

first_dates <- movies_data %>% 
  group_by(Movie) %>% 
  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
  select(Movie, Date) %>% 
  rename(First_Date = Date)

movies_data <- full_join(movies_data, first_dates, by = "Movie") %>% 
  mutate(Timeline = as.integer(Date - First_Date))
```

```{r}
movies_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white")

movies_data %>% 
  ggplot(aes(Rating))+
  geom_bar()

movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white")+
  scale_x_log10()

movies_data %>% 
  ggplot(aes(n_Sentence))+
  geom_histogram(color = "white")+
  scale_x_log10()

movies_data %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white")+
  scale_x_log10()

```

```{r}
movies_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point()+
  geom_smooth()

movies_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~Movie)

movies_data %>% 
  ggplot(aes(Timeline, Helpfulness))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~Movie, scales = "free_x")

movies_data %>% 
  ggplot(aes(log10(Word_Count), Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()

movies_data %>% 
  ggplot(aes((n_Sentence), Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  scale_x_log10()

movies_data %>% 
  ggplot(aes(log10(Word_Count), Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  facet_wrap(~Movie)

```

```{r}
movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.2)+
  geom_smooth()+
  facet_wrap(~Rating)+
  scale_x_log10()

movies_data %>% 
  mutate(WC_Binned = cut_number(Word_Count, n = 10)) %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~WC_Binned)

movies_data %>% 
  mutate(across(.cols = variables, .fns = function(.) log10(. + 1))) %>% 
  select(variables, Word_Count,Rating, Total_Vote, Timeline) %>%
  GGally::ggcorr(label = T)
```

```{r}
mod_lm <- lm(Helpfulness ~ Rating + I(Rating^2) + I(Rating^3)+ log10(Word_Count) + log10(Total_Vote)  + log10(Word_Count)*Rating + Timeline + anticipation   + positive + negative + trust,
           data = movies_data)

summary(mod_lm)
```

```{r}
mod_lm %>% 
  autoplot(which = 1:6, label.hjust = 1.2)
```

```{r}
mod_tobit <- tobit(Helpfulness ~ Rating + I(Rating^2) + I(Rating^3)+ log10(Word_Count) + log10(Total_Vote)  + log10(Word_Count)*Rating + Timeline + anticipation  + positive  + negative  + trust,
                   data = movies_data, left = 0, right = 1)

summary(mod_tobit)
```

```{r}
tibble(Residuals = resid(mod_tobit),
       Fitted = fitted(mod_tobit),
       Observed = movies_data$Helpfulness) %>% 
  ggplot(aes(Fitted, Observed))+
  geom_point(alpha = 0.2)+
  geom_abline(slope = 1, color = "red", size = 1.1, linetype = 2)+
  coord_cartesian(xlim = c(0,1), ylim =c(0,1))
```

```{r}
ggplot(data = tibble(Resids = resid(mod_tobit)),
       aes(Resids, ..density..))+
  geom_histogram(bins = 50, color = "white")
```

```{r}
library(GGally)

movies_data %>%
  mutate(Word_Count = log10(Word_Count),
         Total_Vote = log10(Total_Vote),
         n_Sentence = log10(n_Sentence)) %>% 
  select(Helpfulness, Rating, Total_Vote, Word_Count, n_Sentence) %>% 
  ggpairs()
```

```{r}
summary(mod_tobit)

preds <-  predict(mod_tobit, newdata = tibble(Rating = seq(0.5, 5, 0.5),
                                    Word_Count = rep(30,10),
                                    Total_Vote = rep(10,10)))

qplot(x = seq(0.5, 5, 0.5), preds, geom = "point", ylim = c(0,1))
```

```{r}
fitted(mod_tobit) %>% max

movies_data[which.max(fitted(mod_tobit)),]

predict(mod_tobit, newdata = movies_data[which.min(fitted(mod_tobit)),])
```

```{r}
movies_data[which.min(fitted(mod_tobit)),]  %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  inner_join(get_sentiments("nrc"))
```

### 2022-05-06 Report.Rmd
Thesis Code Backup

---
output:
  html_document:
    theme: flatly
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    df_print: paged
    code_folding: show
---

```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(AER)
library(patchwork)
library(ggfortify)

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE,
                      fig.align = "center",
                      fig.width = 8)

```

```{r}
files <- dir()

files <- files[str_detect(dir(), "all_laptop_reviews.+")]

laptop_data <- map_dfr(files, read_csv)

laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  ))

laptop_data <- laptop_data %>%
  mutate(Total_Vote = Helpful + Unhelpful) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Helpfulness = Helpful / Total_Vote)

laptop_data <- laptop_data %>% 
  mutate(Rev_dup = duplicated(Review)) %>% 
  filter(Rev_dup == 0)

laptop_data <- laptop_data %>% 
  mutate(Doc_ID = row_number())

laptop_data <- laptop_data %>% 
  mutate(Review = str_to_lower(Review, locale = "en"))

words_agg <- laptop_data %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  anti_join(stop_words) %>% 
  count(Doc_ID, name = "Word_Count")

laptop_data <- words_agg %>% 
  inner_join(laptop_data, by = "Doc_ID")

```

```{r}
movies_data <- read_csv("homecoming15-02-22.csv") %>% 
  mutate(Movie = "Homecoming") %>% 
  bind_rows(read_csv("far_from_home15-02-22.csv") %>% 
              mutate(Movie = "Far From Home")) %>% 
  bind_rows(read_csv("no_way_home19-02-22.csv") %>% 
              mutate(Movie = "No Way Home"))

movies_data <- movies_data %>% 
  filter(!is.na(Rating))

movies_data <- movies_data %>% 
  separate(Rating, into = c("Rating", "Total"), sep = "/", ) %>% 
  select(-Total) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Rating = as.double(Rating)) %>% 
  mutate(Helpfulness = Helpful_Vote / Total_Vote) %>% 
  mutate(Rating = Rating/2)

movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)

movies_data <- movies_data %>% 
  mutate(Doc_ID = row_number())

movies_agg <- movies_data %>% 
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  mutate(Doc_ID = row_number()) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  anti_join(stop_words) %>% 
  count(Doc_ID, name = "Word_Count")

movies_data <- movies_data %>% 
  inner_join(movies_agg, by = "Doc_ID")
```

# What Makes a Helpful Review?

In this analysis I replicated the paper "WHAT MAKES A HELPFUL ONLINE REVIEW? A STUDY OF CUSTOMER REVIEWS ON AMAZON.COM" which can be found at this [link.](https://www.researchgate.net/publication/220259990_What_Makes_a_Helpful_Online_Review_A_Study_of_Customer_Reviews_on_Amazoncom)

In that paper the writers used this data:

```{r}
knitr::include_graphics("paper_contents/The_Data.png")
```

In my work I used the latest Spider-Man Trilogy's reviews from IMDB as experience goods and Laptop reviews from BestBuy as search goods which have over 30 unique laptops.

# Descriptive Analysis

The paper uses three explanatory variables:

* Review Rating as Review Extremity

* Word Count as Review Depth (Informativeness)

* Experience/Search good Dummy Variable

By using these variables and their interactions they try to explain Helpfulness percentage of reviews. In this case Helpfulness is :

$$Helpfulness = \frac{Helpful\ Votes}{Helpful\ Votes \ + Unhelpful\ Votes}$$

Additionally Total Votes are used as a control variable because %80 Helpfulness can come from either 4/5 or 80/100.

## Dependent Variable

Let's introduce the dependent variable by showing the distributions of both types of goods separately. In the plots the blue line represents the means.

```{r}
sum_laptop <- laptop_data %>% 
  summarise(Mean = mean(Helpfulness),
            SD = sd(Helpfulness),
            Sample_Size = n())

sum_movies <- movies_data %>% 
  summarise(Mean = mean(Helpfulness),
            SD = sd(Helpfulness),
            Sample_Size = n())
```

```{r}
p1 <- laptop_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue")+
  geom_vline(xintercept = sum_laptop$Mean, size = 2, alpha = 0.5, color = "blue")+
  labs(y = NULL)+
  ggtitle("The Distribution of Laptop Helpfulness")+
  theme_bw()

p2 <- movies_data %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white", fill = "steelblue")+
  geom_vline(xintercept = sum_movies$Mean, size = 2, alpha = 0.5, color = "blue")+
  labs(y = NULL)+
  ggtitle("The Distribution of Movies Helpfulness")+
  theme_bw()

p1/p2
```

The distribution of the Movies can be considered as normal. However, in Laptop reviews we can actually observe high ends and low ends have many observations and obviously the data isn't normally distributed.

The sample size is `r sum_laptop$Sample_Size` for Laptops(Search Goods) and `r sum_movies$Sample_Size` for Movies(Experience Goods). By the way in this data set I only included reviews which had total votes of 5 and higher to make sure that the reviews I am analyzing were read at least by a certain number of people.

## Bivariate Analysis

Let's also show the relationships between explained and explanatory variables one by one. Additionally I am going to point out the hypothesizes which were set in the paper I am replicating.

After this section I am going to present Multiple Regression results.

### Word Count

Before I counted the words in a particular reviews I also used a "stop word" filter. This filter removes widely used helpless words such as "I, you, there etc." In this case word counts are distributed kind of exponentially so I think it would be a nice practice to take the logarithm of this variable. In the Mudambi's paper they didn't apply such a thing.

```{r}
p1 <- laptop_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue")+
  labs(y = NULL)+
  scale_x_continuous(n.breaks = 10)+
  ggtitle("Distribution of the Word Count for Laptops")+
  theme_bw()

p2 <- laptop_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue")+
  scale_x_log10()+
  labs(x = "Log(Word_Count)", y = NULL)+
  theme_bw()

p3 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue")+
  labs(y = NULL)+
  scale_x_continuous(n.breaks = 10)+
  ggtitle("Distribution of the Word Count for Movies")+
  theme_bw()

p4 <- movies_data %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white", fill = "steelblue")+
  scale_x_log10()+
  labs(x = "Log(Word_Count)", y = NULL)+
  theme_bw()

(p1+p2) / (p3+p4)

```

As you can see that after taking the logarithm word counts can be considered as normally distributed.

In Mudambi's paper they hypothesized that:

* "Review depth has a positive effect on the helpfulness of the review."

* "The product type moderates the effect of review depth on the helpfulness of the review. Review depth has a greater positive effect on the helpfulness of the review for search goods than for experience goods."

In the light of these hypothesizes let's analyze the relationship between helpfulness and the review depth for each good.

```{r}
p1 <- laptop_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  scale_x_log10()+
  ggtitle("Laptops")+
  labs(x = "Log(Word Count)")+
  theme_bw()

p2 <- movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  scale_x_log10()+
  ggtitle("Movies")+
  labs(x = "Log(Word Count)")+
  theme_bw()

p1 / p2
```

In this bivariate case we can see that Laptops(Search Good) has indeed the expected effect. On the other hand, Movies(Experience Good) has a slight negative effect or no effect at all. In some sense the second hypothesis is supported because we can clearly see stronger positive effect of the review depth on helpfulness of the review.

I also checked the effects separately for Movie Reviews. Keep in mind that these movies are of the same series but they got criticized in a different manner. "Homecoming" was on the neutral side, "Far From Home" usually was considered as a let down compared to first movie "Homecoming" and "No way Home" was acclaimed pretty well from nearly every Spider-Man fan.

```{r}
movies_data %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  scale_x_log10()+
  facet_wrap(~Movie)+
  ggtitle("Movies Stratified")+
  theme_bw()
```

In this case we can actually see that review depth might not have an effect on helpfulness of the review at all. The only clear negative relationship comes from the movie "Homecoming". Of course this is only the bivariate case.

### Ratings

on IMDB the review ratings are scaled between 1 to 10 whereas on BestBuy ratings are scaled between 1 to 5. To bring them on a same scale I divided IMDB ratings by two.

To my surprise these distributions look similar. We can see there are more higher ratings and we can also see that the lowest rating 1 has many more observations compared to other low ratings such as 2 and 3.

```{r}
p1 <- laptop_data %>% 
  ggplot(aes(Rating))+
  geom_bar(color = "white", fill = "steelblue")+
  labs(y = NULL)+
  ggtitle("Distribution of the Ratings for Laptops")+
  theme_bw()

p2 <- movies_data %>% 
  ggplot(aes(Rating))+
  geom_bar(color = "white", fill = "steelblue")+
  labs(y = NULL)+
  scale_x_continuous(n.breaks = 10)+
  ggtitle("Distribution of the Ratings for Movies")+
  theme_bw()

(p1/p2)
```

In the Mudambi's paper they claim that:

* "Product type moderates the effect of review extremity on the helpfulness of the review. For experience goods, reviews with extreme ratings are less helpful than reviews with moderate ratings."

```{r}
p1 <- laptop_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth(method = "loess")+
  ggtitle("Laptops")+
  theme_bw()

p2 <- movies_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  ggtitle("Movies")+
  theme_bw()

p1 + p2
```

For two types of goods we can't observe the aforementioned claim. For laptops there is some kind of a "U" shape but extreme reviews on the positive side seem to be much more helpful. In movies case we can observe the similar dip on neutral ratings such as 2 and 3. Additionally, there is one more turning point at the higher end of the ratings. Nonetheless, this hypothesis isn't supported with this data.

Again I stratified the movies to check if there are similar patterns.

```{r}
movies_data %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point(alpha = 0.3)+
  geom_smooth()+
  facet_wrap(~Movie)+
  ggtitle("Relationships for each Movie")+
  theme_bw()
```

So for experience goods reverse "U" shape is expected on Mudambi's paper but even after I stratified the data normal "U" shape persists. Which means that extreme reviews might be more helpful than neutral ones.

### Word Count versus Ratings

This is not really related to the paper but I wanted to share. For laptops, people really like writing longer reviews when they are content with the product. We can't see the similar effect for movies.

```{r}
p1 <- laptop_data %>% 
  ggplot(aes(Word_Count, Rating))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()+
  ggtitle("Laptops")+
  theme_bw()

p2 <- movies_data %>% 
  ggplot(aes(Word_Count, Rating))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()+
  ggtitle("Movies")+
  theme_bw()

p1 + p2
```

# Multiple Regression

In the paper writers fit regression for each type of goods separately and as a whole. They also used Tobit Regression as a main tool and presented OLS as a benchmark so I am doing the same.

## Laptops (Search Good)

### Paper Results (Tobit)

```{r}
knitr::include_graphics("paper_contents/Regression_Search.png")
```

### OLS

```{r}
summary(lm(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote), data = laptop_data))
```

### Tobit

```{r}
summary(tobit(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote), data = laptop_data, right = 1, left = 0))
```

In this case I have the similar results with the paper. All the parameters signs are the same. This means that:

* Review Depth has a positive effect on Helpfulness.

* Ratings has a "U" shape which means that extreme ratings are much more useful than neutrals.

Both OLS and Tobit gives the similar results as well. Tobit regression has stronger parameters.

## Movies (Experience Good)

### Paper Results(Tobit)

```{r}
knitr::include_graphics("paper_contents/Regression_Experience.png")
```

### OLS

```{r}
summary(lm(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote), data = movies_data))
```

### Tobit

```{r}
summary(tobit(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote), data = movies_data, right = 1, left = 0))
```

For the movies case there are contradictions from the paper.

* Ratings(Review Extremity) isn't reverse "U" since quadratic term has a positive significant sign.

* There is actually a negative effect (though it is very close to 0) of Review Depth on Helpfulness.

Again both OLS and Tobit give similar results.

## All

```{r}
files <- dir()

files <- files[str_detect(dir(), "all_laptop_reviews.+")]

laptop_data <- map_dfr(files, read_csv)

laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  ))

laptop_data <- laptop_data %>%
  mutate(Total_Vote = Helpful + Unhelpful) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Helpfulness = Helpful / Total_Vote) %>% 
  mutate(is_Exp = 0)

laptop_data <- laptop_data %>% 
  mutate(Rev_dup = duplicated(Review)) %>% 
  filter(Rev_dup == 0)

movies_data <- read_csv("homecoming15-02-22.csv") %>% 
  mutate(Movie = "Homecoming") %>% 
  bind_rows(read_csv("far_from_home15-02-22.csv") %>% 
              mutate(Movie = "Far From Home")) %>% 
  bind_rows(read_csv("no_way_home19-02-22.csv") %>% 
              mutate(Movie = "No Way Home"))

movies_data <- movies_data %>% 
  filter(!is.na(Rating))

movies_data <- movies_data %>% 
  separate(Rating, into = c("Rating", "Total"), sep = "/", ) %>% 
  select(-Total) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Rating = as.double(Rating)) %>% 
  mutate(Helpfulness = Helpful_Vote / Total_Vote) %>% 
  mutate(Rating = Rating/2) %>% 
  mutate(is_Exp = 1)

movies_data <- movies_data %>% 
  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
  filter(Rev_dup == 0)

all_data <- laptop_data %>% 
  rename(Helpful_Vote = Helpful) %>% 
  select(-Unhelpful, -Product_Name, -Page) %>% 
  bind_rows(movies_data %>% select(-Movie))

all_data <- all_data %>% 
  mutate(Doc_ID = row_number())

all_data <- all_data %>% 
  mutate(Review = str_to_lower(Review, locale = "en"))

words_agg <- all_data %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  anti_join(stop_words) %>% 
  count(Doc_ID)

all_data <- words_agg %>% 
  inner_join(all_data, by = "Doc_ID") 
```

Finally I run the regression one last time with a dummy variable for experience goods called `is_Exp`. In the paper, writers encoded Experience goods with 1 and search good with 0. I am following the same.

### Paper Results(Tobit)

```{r}
knitr::include_graphics("paper_contents/Regression_Full_Sample.png")
```

### OLS

```{r}
summary(lm(Helpfulness ~ Rating*is_Exp + I(Rating^2)*is_Exp + log10(n)*is_Exp + log10(Total_Vote), data = all_data))
```

### Tobit

```{r}
summary(tobit(Helpfulness ~ Rating*is_Exp + I(Rating^2)*is_Exp + log10(n)*is_Exp + log10(Total_Vote), data = all_data, left = 0, right = 1))
```

These results are also consistent with individual regressions I ran above. Although parameters change a little bit they still have the same signs.

# Conclusion

The results for search goods are consistent with the results from the paper. For the case of experience goods there are important deviations. First of all, for movies, extreme reviews are just as helpful as search goods' extreme reviews. However, as you saw from the bivariate analysis, the relationship between review extremity and helpfulness was quite complex(the function had two turning points). Secondly, word count (review depth) has little to no relationship with helpfulness of the review.

### 2022-05-06 SearchGoods_EDA.Rmd
Thesis Code Backup

---
output:
  html_document:
    theme: flatly
    highlight: pygments
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    df_print: paged
    code_folding: show
---

```{r, include=FALSE}
library(tidyverse)
library(tidytext)
library(scales)
library(AER)
library(ggfortify)
library(lubridate)
library(koRpus.lang.en)

options(scipen = 20)

knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      fig.align = "center",
                      fig.width = 8)

```

```{r}
## Phone Data

phones_data <- read_csv("all_phone_reviews_15_03_22.csv", show_col_types = FALSE)

phones_data <- phones_data %>% 
  mutate(Product_Type = "Phone")

## Laptop Data

files <- dir()
files <- files[str_detect(dir(), "all_laptop_reviews.+")]
laptop_data <- map_dfr(files, read_csv, show_col_types = FALSE)

laptop_data <- laptop_data %>% 
  filter(!Product_Name %in% c(
    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
  )) %>% 
  mutate(Product_Type = "Laptop")

## TV Data

tvs_data <- read_csv("all_tv_reviews_16_03_22.csv", show_col_types = FALSE)
tvs_data <- tvs_data %>% 
  mutate(Product_Type = "TV")

## Merging All

search_goods <- phones_data %>% 
  bind_rows(tvs_data, laptop_data)

## Filtering Total Votes below 5

search_goods <- search_goods %>% 
  mutate(Total_Vote = Helpful + Unhelpful) %>% 
  filter(Total_Vote > 4) %>% 
  mutate(Helpfulness = Helpful / Total_Vote) %>% 
  mutate(is_Exp = 0)

search_goods <- search_goods %>% 
  mutate(Dupped = duplicated(Review)) %>% 
  filter(Dupped == 0)

## Word Counts

search_goods <- search_goods %>% 
  mutate(Doc_ID = row_number())

words_agg <- search_goods %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  #anti_join(stop_words) %>% 
  count(Doc_ID, name = "Word_Count")

search_goods <- search_goods %>% 
  inner_join(words_agg, by = "Doc_ID")

## Emotion Sentiments (EmoLex)

sentiments_agg <- search_goods %>%
  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
  inner_join(get_sentiments("nrc")) %>% 
  count(Doc_ID, sentiment, name = "Sent_Count") %>% 
  pivot_wider(names_from = sentiment, values_from = Sent_Count, values_fill = 0)

search_goods <- search_goods %>% 
  full_join(sentiments_agg, by = "Doc_ID")

variables <- names(sentiments_agg)[-1]

search_goods <- search_goods %>% 
  mutate(across(.cols = variables, .fns = ~ifelse(is.na(.), 0, .) ))

search_goods <- search_goods %>% 
  mutate(across(.cols = all_of(variables), .fns = function(.) ./Word_Count*100))

search_goods <- search_goods %>% 
  mutate(across(.cols = variables, .fns = function(.) log10(. + 1)))

## Dates

search_goods <- search_goods %>% 
  mutate(Date = as_date(mdy_hm(Date, locale = "english")))

first_dates <- search_goods %>% 
  group_by(Product_Name) %>% 
  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
  select(Product_Name, Date) %>% 
  rename(First_Date = Date)

search_goods <- search_goods %>% 
  full_join(first_dates, by = "Product_Name") %>% 
  mutate(Timeline = as.integer(Date - First_Date))

```

```{r}
## Readability Index(Unfortunately wasn't helpful)

# review_vec <-  search_goods %>%
#   pull(Review)
# 
# SMOG_grade <- vector(mode = "double")
# 
# capture.output(
# 
# for (i in seq_len(length(review_vec))) {
#   SMOG <-  readability(tokenize(review_vec[i], lang = "en", format = "obj"),index = "SMOG", quiet = TRUE)
#   
#   SMOG_grade <- append(SMOG_grade, summary(SMOG) %>% pull(grade))
# }
# ,file = nullfile()
# )
# 
# length(SMOG_grade)
# 
# search_goods <- search_goods %>% 
#   mutate(SMOG_grade = as.double(SMOG_grade))
```

# EDA

```{r}
search_goods %>% 
  ggplot(aes(Helpfulness))+
  geom_histogram(color = "white")

search_goods %>% 
  ggplot(aes(Word_Count))+
  geom_histogram(color = "white")+
  scale_x_log10()

search_goods %>% 
  ggplot(aes(Rating))+
  geom_bar(color = "white")

search_goods %>% 
  ggplot(aes(Timeline+1))+
  geom_histogram(color = "white")+
  scale_x_log10()

search_goods %>% 
  ggplot(aes(Total_Vote))+
  geom_histogram(color = "white")+
  scale_x_log10()

```

```{r}
search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()

search_goods %>% 
  ggplot(aes(Word_Count, Helpfulness))+
  geom_point()+
  geom_smooth()+
  facet_wrap(~Rating)+
  scale_x_log10()

search_goods %>% 
  mutate(WC_Binned = cut_number(Word_Count, n = 10)) %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point()+
  geom_smooth(method = "loess")+
  facet_wrap(~WC_Binned)

search_goods %>% 
  ggplot(aes(Rating, Helpfulness))+
  geom_point()+
  geom_smooth(method = "loess")

search_goods %>% 
  ggplot(aes(Timeline+1, Helpfulness))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()

search_goods %>% 
  ggplot(aes(Total_Vote, Helpfulness))+
  geom_point()+
  geom_smooth()+
  scale_x_log10()

search_goods %>% 
  select(variables, Word_Count,Rating, Total_Vote, Timeline) %>% 
  GGally::ggcorr(label = T)
```

```{r}
model_lm <- lm(Helpfulness ~ Rating + I(Rating^2) + I(Rating^3)+ log10(Word_Count) + log10(Total_Vote)  + log10(Word_Count)*Rating + Timeline + anticipation  + positive + negative + trust,
               data = search_goods )
summary(model_lm) 
```

```{r}
model_tobit <- tobit(Helpfulness ~ Rating + I(Rating^2) + I(Rating^3)+ log10(Word_Count) + log10(Total_Vote)  + log10(Word_Count)*Rating + Timeline + anticipation   + positive + negative + trust,
                     data = search_goods,
                     left = 0, right = 1)
summary(model_tobit)
```

```{r}
tibble(Residuals = resid(model_tobit),
       Fitted = fitted(model_tobit),
       Observed = search_goods$Helpfulness) %>% 
  ggplot(aes(Fitted, Observed))+
  geom_point(alpha = 0.2)+
  geom_abline(slope = 1, color = "red", size = 1.1, linetype = 2)+
  coord_cartesian(xlim = c(0,1), ylim =c(0,1))
```

```{r}
qplot(resid(model_lm), bins = 50)
qplot(resid(model_tobit), bins = 50)
```

```{r}
toy_data <- tibble(Rating = seq(0.5,5, 0.5),
                   Word_Count = rep(800,10),
                   Total_Vote = rep(100,10))

tibble(
  preds = predict(model_tobit, newdata = toy_data),
  Rating = seq(0.5,5, 0.5)
) %>% 
  ggplot(aes(Rating, preds))+
  geom_line()+
  geom_point()
```

### 2022-05-07 Paper.Rmd
All the paper goes here including analysis code.

---
title: "Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?"
bibliography: references.bib
link_citations: true
---

# Introduction

-   E-Retail boomed.

-   Reviews(electronic word-of-mouth) create opportunities for both sellers and buyers. On the buyers' side, reviews can be used to decrease search costs and consumer uncertainty.

-   However, this boom of e-retail also created an abundance of product reviews on the internet so answering the question of "what makes a useful review?" is very important because reading more and more reviews can increase the search costs.

-   Perceived Helpfulness is moderated by product types because different product types have different search cost responsiveness. Consider SEC Classification. Emphasize this a lot.

-   The research on perceived helpfulness is still growing and there is no consensus on neither about methodology nor about important independent variables. In fact, there are conflicting results in the literature. Thus, creating a need for more analyses on different and unique data sets.

-   Briefly talk about other research papers and present the data.

-   Briefly talk about the results.

-

# Literature Review

# Theoretical Framework

-   Nelson's two paper as an Economics theory. SEC Classification.

-   Negativity Bias Theory.

# Data

# Methodology

# Results

# Discussion and Conclusion

### 2022-05-07 Paper.Rmd
The journey conts

@@
 ---
-title: "Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?"
+title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
 bibliography: references.bib
-link_citations: true
+link-citations: yes
+csl: ieee.csl
 ---
@@
 
--   E-Retail boomed.
+Online shopping has becoming more and more prevalent in average consumer's daily life.
+Electronic shopping brought many advantages both for sellers and buyers.
+One of the positive perks is Online Customer Reviews (OCR).
+Online Customer Reviews come in the form of electronic word-of-mouth (EVOM) @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010.
+OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011].
+\###(need different citations here!!!)\###
 
--   Reviews(electronic word-of-mouth) create opportunities for both sellers and buyers. On the buyers' side, reviews can be used to decrease search costs and consumer uncertainty.
+OCR help customers by decreasing their search costs.
+Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product.
+This information acquiring process is costly.
+Furthermore, this information gathering process might be more or less costly depending on the product type @10.2307/1830691.
 
--   However, this boom of e-retail also created an abundance of product reviews on the internet so answering the question of "what makes a useful review?" is very important because reading more and more reviews can increase the search costs.
+However, the increased rate of electronic commerce activity also created an abundance of product reviews on the internet.
+The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021].
+Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews.
+Additionally, not all reviews have the same informativeness level @pan2011.
+Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost.
+To make the understanding of a "helpful review" more clear we can define them as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.
 
--   Perceived Helpfulness is moderated by product types because different product types have different search cost responsiveness. Consider SEC Classification. Emphasize this a lot.
+Since OCR don't share the same level of informativeness and usefulness @pan2011, most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
+On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button.
+In this paper, we acquired data from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.
 
@@
 
+-   Give the background of perceived helpfulness
+
 # Theoretical Framework
@@
 
--   Negativity Bias Theory.
+-   Negativity Bias Theory and Loss Aversion
+
+-   Social Learning and Herding Effect
 

### 2022-05-09 Paper.Rmd
The journey conts again

@@
 One of the positive perks is Online Customer Reviews (OCR).
-Online Customer Reviews come in the form of electronic word-of-mouth (EVOM) @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010.
+Online Customer Reviews come in the form of electronic word-of-mouth @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010.
 OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011].
@@
 This information acquiring process is costly.
-Furthermore, this information gathering process might be more or less costly depending on the product type @10.2307/1830691.
+Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691.
+Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
+On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).
 
@@
 
--   The research on perceived helpfulness is still growing and there is no consensus on neither about methodology nor about important independent variables.
-In fact, there are conflicting results in the literature.
-Thus, creating a need for more analyses on different and unique data sets.
+The research on perceived helpfulness is still growing.
+In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature @hunter1991.
+In this case, the study on perceived helpfulness is not an exception.
+Because of this reason, We think more empirical studies on perceived helpfulness are required.
+This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.
 
@@
 
--
+-   Outline the paper
 
@@
 
--   Give the background of perceived helpfulness
+-   mention moderating effects of product type for every variable
+
+The research on Online Customer Reviews could be considered to have two main branches.
+One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012].
+The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only.
+Of course, the boundary between these two branches are somewhat blurry and same independent variables were used to explain both helpfulness and sales.
+Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales.
+Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018].
+Thus, these two branches are inter-connected with each other.
+This paper tries to understand behavioral aspect.
+
+Many independent variables and their relationship between perceived helpfulness was examined by researchers.
+Hong et al.
+(2017) @hong2017 groups these independent variables into two chunks.
+The first group is reviewer-related predictors.
+Variables within this group tries to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.).
+[@sun2019; @ghose2011].
+The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018].
+Ghose et al.
+(2011) @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones.
+The choice of the variables is of course heavily dependent on the data itself.
+In this paper, we only examined review-related predictors.
+
+Review Length(Depth) could be considered as one of the most important independent variable explaining perceived helpfulness.
+It might be implemented in different ways but for the majority of the studies it is the word count in a given review.
+For most of the researchers, longer reviews contain more information about the product.
+As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020].
+However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015].
+Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].
+
+Review Rating (Review Extremity) is another important identifier of perceived helpfulness.
+This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product.
+It's effect on perceived helpfulness is rather divergent in the literature.
+A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness.
+Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[ @mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006].
+In other studies, linear positive relationship was found.
+In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020].
+There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].
+
+Review Age is an indicator of how long the time passed after a review published on a web site.
+On some papers the opposite of Review Age, Review Freshness could be employed as well.
+Different effects on perceived helpfulness were also observed by researchers.
+Some researchers discussed that a timely review is very important at conveying the true information about a certain product [@liu2014; @li2019; @zhou2019].
+Others discussed that some web sites promotes newer reviews and because of that more recent reviews are more helpful [@lee2014; @choi2020; @wu2021].
+
+-   mention negative positive words here
 
@@
 
-# Data
+# Methodology
 
-# Methodology
+## Data Collection
+
+## Variables and EDA
+
+## Method
 
@@
 # Discussion and Conclusion
+
+# References

### 2022-05-10 Paper.Rmd
joruney conts vol3

@@
 This information acquiring process is costly.
-Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691.
+Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods \@10.2307/1830691.
 Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
@@
 A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness.
-Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[ @mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006].
+Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006].
 In other studies, linear positive relationship was found.
@@
 
--   Nelson's two paper as an Economics theory. SEC Classification.
+## Search and Experience Goods Classification
 
--   Negativity Bias Theory and Loss Aversion
+-   extend this later and try to connect to the methodology
+
+Nelson (1970) @10.2307/1830691 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
+Search Attributes are the qualities that can be assessed before purchase.
+On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase.
+A single good can have both search and experience attributes.
+Depending on its dominant attributes the good can be classified as Search or Experience.
+A product's Total Cost consists of both Search Cost and Product Cost.
+This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.
+
+To explain it in a more generalized way, let's also define what "search" is.
+Nelson (1970) @10.2307/1830691 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
+People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
+This is why search is costlier for Experience Goods.
+For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it.
+Even though a car has experience attributes, with this logic it is considered as a search good @klein1998.
+
+-   might explain why negative reviews arent that helpful for movies
+
+## Negativity Bias Theorem and Loss Aversion
+
+-   needs to be connected to the method
+
+Humans tend to care about losses more than same amount of gains.
+Losing 100\$ is psycholgically much more impactful than finding 100\$.
+This behavior is best explained by "loss aversion" from Behavioral Economics.
+[@kahneman1979; @schindler2017].
+Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses @herr1991.
+
+Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than positive ones.
+--, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones.
+--, higher negative dominance --
+A combination of equally negative and positive cues results in more negative impressions.
+--, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones.
+--[ @rozin2001; @sen2007; @eslami2018].
 

### 2022-05-12 Paper.Rmd
jrny conts rly

@@
 ---
+
+```{r, echo=FALSE}
+library(tidyverse)
+library(tidytext)
+library(scales)
+library(AER)
+library(ggfortify)
+library(lubridate)
+
+options(scipen = 20)
+
+knitr::opts_chunk$set(warning = FALSE,
+                      message = FALSE,
+                      fig.align = "center",
+                      fig.width = 8,
+                      echo = FALSE)
+```
 
@@
 This information acquiring process is costly.
-Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods \@10.2307/1830691.
+Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691 .
 Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
@@
 
-Nelson (1970) @10.2307/1830691 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
+Nelson (1970) [@10.2307/1830691] differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
 Search Attributes are the qualities that can be assessed before purchase.
@@
 To explain it in a more generalized way, let's also define what "search" is.
-Nelson (1970) @10.2307/1830691 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
+Nelson (1970) [@10.2307/1830691] defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
 People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
@@
 Humans tend to care about losses more than same amount of gains.
-Losing 100\$ is psycholgically much more impactful than finding 100\$.
+Losing 100\$ is psychologically much more impactful than finding 100\$.
 This behavior is best explained by "loss aversion" from Behavioral Economics.
@@
 --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones.
---, higher negative dominance --
-A combination of equally negative and positive cues results in more negative impressions.
+--, higher negative dominance -- A combination of equally negative and positive cues results in more negative impressions.
 --, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones.
---[ @rozin2001; @sen2007; @eslami2018].
+--[@rozin2001; @sen2007; @eslami2018].
 
@@
 
-# Methodology
+# Research Methodology
 
@@
 
+The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 @10.5555/1593511.
+The scraper got the customer reviews from IMDB and BestBuy.
+The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America.
+Both websites host a great amount of online reviews.
+After the data was collected it was further transformed and analyzed with the help of R Programming Language [@RCore; @Tidyverse; @Tidytext].
+
+Online Customer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited.
+It is nearly impossible to evaluate a movie before watching it.
+Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective perspectives (writing, production quality etc.).
+There are also numerous studies that analyzed movies as experience goods[@10.2307/1830691; @liu2014; @ghose2006; @baek2012; @lee2016].
+
+BestBuy is a very big electronics retailer and because of this the website offers a sizable number of OCR for search goods.
+Contrary to experience goods, search goods usually have more objectively quantifiable traits.
+For example, resolution or screen size of a TV, RAM or GPU of a Laptop, storage or battery lifetime of a Smart Phone.
+Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019].
+Therefore, we collected search goods data from BestBuy.
+
+-   mention that channels can change the way we perceive search and experience goods.
+
+From IMDB reviews of 22 movies were collected as experience goods.
+In total 22 movies account for 31,863 reviews.
+From BestBuy, total of 383,357 reviews were collected as search goods.
+Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones.
+However, in the data there are many reviews that were never voted.
+To make sure that we are analyzing reviews that were actually read by people, we set a threshold for Total Reviews as five.
+In other words, we removed reviews that have less than 5 Total Votes [@choi2020; @baek2012].
+At the very end, we were left with 15,024 observations for experience goods and 8,042 observations for search goods.
+It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times.
+
+It should be noted that in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names.
+We removed all duplicates along with original reviews because the reviews had different helpfulness ratios.
+
 ## Variables and EDA
+
+```{r Data_Prep_Experience}
+# Experience Goods
+
+## Read the Data
+
+files <- dir()
+
+files <- files[str_detect(files, "movie_.+")]
+
+movies_data <- map_dfr(files, read_csv, show_col_types = FALSE)
+
+## Removing reviews without Ratings
+movies_data <- movies_data %>% 
+  filter(!is.na(Rating))
+
+## Creating Helpul and Total Votes Variables 
+movies_data <- movies_data %>% 
+  separate(Rating, into = c("Rating", "Total"), sep = "/", ) %>% 
+  select(-Total) %>% 
+  filter(Total_Vote > 4) %>% 
+  mutate(Rating = as.double(Rating)) %>% 
+  mutate(Helpfulness = Helpful_Vote / Total_Vote) %>% 
+  mutate(Rating = Rating/2)
+
+## Removing All the Duplicated Reviews including the original since same reviews were written by differend user names
+movies_data <- movies_data %>% 
+  mutate(Rev_dup = duplicated(Review) | duplicated(Review, fromLast = TRUE)) %>% 
+  filter(Rev_dup == 0)
+
+## Words
+movies_data <- movies_data %>% 
+  mutate(Doc_ID = row_number())
+
+## Word Count
+movies_agg <- movies_data %>% 
+  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
+  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
+  count(Doc_ID, name = "Word_Count")
+
+movies_data <- movies_data %>% 
+  inner_join(movies_agg, by = "Doc_ID")
+
+## Emotion Sentiments (EmoLex)
+### log10(Proportion of Emotion Words * 100)
+
+sentiments_agg <- movies_data %>%
+  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
+  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
+  inner_join(get_sentiments("nrc")) %>% 
+  count(Doc_ID, sentiment, name = "Sent_Count") %>% 
+  pivot_wider(names_from = sentiment, values_from = Sent_Count, values_fill = 0)
+
+movies_data <- movies_data %>% 
+  full_join(sentiments_agg, by = "Doc_ID")
+
+variables <- names(sentiments_agg)[-1]
+
+movies_data <- movies_data %>% 
+  mutate(across(.cols = all_of(variables), .fns = ~ifelse(is.na(.), 0, .) ))
+
+movies_data <- movies_data %>% 
+  mutate(across(.cols = all_of(variables), .fns = function(.) ./Word_Count*100))
+
+movies_data <- movies_data %>% 
+  mutate(across(.cols = variables, .fns = function(.) log10(. + 1)))
+
+## Freshness (Timeline)
+movies_data <- movies_data %>% 
+  mutate(Date = dmy(Date, locale = "english"))
+
+first_dates <- movies_data %>% 
+  group_by(Movie) %>% 
+  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
+  select(Movie, Date) %>% 
+  rename(First_Date = Date)
+
+movies_data <- full_join(movies_data, first_dates, by = "Movie") %>% 
+  mutate(Freshness = as.integer(Date - First_Date))
+
+```
+
+```{r Data_Prep_Search}
+
+# Search Goods
+## Phone Data
+phones_data <- read_csv("all_phone_reviews_15_03_22.csv", show_col_types = FALSE)
+
+phones_data <- phones_data %>% 
+  mutate(Product_Type = "Phone")
+
+## Laptop Data
+files <- dir()
+files <- files[str_detect(dir(), "all_laptop_reviews.+")]
+laptop_data <- map_dfr(files, read_csv, show_col_types = FALSE)
+### Removing replicates that I couldn't detect earlier
+laptop_data <- laptop_data %>% 
+  filter(!Product_Name %in% c(
+    'Samsung - Galaxy Book Pro 360 15.6" AMOLED Touch-Screen Laptop - Intel Evo Platform Core i7 - 16GB Memory - 1TB SSD - Mystic Navy',
+    'ASUS - 14.0" Laptop - Intel Celeron N4020 - 4GB Memory - 64GB eMMC - Star Black - Star Black',
+    'ASUS - 14" Chromebook - Intel Celeron N3350 - 4GB Memory - 32GB eMMC - Silver',
+    'Samsung - Galaxy 13.3" 4K Ultra HD Touch-Screen Chromebook - Intel Core i5 - 8GB Memory - 256GB SSD - Mercury Gray'
+  )) %>% 
+  mutate(Product_Type = "Laptop")
+
+## TV Data
+tvs_data <- read_csv("all_tv_reviews_16_03_22.csv", show_col_types = FALSE)
+tvs_data <- tvs_data %>% 
+  mutate(Product_Type = "TV")
+
+## Merging All 
+search_goods <- phones_data %>% 
+  bind_rows(tvs_data, laptop_data)
+
+## Creating Total Votes variable Filtering Total Votes below 5
+
+search_goods <- search_goods %>% 
+  mutate(Total_Vote = Helpful + Unhelpful) %>% 
+  filter(Total_Vote > 4) %>% 
+  mutate(Helpfulness = Helpful / Total_Vote) %>% 
+  mutate(is_Exp = 0)
+
+search_goods <- search_goods %>% 
+  mutate(Dupped = duplicated(Review)) %>% 
+  filter(Dupped == 0)
+
+## Word Counts
+
+search_goods <- search_goods %>% 
+  mutate(Doc_ID = row_number())
+
+words_agg <- search_goods %>%
+  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
+  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
+  count(Doc_ID, name = "Word_Count")
+
+search_goods <- search_goods %>% 
+  inner_join(words_agg, by = "Doc_ID")
+
+## Emotion Sentiments (EmoLex)
+### log10(Proportion of Emotion Words * 100)
+
+sentiments_agg <- search_goods %>%
+  mutate(Review = str_to_lower(Review, locale = "en")) %>% 
+  unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
+  inner_join(get_sentiments("nrc")) %>% 
+  count(Doc_ID, sentiment, name = "Sent_Count") %>% 
+  pivot_wider(names_from = sentiment, values_from = Sent_Count, values_fill = 0)
+
+search_goods <- search_goods %>% 
+  full_join(sentiments_agg, by = "Doc_ID")
+
+variables <- names(sentiments_agg)[-1]
+
+search_goods <- search_goods %>% 
+  mutate(across(.cols = variables, .fns = ~ifelse(is.na(.), 0, .) ))
+
+search_goods <- search_goods %>% 
+  mutate(across(.cols = all_of(variables), .fns = function(.) ./Word_Count*100))
+
+search_goods <- search_goods %>% 
+  mutate(across(.cols = variables, .fns = function(.) log10(. + 1)))
+
+## Freshness (Timeline)
+
+search_goods <- search_goods %>% 
+  mutate(Date = as_date(mdy_hm(Date, locale = "english")))
+
+first_dates <- search_goods %>% 
+  group_by(Product_Name) %>% 
+  slice_min(order_by = Date, n = 1, with_ties = F) %>% 
+  select(Product_Name, Date) %>% 
+  rename(First_Date = Date)
+
+search_goods <- search_goods %>% 
+  full_join(first_dates, by = "Product_Name") %>% 
+  mutate(Freshness = as.integer(Date - First_Date))
+```
+
+### Independent Variable
 

### 2022-05-16 Paper.Rmd
jrny conts rly :(

@@
 csl: ieee.csl
+output:
+  bookdown::pdf_document2: 
+    fig.caption: yes
+    includes:
+      in_header: non-float-fig.tex
 ---
 
-```{r, echo=FALSE}
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
 library(tidyverse)
@@
 library(lubridate)
+library(bookdown)
+library(patchwork)
+
+theme_set(theme_bw(base_size = 12))
 
@@
                       fig.align = "center",
-                      fig.width = 8,
+                      fig.width = 7,
                       echo = FALSE)
@@
 This information acquiring process is costly.
-Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @10.2307/1830691 .
+Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @nelson1970 .
 Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
@@
 
-Nelson (1970) [@10.2307/1830691] differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
+Nelson (1970) [@nelson1970] differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
 Search Attributes are the qualities that can be assessed before purchase.
@@
 To explain it in a more generalized way, let's also define what "search" is.
-Nelson (1970) [@10.2307/1830691] defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
+Nelson (1970) [@nelson1970] defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
 People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
@@
 
-The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 @10.5555/1593511.
+The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 @python3.
 The scraper got the customer reviews from IMDB and BestBuy.
@@
 Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective perspectives (writing, production quality etc.).
-There are also numerous studies that analyzed movies as experience goods[@10.2307/1830691; @liu2014; @ghose2006; @baek2012; @lee2016].
+There are also numerous studies that analyzed movies as experience goods[@nelson1970] ; @liu2014; @ghose2006; @baek2012; @lee2016].
 
@@
 It should be noted that in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names.
-We removed all duplicates along with original reviews because the reviews had different helpfulness ratios.
+All duplicates along with original reviews were removed because the reviews had different helpfulness ratios.
 
-## Variables and EDA
+## Exploratory Data Analysis
 
@@
 
-### Independent Variable
+In this section both dependent and independent variables are going to be introduced.
+The goal of this section is not "confirmatory" whatsoever.
+As a researcher, I believe sharing the data that I used in the study transparently increases the research's reproducibility value.
+
+As an outline, firstly the dependent variable is going to be introduced in a univariate manner and then independent variables are going to come into the picture both in univariate and bivariate way.
+
+### Dependent Variable
+
+$$
+Perceived\ Helpfulness = \frac{Helpful\ Votes}{Total\ Votes}
+$$
+
+The ratio of helpfulness is derived from the formula above. Below on Figure \@ref(fig:IV-Hist-Search) the distribution of the helpfulness for search goods can be observed.
+
+```{r IV-Hist-Search, fig.cap="Distribution of the Helpfulness of Search Goods"}
+
+search_goods %>% 
+  ggplot(aes(Helpfulness))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 10)+
+  labs(y = NULL)
+
+```
+
+As it can be seen the distribution is rather skewed.
+Looks like in the electronics case, readers find some reviews very helpful.
+In fact, in the data there is one review which had over 170 helpful votes with zero unhelpful votes.
+On the other hand, distribution for experience goods on Figure \@ref(fig:IV-Hist-Exp) presents a different picture.
+This time helpfulness ratio is sort of normally distributed.
+There aren't very helpful reviews.
+The most helpful review interval seems to be lying between 70% to 80%.
+
+```{r IV-Hist-Exp, fig.cap="Distribution of the Helpfulness of Experience Goods"}
+movies_data %>% 
+  ggplot(aes(Helpfulness))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 10)+
+  labs(y = NULL)
+```
+
+Hong et al.
+(2014) [@hong2014; @sun2019] states that consumers likely to form homogeneous opinions about search goods.
+On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods.
+Intuitively, what these histograms show is the same.
+For instance, positive or negative attributes of search goods can be expressed in a limited number of ways.
+The storage space of a phone might be small or CPU of a laptop might not be fast as expected.
+Thus, one good review is be enough to reveal the quality of a product.
+I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search).
+In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%.
+This is because evaluation process of movies is rather subjective.
+One person might not like Spider-Man: Homecoming and another would love it.
+
+-   you can elaborate a little bit more about how movies cant be evaluated objectively
+
+### Independent Variables
+
+#### Review Rating (Review Extremity)
+
+Review Rating is the star rating that was given by the reviewer as an evaluation of a product.
+
+For both search and experience goods the bi-modality of the distributions can be observed on Figure \@ref(fig:Search-Rating) (A) and Figure \@ref(fig:Experience-Rating) (A) respectively.
+Hu et al.
+@hu2006 also pointed out a similar distribution concerning Online Product Reviews.
+This might mean that consumers usually tend to write product reviews when they are extremely happy or unhappy with the product.
+
+Because the data was taken from two different websites (BestBuy and IMDB), there are two different scales.
+For IMDB that is 1 to 10 and for BestBuy the scale is between 1 and 5.
+To make the interpretation of the regression coefficients uniform, IMDB's scale was divided by 2.
+
+On Figure \@ref(fig:Search-Rating) (B) and Figure \@ref(fig:Experience-Rating) (B) the bivariate relationship between perceived helpfulness and review extremity can be seen.
+Again, as a researcher, I must emphasize that this analysis is not confirmatory.
+On figures, we can observe "U" type of relationship for both Search and Experience goods, though the non-linearity seems to be stronger with Search goods.
+This might suggest that on the average extreme reviews might be more helpful than moderate reviews [@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006].
+On the other hand, it is observable that positive reviews on the average are more helpful than the rest.
+This might indicate that there is a linear positive relationship [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020].
+
+```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods.", fig.height=7}
+p1 <- search_goods %>% 
+  ggplot(aes(Rating))+
+  geom_bar(fill = "steelblue")+
+  labs(y = "Count", x = NULL)
+
+p2 <- search_goods %>% 
+  ggplot(aes(Rating, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(method = "loess", color = "steelblue")+
+  labs(x = "Review Rating")
+
+plots <-  p1 / p2
+
+plots + plot_annotation(tag_levels = "A",
+                        title = "The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods.")
+```
+
+```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods.", fig.height=7}
+p1 <- movies_data %>% 
+  ggplot(aes(Rating))+
+  geom_bar(fill = "steelblue")+
+  scale_x_continuous(n.breaks = 10)+
+  labs(y = "Count", x = NULL)
+
+p2 <- movies_data %>% 
+  ggplot(aes(Rating, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 10)+
+  labs(x = "Review Rating")
+
+plots <-  p1 / p2
+
+plots + plot_annotation(tag_levels = "A",
+                        title = "The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods.")
+```
+
+#### Review Length (Review Depth)
+
+Review Length is the number of the words in a given review.
+
+The exponential distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A).
+This means that reviews become less prevalent as they get longer.
+This might suggest logarithmic transformation which can increase the model fit.
+For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).
+
+-   you might add confidence interval for mean on plots.
+
+The bivariate relationship between the number of words and Helpfulness seems to be varying for different product types.
+For Search goods on Figure \@ref(fig:Search-Length) (C) there is a clear positive relationship [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020].
+However, this positive relationship appears to stop at a threshold[@schindler2012; @huang2015; @baek2012; @kuan2015; @eslami2018].
+With this in mind, logarithmic transformation might make more sense (see Figure \@ref(fig:Search-Length) (D)) for modelling purposes.
+For Experience goods, on the other hand, there seems to be a weak negative relationship or no relationship at all (see Figure \@ref(fig:Experience-Length) (C) and (D)).
+
+-   maybe add more framework for experience goods and no relationship
+
+```{r Search-Length, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
+p1 <- search_goods %>% 
+  ggplot(aes(Word_Count))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = "Number of the Words")
+
+p1_log <- search_goods %>% 
+  ggplot(aes(Word_Count))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  scale_x_log10(n.break = 8)+
+  labs(y = NULL, x = "log10(Number of the Words)")
+
+p2 <- search_goods %>% 
+  ggplot(aes(Word_Count, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(x = "Number of the Words")
+
+p2_log <- search_goods %>% 
+  ggplot(aes(Word_Count, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_log10(n.breaks = 8)+
+  labs(x = "log10(Number of the Words)")
+
+plots <-  p1 / p1_log / p2 / p2_log
+
+plots + plot_annotation(
+  title = "The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)",
+  tag_levels = "A"
+)
+```
+
+```{r Experience-Length, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
+p1 <- movies_data %>% 
+  ggplot(aes(Word_Count))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = "Number of the Words")
+
+p1_log <- movies_data %>% 
+  ggplot(aes(Word_Count))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  scale_x_log10(n.break = 8)+
+  labs(y = NULL, x = "log10(Number of the Words)")
+
+p2 <- movies_data %>% 
+  ggplot(aes(Word_Count, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(x = "Number of the Words")
+
+p2_log <- movies_data %>% 
+  ggplot(aes(Word_Count, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_log10(n.breaks = 8)+
+  labs(x = "log10(Number of the Words)")
+
+plots <-  p1 / p1_log / p2 / p2_log
+
+plots + plot_annotation(
+  title = "The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)",
+  tag_levels = "A"
+)
+```
 

### 2022-05-18 Paper.Rmd
jrny conts again. jrny never ends...

@@
       in_header: non-float-fig.tex
+    toc_depth: 4
 ---
@@
 
-plots + plot_annotation(tag_levels = "A",
-                        title = "The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods.")
+plots + plot_annotation(tag_levels = "A")
 ```
@@
 
-plots + plot_annotation(tag_levels = "A",
-                        title = "The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods.")
+plots + plot_annotation(tag_levels = "A")
 ```
@@
 plots + plot_annotation(
-  title = "The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)",
   tag_levels = "A"
@@
 plots + plot_annotation(
-  title = "The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)",
   tag_levels = "A"
@@
 
-## Method
+#### Freshness of A Review
+
+Review Freshness indicates how recent a review is. To engineer this variable following steps were taken:
+
+1.  The first review date for a particular brand and model of a product (movie, phone, laptop, tv) was taken.
+2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and model resulting an integer variable representing days.
+3.  Bigger numbers represent more recent reviews.
+
+Distributions of both product types resemble exponential distribution (see Figure \@ref(fig:Search-Freshness) (A) and Figure \@ref(fig:Experience-Freshness) (A)).
+Again a logarithmic transformation might be useful here (see Figure \@ref(fig:Search-Freshness) (B) and Figure \@ref(fig:Experience-Freshness) (B)) .
+Interestingly, even after 3 years from the release date some products are still getting reviewed from customers.
+
+On the scatter plots a weak relationship between perceived helpfulness and review freshness could be observed.
+The smoother line suggests both positive [@lee2014; @choi2020; @wu2021] and negative [@liu2014; @li2019; @zhou2019] linear relationship between two variables.
+This non-linearity may explain different findings in the literature.
+
+```{r Search-Freshness, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
+p1 <- search_goods %>% 
+  ggplot(aes(Freshness))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = "Freshness of Review")
+
+p1_log <- search_goods %>% 
+  ggplot(aes(Freshness + 1))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  scale_x_log10(n.break = 8)+
+  labs(y = NULL, x = "log10(Freshness of Review + 1)")
+
+p2 <- search_goods %>% 
+  ggplot(aes(Freshness, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(x = "Freshness of Review")
+
+p2_log <- search_goods %>% 
+  ggplot(aes(Freshness + 1, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_log10(n.breaks = 8)+
+  labs(x = "log10(Freshness of Review + 1)")
+
+plots <- p1 / p1_log / p2 / p2_log
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+
+```
+
+```{r Experience-Freshness, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
+p1 <- movies_data %>% 
+  ggplot(aes(Freshness))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = "Freshness of Review")
+
+p1_log <- movies_data %>% 
+  ggplot(aes(Freshness + 1))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  scale_x_log10(n.break = 8)+
+  labs(y = NULL, x = "log10(Freshness of Review + 1)")
+
+p2 <- movies_data %>% 
+  ggplot(aes(Freshness, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(x = "Freshness of Review")
+
+p2_log <- movies_data %>% 
+  ggplot(aes(Freshness + 1, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_log10(n.breaks = 8)+
+  labs(x = "log10(Freshness of Review + 1)")
+
+plots <- p1 / p1_log / p2 / p2_log
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+
+```
+
+#### Proportion of Negative Words
+
+Negative words were derived by using NRC Word-Emotion Association Lexicon @Mohammad13.
+A lexicon is basically a dictionary of words.
+These words might have similar emotions or sentiments.
+In this case, negative words lexicon was used in order to engineer this variable.
+
+$$
+Negative\ Word \% = \frac{Number\ of\ Matched\ Negative\ Word}{Total\ Words\ in\ Review} 
+$$
+
+These steps were taken in order to create this variable:
+
+1.  Words in a review were tokenized.
+2.  Tokenized words were matched with the lexicon.
+3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
+4.  Logarithmic transformation was applied in order to scale the variable in a better way.
+
+On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen.
+On plots, x-axis labels were given in the logarithm of base 10 so 1.00 on the x-axis implies that 10% of the review was negative words.
+It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods don't have any negative words in them.
+For experience goods this number is `r round(mean(movies_data$negative == 0), digits = 2)` percent.
+
+-   comment on scatterplot
+
+```{r Search-Neg, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
+p1 <- search_goods %>% 
+  ggplot(aes(negative))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = NULL)
+
+p2 <- search_goods %>% 
+  ggplot(aes(negative, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")
+
+plots <- p1 / p2
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+```
+
+```{r Experience-Neg, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
+p1 <- movies_data %>% 
+  ggplot(aes(negative))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = NULL)
+
+p2 <- movies_data %>% 
+  ggplot(aes(negative, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")
+
+plots <- p1 / p2
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+```
+
+#### Proportion of Positive Words
+
+## Hypothesis Development and Method
 

### 2022-05-19 Paper.Rmd
jrnyyyyyyyy

@@
 library(patchwork)
+library(GGally)
 
@@
 
--   comment on scatterplot
+On Figure \@ref(fig:Search-Neg) (B), non-linear relationship between perceived helpfulness and the proportion of negative words can be observed search goods.
+It should be kept in mind that as the proportion increases the sample size decreases.
+This might mean that any statistical test for non-linearity would have low power.
+On the other hand, somewhat weak negative linear relationship between perceived helpfulness and proportion of negative words can be seen for experience goods on Figure \@ref(fig:Experience-Neg) (B).
+
+-   need citation here!
 
@@
 
+This variable was engineered in the same manner with its negative words counterpart.
+In this case, however, reviews of both good types have more positive words in them proportionally when compared to negative words.
+`r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods don't have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods.
+Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).
+
+On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts.
+Furthermore, these plots kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)).
+In a sense, both negative and positive proportions imply number of words.
+As the proportion increases so does the number of words.
+That's why aforementioned figures show similar relationships between variables.
+On higher dimensions these relationships might be different.
+That is why Exploratory Data Analysis should never be conducted in a confirmatory sense.
+
+-   needs sth from literature here as well
+
+```{r Search-Pos, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
+p1 <- search_goods %>% 
+  ggplot(aes(positive))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = NULL)
+
+p2 <- search_goods %>% 
+  ggplot(aes(positive, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")
+
+plots <- p1 / p2
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+```
+
+```{r Experience-Pos, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
+p1 <- movies_data %>% 
+  ggplot(aes(positive))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = NULL, x = NULL)
+
+p2 <- movies_data %>% 
+  ggplot(aes(positive, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue")+
+  scale_x_continuous(n.breaks = 8)+
+  labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")
+
+plots <- p1 / p2
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+```
+
+### Control Variables
+
+"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 over 5 Helpful votes or 80 over 100 Helpful votes [@mudambi2010; @choi2020].
+
+### Correlation Table
+
+Before progressing to the modelling section, it would be a good practice to check the correlations between independent and control variables in order not to cause any multi-colinearity problems.
+As it can be seen on Figure \@ref(fig:Correlations) there aren't any major correlations between independent and control variables for both good types.
+
+```{r Correlations, fig.cap="Correlations between Independent Variables.", fig.height=8}
+p1 <- search_goods %>% 
+  select(Rating, Word_Count, Freshness, positive, negative, Total_Vote) %>% 
+  rename(Proportion_Positive = positive) %>% 
+  rename(Proportion_Negative = negative) %>% 
+  mutate(Word_Count = log10(Word_Count),
+         Total_Vote = log10(Total_Vote)) %>% 
+  ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
+         high = "darkred", label_round = 2, layout.exp = 1)+
+  labs(title = "Search Goods")+
+  theme_void()
+
+p2 <- movies_data %>% 
+  select(Rating, Word_Count, Freshness, positive, negative, Total_Vote) %>% 
+  rename(Proportion_Positive = positive) %>% 
+  rename(Proportion_Negative = negative) %>% 
+  mutate(Word_Count = log10(Word_Count),
+         Total_Vote = log10(Total_Vote)) %>% 
+  ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
+         high = "darkred", label_round = 2, layout.exp = 1)+
+  labs(title = "Experience Goods")+
+  theme_void()
+
+(p1 / p2) +
+  plot_layout(guides = "collect")
+```
+
 ## Hypothesis Development and Method

### 2022-05-31 Paper.Rmd
jrny conts vol idk

@@
 library(GGally)
+library(stargazer)
 
@@
 
+Korfiatis et al.
+(2012) @korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers.
+This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006].
+As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful.
+This extremeness has more objective nature for Search Goods since there are more ways to express pleasantness or unpleasantness for a particular product.
+For instance a bad design in a laptop might cause fans to make much more noise than they should normally do.
+This information along with a very low rating may signal there are some inherent problems with that particular product, making the feedback more helpful.
+On the other hand, for Experience Goods and in this specific case movies, opinions for a given product might be much more subjective.
+For example, a reviewer might find a movie "childish" and give it one star, the other might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness.
+Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process @hoch1989.
+In other words, prior expectations play a bigger role in decision making process for experience goods.
+Therefore it is hypothesized that:
+
+*H1: There is a U-Shaped relationship between Perceived Helpfulness and Review Rating. This U-Shape is stronger/weaker for Search/Experience Goods.*
+
+In order to decrease the uncertainty, search costs must be reduced.
+In \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods.
+Furthermore, people tend to have homogeneous opinions about Search Goods @hong2014 .
+This might mean that information cues are much more uniform for Search Goods.
+[@huang2015; @baek2012].
+In other words, there are limited ways to construct a review because search attributes are more objective.
+Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length.
+However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer.
+Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015].
+On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions @hong2014.
+This means that movie reviews are much more subjective by nature.
+Since there are less objectivity, a helpful review to one person might not be helpful to another.
+However, since there are other ways to objectively evaluate a movie, a weaker positive linear relationship is expected.
+Therefore it is hypothesized that:
+
+*H2: There is a positive relationship between logarithm of Review Length and Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.
+
+-   method
+
+Tobit Regression is selected as the method because of three reasons.
+First of all, dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1.
+The second reason as stated by Mudambi (2010) @mudambi2010 is the potential selection bias in the sample.
+Unfortunately, it is not possible to know how many people read a particular review.
+Neither BestBuy nor IMDB discloses this information.
+Because of this, being included in a sample could be correlated with independent variables.
+For instance, potentially more voted reviews could attract more readers or readers could be drawn to reviews which have certain ratings.
+Lastly, there are many studies from the literature that used Tobit Regression as their research method [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].
+
 # Results
+
+You can find the results at Table \@ref(tab:Reg-Results)
+
+```{r}
+search_tobit <- tobit(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote) + log10(Word_Count) * Rating + log10(Freshness+1) + positive + negative,
+                     data = search_goods,
+                     left = 0, right = 1)
+
+experience_tobit <- tobit(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote) + log10(Word_Count) * Rating + log10(Freshness+1) + positive + negative,
+                     data = movies_data,
+                     left = 0, right = 1)
+
+search_lm <- lm(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote) + log10(Word_Count) * Rating + log10(Freshness+1) + positive + negative,
+                     data = search_goods)
+
+experience_lm <- lm(Helpfulness ~ Rating + I(Rating^2) + log10(Word_Count) + log10(Total_Vote) + log10(Word_Count) * Rating + log10(Freshness+1) + positive + negative,
+                     data = movies_data)
+
+```
+
+```{r Reg-Results, results='asis'}
+stargazer(list("Search Tobit" = search_tobit,
+               "Experience Tobit" = experience_tobit,
+               "Search Linear" = search_lm,
+               "Experience Linear" = experience_lm),
+          type = "latex",
+          header = FALSE,
+          model.numbers = FALSE,
+          column.labels = c("Search", "Experience", "Search", "Experience"),
+          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
+                               "log10(Total Vote)", "log10(Freshness + 1)",
+                               "Positive Proportion",  
+                               "Negative Proportion", "Rating x Review Length"),
+          star.cutoffs = c(0.05, 0.01, 0.001),
+          label = "tab:Reg-Results")
+```
 

### 2022-06-02 Paper.Rmd
will this ever end?

@@
 
+As it was mentioned in \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses.
+Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses.
+Guo et al.
+(2019) @guo2019 found out that people spent more time when evaluating negative reviews.
+This may suggest a linear interaction between Review Extremity and Review Length.
+Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low.
+And when a review is longer it is more helpful for negatively rated reviews than positively rated reviews.
+In this case, it is hypothesized that:
+
+*H3: There is a negative linear interaction effect between Review Rating and the logarithm of the Review Length for both Search and Experience Goods.*
+
+Potential buyers may find more recent reviews helpful because they may want to get updated information on a product.
+This might especially be true for products which are on the market for more than a year.
+For instance, a laptop which was produced in 2018 could be a good choice for that year but for year 2021 it is probable that its features and specifications would be below average.
+A similar behavior might be possible for movies as well.
+However, this time reviewers might need to take their time to digest and evaluate the movie.
+A review which is carefully constructed may be posted later making it more recent compared to a review which was hastily written.
+Furthermore, some popular movies which are considered as classics may attract reviews even way later than they were first released.
+Since some websites may employ algorithms that may push newer reviews to the top in order to be able to increase the interaction on their platforms, these kind of reviews may attract more helpful votes.
+Thus, it is hypothesized that:
+
+*H4: There is a positive relationship between Perceived Helpfulness and Freshness of a Review for both Search and Experience Goods.*
+
 -   method

### 2022-06-03 Paper.Rmd
not much of a change

@@
 Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost.
-To make the understanding of a "helpful review" more clear we can define them as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.
+To make the understanding of a "helpful review" more clear it can defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.
 
@@
 On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button.
-In this paper, we acquired data from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.
+In this paper, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.
 
@@
 In this case, the study on perceived helpfulness is not an exception.
-Because of this reason, We think more empirical studies on perceived helpfulness are required.
+Because of this reason, more empirical studies on perceived helpfulness are required.
 This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.
@@
 
-Many independent variables and their relationship between perceived helpfulness was examined by researchers.
+Many independent variables and their relationship between perceived helpfulness were examined by researchers.
 Hong et al.
@@
 The choice of the variables is of course heavily dependent on the data itself.
-In this paper, we only examined review-related predictors.
+In this paper, only review-related predictors were examined.
 
-Review Length(Depth) could be considered as one of the most important independent variable explaining perceived helpfulness.
+Review Length (Depth) could be considered as one of the most important independent variable explaining perceived helpfulness.
 It might be implemented in different ways but for the majority of the studies it is the word count in a given review.
@@
 
--   mention negative positive words here
+The counts of negative or positive words out of total word count (the proportion of negative and positive words) were employed by a handful of studies [@baek2012; @kuan2015].
+These metrics can measure the sentiment of the review itself.
+They are usually different than Review Extremity.
+In most cases Review Extremity and Review Sentiment (Valence) don't match @zhang2011.
+Both Baek et al.
+(2012) @baek2012 and Kuan et al.
+(2015) @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness.
+The relationship between the proportion of positive words and perceived helpfulness was found to be negative @kuan2015.
 
@@
 1.  Words in a review were tokenized.
-2.  Tokenized words were matched with the lexicon.
+2.  Tokenized words were matched with the words in the lexicon.
 3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
@@
 
--   method
+So far it should be understood that people try to cut down their losses.
+That is why negative cues draw more attention than positive ones.
+It is known that Review Rating is the satisfaction level of a customer towards a product.
+However, Review Rating itself isn't enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product.
+The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review.
+In this case
+
+-   negativity bias/ negative info is more diagnostic than positive/ literature etc./ mention that review extremity and review sentiment are different things.
+
+```{=html}
+<!-- -->
+```
+-
 

### 2022-06-08 Paper.Rmd
forgot to commit yesterday damn it

@@
 Online Customer Reviews come in the form of electronic word-of-mouth @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010.
-OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011].
-\###(need different citations here!!!)\###
+OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].
 
@@
 Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost.
-To make the understanding of a "helpful review" more clear it can defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.
+To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.
 
@@
 
--   Briefly talk about other research papers and present the data.
+This study uses secondary data.
+The reviews were collected from two websites.
+Namely, IMDB and BestBuy.
+The data was scrapped with Selenium Webdriver for Python @python3.
+Over 400,000 reviews and their meta data were gathered initially.
+After the data transformation process the final sample size was over 23,000.
 
@@
 
--   Social Learning and Herding Effect
-
 # Research Methodology
@@
   unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
-  inner_join(get_sentiments("nrc")) %>% 
+  inner_join(get_sentiments("nrc") %>% 
+               filter(!word %in% c("cage", "john","climax", "force", "king", "mad",
+                                   "fury", "hardy","margin", "harry", "venom",
+                                   "marvel", "stark", "iron", "vulture", "green",
+                                   "goblin", "bale"))) %>% 
   count(Doc_ID, sentiment, name = "Sent_Count") %>% 
@@
   unnest_tokens(output = word, input = Review, to_lower = FALSE) %>% 
-  inner_join(get_sentiments("nrc")) %>% 
+  inner_join(get_sentiments("nrc")%>% 
+               filter(!word %in% c("cage", "john","climax", "force", "king", "mad",
+                                   "fury", "hardy","margin", "harry", "venom",
+                                   "marvel", "stark", "iron", "vulture", "green",
+                                   "goblin", "bale"))) %>% 
   count(Doc_ID, sentiment, name = "Sent_Count") %>% 
@@
 So far it should be understood that people try to cut down their losses.
-That is why negative cues draw more attention than positive ones.
+That is why negative cues draw more attention than positive ones [@kahneman1979; @schindler2017].
+Additionally, people find negative information more credible and persuasive than positive information [@ito1998; @Kanouse1984ExplainingNB].
 It is known that Review Rating is the satisfaction level of a customer towards a product.
@@
 The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review.
-In this case
+Reviews with negative sentiments may bring out the risks associated with the purchase better than reviews with positive sentiments.
+Since in this study movies and electronics are compared, it is costlier to make a wrong decision on Search Goods than Experience Goods.
+Therefore, it is hypothesized that:
 
--   negativity bias/ negative info is more diagnostic than positive/ literature etc./ mention that review extremity and review sentiment are different things.
-
-```{=html}
-<!-- -->
-```
--
+*H5: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
+*H6: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*
 
@@
 
-You can find the results at Table \@ref(tab:Reg-Results)
+Tobit regression results are presented at Table \@ref(tab:Reg-Results) alongside with OLS results as a benchmark [@mudambi2010; @kuan2015; @choi2020].
+
+Hyphothesis 1 proposed a U-Shape for the relationship between Review Extremity and Perceived Helpfulness.
+For Search Goods this is true because the linear Rating Extremity coefficient (-0.061, p \< 0.01) has a negative sign and the quadratic Rating Extremity coefficient (0.036, p \< 0.001) has a positive sign.
+The presence of the significant linear interaction effect between Review Extremity and Review Length accentuates the linear Rating Extremity coefficient (-0.043, p \< 0.001).
+This means that as reviews get longer negative extreme reviews become more useful.
+For Experience Goods, on the other hand, both linear (0.026, p \< 0.001) and quadratic (0.006, p \< 0.001) Review Extremity terms are positive.
+A U-Shaped function can't be observed.
+However, the significant interaction effect between Review Length and Review Extremity (-0.015, p \< 0.001) suggests that for longer reviews the linear term turns to negative.
+This means that the function takes a U-Shape after a certain review length.
+It can also be observed that Search Goods have stronger coefficients than Experience Goods meaning the expected U-Shape is more prominent for Search Goods.
+Therefore, it can be said that for shorter reviews Hypothesis 1 is partially supported and for longer reviews it is fully supported.
+
+A positive linear relationship between the logarithm of Review Length and Perceived Helpfulness was proposed with Hypothesis 2.
+A strong relationship between Review Length and Perceived Helpfulness is observed (0.404, p \< 0.001) for Search Goods.
+This effect is moderated by Review Extremity since the interaction effect is significant with a negative sign (-0.043, p \< 0.001).
+As review rating increases the responsiveness of the Perceived Helpfulness to Review Length decreases.
+This means that for positive extreme reviews relatively shorter texts are more helpful.
+Logarithmic form also proves that words in a review shows diminishing returns to helpfulness.
+Experience Goods somewhat deviates from the results of Search Goods.
+There is a weak positive relationship between Review Length and Perceived Helpfulness (0.021, p \< 0.01).
+However, this positive relationship quickly turns to negative for higher ratings because of the presence of the interaction term between Review Length and Review Extremity (-0.015, p \< 0.001).
+For lower ratings Hypothesis 2 is fully supported but as the Review Extremity increases this support weakens.
+
+For both good types the interaction effects are significantly negative (-0.043, p \< 0.001 ; -0.015, p \< 0.001).
+This means that as Review Extremity increases longer reviews become less helpful, supporting the idea of people spending more time evaluating negative information because it takes more time to read a longer review.
+However, there are nuances too.
+For Search Goods, the effect of the Review Length is always positive whether or not Review Extremity is low or high.
+On the contrary, for Experience Goods, after some point of Review Extremity longer reviews become "unhelpful" because the sign of the Review Length turns to negative.
+In this case Hypothesis 3 is supported wholly for Search Goods and somewhat supported for Experience Goods.
+
+Hypothesis 4 is fully supported. Recent reviews seem to be more helpful for both good types (0.029, p \< 0.001 ; 0.038, p \< 0.001).
+
+The results for Negative Word Proportion is quite interesting because it shows different characteristics for different product types.
+As expected, for Search Goods, Negative Word Proportion has a significant positive coefficient (0.061, p \< 0.001).
+The presence of negative words indeed increases the perceived helpfulness.
+Contrary to this, there is a negative relationship between negative words and perceived helpfulness for Experience Goods (-0.021, p \< 0.001).
+Hypothesis 5 is only supported for Search Goods and not supported for Experience Goods.
+
+Positive Word Proportion is only significant for Search Goods (-0.056, p \< 0.001).
+The presence of positive words has a negative effect on perceived helpfulness just as expected.
+The coefficient for Experience Goods show the expected sign too but it is statistically insignificant (-0.007, p \> 0.5).
+With this result, Hypothesis 6 is again only supported for Search Goods and not supported for Experience Goods.
+
+The result of the only control variable should also be reported.
+It seems that total amount of votes that a review gets has a negative relationship (-0.157, p \< 0.001) with perceived helpfulness for Search Goods.
+The opposite is true for Experience Goods (0.123, p \< 0.001).
 

### 2022-06-10 Paper.Rmd
sending it to the danışman.

@@
                       fig.align = "center",
-                      fig.width = 7,
+                      fig.width = 8,
+                      fig.height = 4,
                       echo = FALSE)
@@
 # Literature Review
-
--   mention moderating effects of product type for every variable
 
@@
 
+The classification of Experience and Search goods plays a moderating role in the literature [@mudambi2010; @sun2019; @baek2012; @lee2016].
+Some of these studies showed that Review Length has a greater effects for search products than experience products [@mudambi2010; @baek2012; @lee2016].
+These findings suggest that search goods can be evaluated in a more objective way than experience goods.
+The moderating effect of product type on Review Extremity, on the contrary, is disputable.
+Mudambi (2010) @mudambi2010 showed that moderate reviews are more helpful for experience products than search products.
+Baek (2012) @baek2012 and Lee (2016) @lee2016 had the opposite results which indicated that more extreme reviews (negative or positive) is more helpful more search goods than experience goods.
+
 # Theoretical Framework
@@
 
--   extend this later and try to connect to the methodology
+-   could be extended later
 
@@
 
--   might explain why negative reviews arent that helpful for movies
+-   might explain that goods within the same group can show different characteristics
 
@@
 
--   needs to be connected to the method
+-   should be extended a little bit more
 
@@
 It is nearly impossible to evaluate a movie before watching it.
-Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective perspectives (writing, production quality etc.).
-There are also numerous studies that analyzed movies as experience goods[@nelson1970] ; @liu2014; @ghose2006; @baek2012; @lee2016].
+Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (writing, production quality etc.).
+There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].
 
@@
 Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019].
-Therefore, we collected search goods data from BestBuy.
+Therefore, search goods data was collected from BestBuy.
 
@@
 However, in the data there are many reviews that were never voted.
-To make sure that we are analyzing reviews that were actually read by people, we set a threshold for Total Reviews as five.
-In other words, we removed reviews that have less than 5 Total Votes [@choi2020; @baek2012].
-At the very end, we were left with 15,024 observations for experience goods and 8,042 observations for search goods.
+To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five.
+In other words, reviews that had less than 5 Total Votes were removed from the analysis data[@choi2020; @baek2012].
+At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods.
 It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times.
-
-It should be noted that in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names.
+Most of the search product reviews aren't getting voted and even maybe they aren't getting read at all.
+This might support the idea that people form more homogeneous opinions about search goods @hong2014.
+Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information.
+On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times.
+This might be because people form heterogeneous opinions about experience goods @hong2014.
+
+As a data cleaning note, in IMDB data there were cases (20 observations to be exact) where the same reviews were written by different user names.
 All duplicates along with original reviews were removed because the reviews had different helpfulness ratios.
@@
 
-As an outline, firstly the dependent variable is going to be introduced in a univariate manner and then independent variables are going to come into the picture both in univariate and bivariate way.
+In this section there will be univariate visualizations of all variables and bivariate visualizations of independent variables against the dependent variable.
+
+-   elaborate more on the importance of EDA here
 
@@
 The storage space of a phone might be small or CPU of a laptop might not be fast as expected.
-Thus, one good review is be enough to reveal the quality of a product.
+Thus, one good review is enough to reveal the quality of a product.
 I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search).
 In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%.
-This is because evaluation process of movies is rather subjective.
+This might be because evaluation process of movies is rather subjective.
 One person might not like Spider-Man: Homecoming and another would love it.
-
--   you can elaborate a little bit more about how movies cant be evaluated objectively
+This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.
 
@@
 
-```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods.", fig.height=7}
+```{r Search-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Search Goods."}
 p1 <- search_goods %>% 
@@
   geom_bar(fill = "steelblue")+
-  labs(y = "Count", x = NULL)
+  labs(y = "Count", x = "Review Rating")
 
@@
 
-plots <-  p1 / p2
+plots <-  p1 + p2
 
@@
 
-```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods.", fig.height=7}
+```{r Experience-Rating, fig.cap="The Distribution(A) and the Scatter Plot(B) of Review Rating for Experience Goods."}
 p1 <- movies_data %>% 
@@
   scale_x_continuous(n.breaks = 10)+
-  labs(y = "Count", x = NULL)
+  labs(y = "Count", x = "Review Rating")
 
@@
 For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).
-
--   you might add confidence interval for mean on plots.
 
@@
 
--   maybe add more framework for experience goods and no relationship
-
-```{r Search-Length, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
+```{r Search-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Search Goods and respective logarithmic transformations (B), (D)"}
 p1 <- search_goods %>% 
@@
 
-plots <-  p1 / p1_log / p2 / p2_log
+plots <-  (p1 + p1_log) / (p2 + p2_log)
 
@@
 
-```{r Experience-Length, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
+```{r Experience-Length, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Length for Experience Goods and respective logarithmic transformations (B), (D)"}
 p1 <- movies_data %>% 
@@
 
-1.  The first review date for a particular brand and model of a product (movie, phone, laptop, tv) was taken.
+1.  The first review date for a particular brand and model of a product (Movie, Phone, Laptop, TV) was taken.
 2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and model resulting an integer variable representing days.
@@
 
-```{r Search-Freshness, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
+```{r Search-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Search Goods and respective logarithmic transformations (B), (D)"}
 p1 <- search_goods %>% 
@@
 
-plots <- p1 / p1_log / p2 / p2_log
+plots <- (p1 + p1_log) / (p2 + p2_log)
 
@@
 
-```{r Experience-Freshness, fig.height=8, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
+```{r Experience-Freshness, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Review Freshness for Experience Goods and respective logarithmic transformations (B), (D)"}
 p1 <- movies_data %>% 
@@
 In this case, negative words lexicon was used in order to engineer this variable.
+A sample of negative words from the lexicon can be observed below.
+
+*"caricature, superstition, compost, misconception, grief, violation, scrub, omen, erratic, porcupine"*
 
 $$
-Negative\ Word \% = \frac{Number\ of\ Matched\ Negative\ Word}{Total\ Words\ in\ Review} 
+Negative\ Word \% = \frac{Number\ of\ Matched\ Negative\ Word}{Total\ Words\ in\ the\ Review} 
 $$
@@
 3.  Matches were counted and divided by the total number of words with the respective review then multiplied by 100 in order to make regression results more interpretable.
-4.  Logarithmic transformation was applied in order to scale the variable in a better way.
+4.  Logarithmic transformation was applied in order to scale the variable in a more normalized way.
 
@@
 
-On Figure \@ref(fig:Search-Neg) (B), non-linear relationship between perceived helpfulness and the proportion of negative words can be observed search goods.
-It should be kept in mind that as the proportion increases the sample size decreases.
-This might mean that any statistical test for non-linearity would have low power.
+On Figure \@ref(fig:Search-Neg) (B), non-linear relationship between perceived helpfulness and the proportion of negative words can be observed for search goods.
+This might suggest that too much negative information might fall into slander rather than informing the customer about the potential risks of the product.
 On the other hand, somewhat weak negative linear relationship between perceived helpfulness and proportion of negative words can be seen for experience goods on Figure \@ref(fig:Experience-Neg) (B).
 
--   need citation here!
-
-```{r Search-Neg, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
+```{r Search-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
 p1 <- search_goods %>% 
@@
   scale_x_continuous(n.breaks = 8)+
-  labs(y = NULL, x = NULL)
+  labs(y = "Count", x = "Log10(Proportion of Negative Words)")
 
@@
 
-plots <- p1 / p2
+plots <- p1 + p2
 
@@
 
-```{r Experience-Neg, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
+```{r Experience-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
 p1 <- movies_data %>% 
@@
 #### Proportion of Positive Words
+
+$$
+Positive\ Word \% = \frac{Number\ of\ Matched\ Positive\ Word}{Total\ Words\ in\ the\ Review} 
+$$
 
@@
 Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).
+
+*A sample of positive words from EmoLex:*
+
+*"covenant, jovial, score, foundation, affirmation, reliable, mending, garden, luxurious, wit"*
 
@@
 
--   needs sth from literature here as well
-
-```{r Search-Pos, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
+```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
 p1 <- search_goods %>% 
@@
 
-```{r Experience-Pos, fig.height=7, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
+```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
 p1 <- movies_data %>% 
@@
 
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\
+--- --- --- ---
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+--- --- --- ---
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+--- --- --- ---
+
 # References

### 2022-08-28 Paper.Rmd
jrny conts
it does

@@
 link-citations: yes
-csl: ieee.csl
 output:
@@
 One of the positive perks is Online Customer Reviews (OCR).
-Online Customer Reviews come in the form of electronic word-of-mouth @dellarocas2003 and can be defined as "*peer-generated product evaluations posted on company or third party websites*" @mudambi2010.
+Online Customer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010].
 OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].
@@
 This information acquiring process is costly.
-Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods @nelson1970 .
+Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] .
 Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
@@
 Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews.
-Additionally, not all reviews have the same informativeness level @pan2011.
+Additionally, not all reviews have the same informativeness level [@pan2011].
 Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost.
-To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" @mudambi2010.
-
-Since OCR don't share the same level of informativeness and usefulness @pan2011, most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
+To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].
+
+Since OCR don't share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
 On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button.
-In this paper, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable @ahmad2015.
+In this study, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].
 
 The research on perceived helpfulness is still growing.
-In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature @hunter1991.
+In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature [@hunter1991].
 In this case, the study on perceived helpfulness is not an exception.
 Because of this reason, more empirical studies on perceived helpfulness are required.
-This paper aims to add one more perspective to growing literature of customer reviews and review helpfulness.
+This paper aims to add one more perspective to the growing literature of customer reviews and review helpfulness.
 
@@
 Namely, IMDB and BestBuy.
-The data was scrapped with Selenium Webdriver for Python @python3.
+The data was scrapped with Selenium Webdriver for Python [@python3].
 Over 400,000 reviews and their meta data were gathered initially.
 After the data transformation process the final sample size was over 23,000.
-
--   Briefly talk about the results.
-
--   Outline the paper
+Then this data was subjected to empirical tests.
+It was found out that consumers usually find extreme reviews more helpful than neutral ones.
+Furthermore, consumers prefer longer reviews when reviews are rated negatively.
+On the contrast, positive reviews with fewer words were deemed more helpful by readers on the average.
+These effects were further moderated by product types, namely, Search and Experience goods.
+
+The plan of this study is outlined as the following.
+In the next section, the literature on the subject of Review Helpfulness is going to be presented.
+In the third section, the related theories which would make the understanding of the consumer behavior and review helpfulness will be laid out.
+Next, the data and the research methodology are going to be introduced.
+The results will be shared in the fifth section.
+In the last section the results are going to be discussed and the study is going to be concluded.
 
@@
 The other branch is concerned with rather behavioral or psychological outcomes and focuses on perceived helpfulness only.
-Of course, the boundary between these two branches are somewhat blurry and same independent variables were used to explain both helpfulness and sales.
+The boundary between these two branches are somewhat blurry and the same independent variables were used to explain both helpfulness and sales.
 Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales.
@@
 Thus, these two branches are inter-connected with each other.
-This paper tries to understand behavioral aspect.
+This paper tries to understand behavioral aspect of the review helpfulness rather than its effects on sales.
 
 Many independent variables and their relationship between perceived helpfulness were examined by researchers.
-Hong et al.
-(2017) @hong2017 groups these independent variables into two chunks.
+@hong2017 groups these independent variables into two chunks.
 The first group is reviewer-related predictors.
-Variables within this group tries to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.).
+Variables within this group try to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.).
 [@sun2019; @ghose2011].
 The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018].
-Ghose et al.
-(2011) @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones.
-The choice of the variables is of course heavily dependent on the data itself.
-In this paper, only review-related predictors were examined.
+@ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones.
+The choice of the variables is heavily dependent on the data itself.
+In my paper, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.
 
@@
 This is usually the star rating on a 1-5 or 1-10 scale and resembles the evaluation of the reviewer for a given product.
-It's effect on perceived helpfulness is rather divergent in the literature.
+Its effect on perceived helpfulness is rather divergent in the literature.
 A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness.
@@
 Review Age is an indicator of how long the time passed after a review published on a web site.
-On some papers the opposite of Review Age, Review Freshness could be employed as well.
+On some papers the opposite of Review Age, Review Freshness (Recency) could be employed as well.
 Different effects on perceived helpfulness were also observed by researchers.
@@
 They are usually different than Review Extremity.
-In most cases Review Extremity and Review Sentiment (Valence) don't match @zhang2011.
-Both Baek et al.
-(2012) @baek2012 and Kuan et al.
-(2015) @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness.
-The relationship between the proportion of positive words and perceived helpfulness was found to be negative @kuan2015.
+In most cases Review Extremity and Review Sentiment (Valence) don't match [@zhang2011].
+@baek2012 and @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness.
+The relationship between the proportion of positive words and perceived helpfulness was found to be negative [@kuan2015].
 
 The classification of Experience and Search goods plays a moderating role in the literature [@mudambi2010; @sun2019; @baek2012; @lee2016].
-Some of these studies showed that Review Length has a greater effects for search products than experience products [@mudambi2010; @baek2012; @lee2016].
+Some of these studies showed that Review Length has a greater effect for search products than experience products [@mudambi2010; @baek2012; @lee2016].
 These findings suggest that search goods can be evaluated in a more objective way than experience goods.
-The moderating effect of product type on Review Extremity, on the contrary, is disputable.
-Mudambi (2010) @mudambi2010 showed that moderate reviews are more helpful for experience products than search products.
-Baek (2012) @baek2012 and Lee (2016) @lee2016 had the opposite results which indicated that more extreme reviews (negative or positive) is more helpful more search goods than experience goods.
+There is also moderating effect of product type on Review Extremity.
+@mudambi2010 showed that moderate reviews are more helpful for experience products than search products.
+@baek2012 and @lee2016 had the results which indicated that more extreme reviews (negative or positive) is much more helpful for search goods than experience goods.
+
+Many different types of research methodologies were employed in the literature of the Review Helpfulness.
+To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014].
+Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020].
+Ordinary Least Squares were also used as a main empirical methodology in some papers [@liu2014; @ghose2006; @lee2016].
+Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012].
+Some other studies employed Multi-Level Regression models in order to deal with potential biases [@ghose2011; @wu2021; @kuan2015].
+In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011].
+Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014].
+One paper attacked the problem of the review helpfulness with three methods, namely, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].
 
@@
 
-Nelson (1970) [@nelson1970] differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
+@nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
 Search Attributes are the qualities that can be assessed before purchase.
@@
 To explain it in a more generalized way, let's also define what "search" is.
-Nelson (1970) [@nelson1970] defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
+@nelson1970 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
 People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
@@
 For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it.
-Even though a car has experience attributes, with this logic it is considered as a search good @klein1998.
+Even though a car has experience attributes, with this logic it is considered as a search good [@klein1998].
 
@@
 Losing 100\$ is psychologically much more impactful than finding 100\$.
-This behavior is best explained by "loss aversion" from Behavioral Economics.
+This behavior is best explained in "loss aversion" from behavioral economics.
 [@kahneman1979; @schindler2017].
-Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses @herr1991.
-
-Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than positive ones.
+Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].
+
+Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than the positive ones.
 --, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones.
@@
 
-# Research Methodology
+# The Data and Research Methodology
 
@@
 
-The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 @python3.
+The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 [@python3].
 The scraper got the customer reviews from IMDB and BestBuy.
@@
 
-BestBuy is a very big electronics retailer and because of this the website offers a sizable number of OCR for search goods.
+BestBuy is a very big electronics retailer and this is why the website offers a sizable number of OCR for search goods.
 Contrary to experience goods, search goods usually have more objectively quantifiable traits.
@@
 From IMDB reviews of 22 movies were collected as experience goods.
-In total 22 movies account for 31,863 reviews.
+In total, 22 movies account for 31,863 reviews.
 From BestBuy, total of 383,357 reviews were collected as search goods.
@@
 To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five.
-In other words, reviews that had less than 5 Total Votes were removed from the analysis data[@choi2020; @baek2012].
+In other words, reviews that had less than 5 Total Votes were removed from the analysis data [@choi2020; @baek2012].
 At the very end, the analysis data was consisted of 15,024 observations for experience goods and 8,042 observations for search goods.
 It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times.
-Most of the search product reviews aren't getting voted and even maybe they aren't getting read at all.
-This might support the idea that people form more homogeneous opinions about search goods @hong2014.
+Most of the search product reviews aren't getting voted and even possible that they aren't getting read at all.
+This might support the idea that people form more homogeneous opinions about search goods [@hong2014].
 Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information.
 On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times.
-This might be because people form heterogeneous opinions about experience goods @hong2014.
+This might be because people form heterogeneous opinions about experience goods [@hong2014].
 
@@
 
-Hong et al.
-(2014) [@hong2014; @sun2019] states that consumers likely to form homogeneous opinions about search goods.
+@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019].
 On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods.
@@
 For both search and experience goods the bi-modality of the distributions can be observed on Figure \@ref(fig:Search-Rating) (A) and Figure \@ref(fig:Experience-Rating) (A) respectively.
-Hu et al.
 @hu2006 also pointed out a similar distribution concerning Online Product Reviews.
@@
 This means that reviews become less prevalent as they get longer.
-This might suggest logarithmic transformation which can increase the model fit.
+This might suggest logarithmic transformation can increase the model fit.
 For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).
@@
 For Search goods on Figure \@ref(fig:Search-Length) (C) there is a clear positive relationship [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020].
-However, this positive relationship appears to stop at a threshold[@schindler2012; @huang2015; @baek2012; @kuan2015; @eslami2018].
+However, this positive relationship appears to stop at a threshold [@schindler2012; @huang2015; @baek2012; @kuan2015; @eslami2018].
 With this in mind, logarithmic transformation might make more sense (see Figure \@ref(fig:Search-Length) (D)) for modelling purposes.
@@
 
-Negative words were derived by using NRC Word-Emotion Association Lexicon @Mohammad13.
+Negative words were derived by using NRC Word-Emotion Association Lexicon [@Mohammad13].
 A lexicon is basically a dictionary of words.
@@
 
+The relatively high positive/negative correlation between the Review Rating and Positive/Negative word proportions might give a hint about the usefulness of the lexicon.
+As the Review Rating gets higher the review contains more positive words and, on the other hand, low rated reviews have more negative words in them.
+This makes sense intuitively.
+
 ```{r Correlations, fig.cap="Correlations between Independent Variables.", fig.height=8}
+
 p1 <- search_goods %>% 
-  select(Rating, Word_Count, Freshness, positive, negative, Total_Vote) %>% 
-  rename(Proportion_Positive = positive) %>% 
-  rename(Proportion_Negative = negative) %>% 
-  mutate(Word_Count = log10(Word_Count),
-         Total_Vote = log10(Total_Vote)) %>% 
+  select("Review Rating" = Rating,
+         "Review Length" = Word_Count, Freshness,
+        "Positive Proportion" = positive,
+        "Negative Proportion" = negative,
+        "Total Votes" = Total_Vote) %>% 
+  mutate(`Review Length` = log10(`Review Length`),
+         `Total Votes` = log10(`Total Votes`)) %>% 
   ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
@@
 p2 <- movies_data %>% 
-  select(Rating, Word_Count, Freshness, positive, negative, Total_Vote) %>% 
-  rename(Proportion_Positive = positive) %>% 
-  rename(Proportion_Negative = negative) %>% 
-  mutate(Word_Count = log10(Word_Count),
-         Total_Vote = log10(Total_Vote)) %>% 
+  select("Review Rating" = Rating,
+         "Review Length" = Word_Count, Freshness,
+        "Positive Proportion" = positive,
+        "Negative Proportion" = negative,
+        "Total Votes" = Total_Vote) %>% 
+  mutate(`Review Length` = log10(`Review Length`),
+         `Total Votes` = log10(`Total Votes`)) %>% 
   ggcorr(label = TRUE, hjust = 0.75, nbreaks = 5,low = "steelblue", mid = "grey95",
@@
 
-Korfiatis et al.
-(2012) @korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers.
+@korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers.
 This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006].
 As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful.
-This extremeness has more objective nature for Search Goods since there are more ways to express pleasantness or unpleasantness for a particular product.
+This extremeness has more objective nature for Search Goods since there are fewer ways to express pleasantness or unpleasantness for a particular product.
 For instance a bad design in a laptop might cause fans to make much more noise than they should normally do.
@@
 For example, a reviewer might find a movie "childish" and give it one star, the other might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness.
-Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process @hoch1989.
+Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989].
 In other words, prior expectations play a bigger role in decision making process for experience goods.
@@
 In \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods.
-Furthermore, people tend to have homogeneous opinions about Search Goods @hong2014 .
+Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014].
 This might mean that information cues are much more uniform for Search Goods.
@@
 Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015].
-On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions @hong2014.
+On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014].
 This means that movie reviews are much more subjective by nature.
@@
 Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses.
-Guo et al.
-(2019) @guo2019 found out that people spent more time when evaluating negative reviews.
+@guo2019 found out that people spent more time when evaluating negative reviews.
 This may suggest a linear interaction between Review Extremity and Review Length.
@@
 
-*H5: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
+*H5: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*
+
+\
 *H6: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*
@@
 First of all, dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1.
-The second reason as stated by Mudambi (2010) @mudambi2010 is the potential selection bias in the sample.
+The second reason as stated by @mudambi2010 is the potential selection bias in the sample.
 Unfortunately, it is not possible to know how many people read a particular review.
@@
 
---- --- --- ---
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
---- --- --- ---
+------------------------------------------------------------------------
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+------------------------------------------------------------------------
 

### 2022-08-29 Paper.Rmd
it never ends

@@
 One paper attacked the problem of the review helpfulness with three methods, namely, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].
+
+Any website which offers online reviews for products were used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data.
+They have their respective APIs and on top of that, it is relatively easier to scrape both websites.
+Additionally, both websites offer product reviews for a numerous different types of products.
+Amazon is a huge e-retailer and offers a wide range of items.
+IMDB is a home for both critic and user reviews of Movies and TV Shows.
+In some other studies local equivalents of Amazon was used as well.
+[@sun2019].
+@cao2011 used data from CNET Download.com which is a software distributor.
 
@@
 files <- dir()
-
 files <- files[str_detect(files, "movie_.+")]
@@
 
-## Removing All the Duplicated Reviews including the original since same reviews were written by differend user names
+## Removing All the Duplicated Reviews including the originals since same reviews were written by differend user names
 movies_data <- movies_data %>% 
@@
 
-## Words
+# Words
+## Creating Review ID
 movies_data <- movies_data %>% 
@@
 files <- files[str_detect(dir(), "all_laptop_reviews.+")]
+
 laptop_data <- map_dfr(files, read_csv, show_col_types = FALSE)
+
 ### Removing replicates that I couldn't detect earlier
@@
 ## Word Counts
-
+### Creating Review IDs
 search_goods <- search_goods %>% 
@@
 ## Freshness (Timeline)
-
 search_goods <- search_goods %>% 
@@
 
-*"caricature, superstition, compost, misconception, grief, violation, scrub, omen, erratic, porcupine"*
+> *"caricature, superstition, compost, misconception, grief, violation, scrub, omen, erratic, porcupine"*
 
@@
 
-*"covenant, jovial, score, foundation, affirmation, reliable, mending, garden, luxurious, wit"*
+> *"covenant, jovial, score, foundation, affirmation, reliable, mending, garden, luxurious, wit"*
 
@@
 
-## Hypothesis Development and Method
+## Hypothesis Development
 
@@
 
-*H1: There is a U-Shaped relationship between Perceived Helpfulness and Review Rating. This U-Shape is stronger/weaker for Search/Experience Goods.*
+***H1**: There is a U-Shaped relationship between Perceived Helpfulness and Review Rating. This U-Shape is stronger/weaker for Search/Experience Goods.*
 
@@
 
-*H2: There is a positive relationship between logarithm of Review Length and Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.
+***H2**: There is a positive relationship between logarithm of Review Length and Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.
 
@@
 
-*H3: There is a negative linear interaction effect between Review Rating and the logarithm of the Review Length for both Search and Experience Goods.*
+***H3**: There is a negative linear interaction effect between Review Rating and the logarithm of the Review Length for both Search and Experience Goods.*
 
@@
 
-*H4: There is a positive relationship between Perceived Helpfulness and Freshness of a Review for both Search and Experience Goods.*
+***H4**: There is a positive relationship between Perceived Helpfulness and Freshness of a Review for both Search and Experience Goods.*
 
@@
 
-*H5: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*
-
-\
-*H6: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*
-
-Tobit Regression is selected as the method because of three reasons.
-First of all, dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1.
+***H5**: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
+***H6**: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*
+
+## Research Methodology
+
+Tobit model is also named as Censored Regression model.
+Censored data arises when there exist lower (censored from below) or upper (censored from above) or both lower and upper boundaries for the dependent variable.
+This type of data is fairly prevalent in Economics.
+For instance, in consumer economics there is no such thing as "negative consumption" or in labor economics there is no such thing as "negative work hours".
+Furthermore, there might be cases where some really high values could be recorded as "50,000 or more" because of the data collection design.
+Ordinary Least Squares can't take account of the censored observations in the data because it extrapolates lower and upper ends when it fits the model and this leads biased estimations.
+
+Tobit regression approaches censored dependent variable problem from two angles.
+In a sense Tobit regression could be considered as the summation of Probit regression and Truncated regression.
+The probit side considers if a particular observation is above or below the given limit.
+If the observation, for example, is below the lower limit then it must be equal to the lower limit.
+If it is higher than the lower limit the problem turns to a normal regression.
+In this case, Perceived Helpfulness can be expressed such as this:
+
+$$
+y=
+\begin{cases}
+  0   & \text{if  $ \ y^* \le0$} \\
+  y^* & \text{if $ \ 0< y^* <1$} \\
+  1   & \text{if $ \ y^* \ge 1$}
+\end{cases}
+$$
+
+Tobit Regression is selected as the analysis method because of three reasons.
+First of all, the dependent variable, perceived helpfulness, is defined in a continuous range from 0 to 1 since perceived helpfulness is a percentage as mentioned above.
 The second reason as stated by @mudambi2010 is the potential selection bias in the sample.
 Unfortunately, it is not possible to know how many people read a particular review.
-Neither BestBuy nor IMDB discloses this information.
+Neither BestBuy nor IMDB disclose this information.
 Because of this, being included in a sample could be correlated with independent variables.
@@
 
-\
---- --- --- ---
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-------------------------------------------------------------------------
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-------------------------------------------------------------------------
-
 # References

### 2022-09-04 Paper.Rmd
this has to be the final outline

@@
 
-Any website which offers online reviews for products were used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data.
+Any website which offers online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data.
 They have their respective APIs and on top of that, it is relatively easier to scrape both websites.
@@
 
+There might be variety reasons why there are some conflicting results in the literature.
+First of all, many different data sources were used in the studies.
+Even in the same data source, for instance Amazon, there exist a wide range of products with different brands.
+Different sub-groups of products can receive different feedbacks.
+This might increase the potential noise in the data, leading conflicting results.
+Secondly, many different research designs and research methodologies were employed.
+In these different research designs different independent and control variables were used because the data at the hand may allow for different sets of variables.
+Lastly, there is no established theory of review helpfulness.
+This means that studies are rather unorganized and researchers are usually inclining towards their own domain of expertise when it comes to explaining review helpfulness.
+
 # Theoretical Framework
@@
 --[@rozin2001; @sen2007; @eslami2018].
+
+## Some other theory
 
@@
 
-# Discussion and Conclusion
+# Discussion
 
@@
 
+# Conclusion
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
+\*\*WORK IN PROGRESS\*\*
+
 # References

### 2022-09-05 Paper.Rmd
laf salatası begins

@@
 
--   could be extended later
-
-@nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
+-   I am extending it atm
+
+Relaxing the assumption that consumers have perfect information about the products on the market raises the problem of information acquisition for consumers.
+Getting the complete information about products is important because economic agents want to maximize their utility by finding the best good on the market.
+The complete information is the information about both the prices and quality levels of the goods which are available on the market.
+Acquiring the information of the quality of a product is harder than getting the information about its price.
+To explain, a consumer can check the price list of laptops and have an idea about maximum and minimum prices but getting the information about a laptop's technical components or a brand's support for its products is a lot more effort taking and costly.
+
+In order to solve this problem @nelson1970 differentiated goods based on their search and experience attributes [@nelson1974economic; @nelson1974; @nelson1981].
 Search Attributes are the qualities that can be assessed before purchase.
-On the contrary, Experience Attributes can only be assessed by using the product itself, in other words evaluation is only possible after purchase.
+On the contrary, Experience Attributes can only be assessed by using the product itself, in other words, evaluation is only possible after purchase.
 A single good can have both search and experience attributes.
 Depending on its dominant attributes the good can be classified as Search or Experience.
+@darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after consumption.
+
+-   you were about to define what search is and when it is not effective
+
 A product's Total Cost consists of both Search Cost and Product Cost.
@@
 ## Some other theory
+
+## some other
 

### 2022-09-07 Paper.Rmd
extend search/exp framework

@@
 
--   I am extending it atm
-
 Relaxing the assumption that consumers have perfect information about the products on the market raises the problem of information acquisition for consumers.
@@
 Depending on its dominant attributes the good can be classified as Search or Experience.
-@darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after consumption.
-
--   you were about to define what search is and when it is not effective
-
-A product's Total Cost consists of both Search Cost and Product Cost.
-This Search Cost is higher for Experience Goods, in other words, information search is costlier for Experience Goods than Search Goods.
-
-To explain it in a more generalized way, let's also define what "search" is.
-@nelson1970 defines search as "The most obvious procedure available to the consumer in obtaining information about price or quality is search".
-People will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
-This is why search is costlier for Experience Goods.
-For instance, getting information about a car (test drive, guides on the web etc.) is less costly than actually buying it.
-Even though a car has experience attributes, with this logic it is considered as a search good [@klein1998].
-
--   might explain that goods within the same group can show different characteristics
+@darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after the consumption.
+Though, Credence goods won't be discussed any further in this study.
+
+Consumers can choose from two different strategies when they want to acquire more information about products.
+Consumers "search" in order to get information about a product assuming that they perfectly know where they can obtain the knowledge.
+@nelson1970 defines the search process as *"The most obvious procedure available to the consumer in obtaining information about price or quality is search"*.
+The search process is complete when consumers inspect the option and that inspection happens before the purchase.
+Contrary to the search process, consumer may choose to "experience" the product.
+The consumer follows this strategy when the search for information is either inappropriate, inefficient or costly compared to just experiencing the good.
+This is true for cheap goods especially.
+For instance, in order to find out the best chocolate in the market it's best for the consumer to buy every other brand available and taste them.
+Thus, consumers will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
+This is why search is costlier for Experience goods.
+Therefore, the kind of strategy that a consumer chooses depends on the product's Search or Experience attributes and how dominant these attributes are.
+
+@nelson1970 also states that consumers can use other consumers' experiences in their search processes.
+The information about a certain good is usually acquired in the form of "word-of"mouth" in this kind of search process.
+This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search".
+@klein1998 discusses that experience sharing becomes easier with the increasing usage of the internet.
+Because experiences about products can be shared much more easily on the internet, consumers' pre-purchase behavior might change accordingly.
+The reason of this is that internet decreases search costs considerably.
+Furthermore, the potential consumer may engage in "vicarious learning" where he/she gets indirect usage experience through the experiences of other consumers in the search process [@murray1991].
+
+Ultimately, to put the theory in a more generalized way, a product's Total Cost consists of both Search Cost and Product Cost.
+This Search Cost is higher for Experience goods, in other words, information search is costlier for Experience goods than Search goods.
+In the consumer's perspective, to make the search viable, the marginal benefit of an additional search must be grater than the marginal cost of the additional search.
+The increasing use of internet decreases the search costs.
+Because of the decreased search costs, the consumer may undertake more search processes and this might change how people perceive good types, in other words, internet and virtual experience sharing can convert some Experience goods to Search goods [@klein1998].
 

### 2022-09-10 Paper.Rmd
most of the nbt and loss aversion done

@@
 
--   should be extended a little bit more
+-   expand NBT a little bit more
+
+Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones.
+Someone else's hair in one's meal has the potential of ruining the whole meal.
+On the contrary a plate of hair won't turn to a delicious meal just because there is a slice of a delicious pizza on top of the hair.
+@rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects.
+Namely, Negative Potency, Steeper Negative Gradients, Negative Dominance and Negative differentiation [@rozin2001; @sen2007; @eslami2018].
+
+**Negative Potency** defends that the exact opposite of something positive carries heavier weight.
+In other words, negative events are much more impactful than their exact positive counterparts.
+For instance, losing 100\$ could have a harder psychological effect on a person than that particular person is gaining 100\$.
+Loss Aversion [@kahneman1979; @tversky1991] is the phenomenon where the Negative Potency can be observed the best.
+People risk more/less when they are losing/gaining something.
+The behavior can be explained by the Endowment Effect [@kahneman1990].
+Endowment effect occurs because people usually over-estimate the value of their belongings, for example a pencil.
+However, they would have under-valued the same pencil if the item didn't belong to them.
+The reason to this behavior is that the dis-utility of losing that pencil is greater than the utility of acquring the same pencil.
+
+**Greater Steepness of Negative Gradients** simply implies that the marginal psychological effect of a negative entity is much more higher than a positive one.
+In other words, negative things cause more negativity as the time goes on.
+
+**Negativity Dominance** asserts that a balanced mixture of positive and negative evaluations creates a perception of negativity.
+This means that negative entities have higher weight than positive entities.
+This is apparent in religions.
+For most of the religions being a good and pious person takes time, demands upmost care.
+However, tainting this image is very easy with certain actions such as murder or pre-martial intercourse.
+
+**Greater Negative Differentiation** discusses the possibility that human cognition is fine-tuned to negative entities because being aware of negative stimuli might correlate with survival in the process of the evolution.
+As a consequence, the vocabulary that reflects and describes the state of negativeness is much more wider than its counterpart positiveness.
+[@peeters1971].
+
+-   talk about loss aversion in detail
+
+Prospect Theory (Loss Aversion) criticizes Expected Utility Theory by introducing the thought that Expected Utility Theory is insufficient explaining the decision making behavior of economic agents who are under risk.
+In Expected Utility Theory outcomes are weighted by their probabilities but Prospect Theory discusses that people give more weight to the outcomes that they know for sure will happen.
+This is called *certainty effect* [@kahneman1979].
 
@@
 
-Negativity Bias Theorem has four main aspects, namely, higher negative potency -- Negative signals have more impact on people than the positive ones.
---, steeper negative gradients -- Negativity of negatives events grows faster in space and time than positive ones.
---, higher negative dominance -- A combination of equally negative and positive cues results in more negative impressions.
---, and various negative differentiations -- Negative cues produce more diverse individual responses than positive ones.
---[@rozin2001; @sen2007; @eslami2018].
-
 ## Some other theory
-
-## some other
 
@@
 Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low.
-And when a review is longer it is more helpful for negatively rated reviews than positively rated reviews.
+And when a review is longer it is evaluated as more helpful for negatively rated reviews than positively rated reviews.
 In this case, it is hypothesized that:

### 2022-09-13 Paper.Rmd
extend nbt and loss aversion

@@
 
--   expand NBT a little bit more
-
 Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones.
@@
 @rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects.
-Namely, Negative Potency, Steeper Negative Gradients, Negative Dominance and Negative differentiation [@rozin2001; @sen2007; @eslami2018].
+Namely, Negative Potency, Steeper Negative Gradients, Negative Dominance and Negative Differentiation [@rozin2001; @sen2007; @eslami2018].
+Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].
 
@@
 People risk more/less when they are losing/gaining something.
-The behavior can be explained by the Endowment Effect [@kahneman1990].
+This behavior can be explained by the Endowment Effect [@kahneman1990].
 Endowment effect occurs because people usually over-estimate the value of their belongings, for example a pencil.
 However, they would have under-valued the same pencil if the item didn't belong to them.
-The reason to this behavior is that the dis-utility of losing that pencil is greater than the utility of acquring the same pencil.
+The reason to this behavior is that the dis-utility of losing that pencil is greater than the utility of acquiring the same pencil.
 
@@
 This is apparent in religions.
-For most of the religions being a good and pious person takes time, demands upmost care.
+For most of the religions being a good and pious person takes time, demands utmost care.
 However, tainting this image is very easy with certain actions such as murder or pre-martial intercourse.
@@
 
--   talk about loss aversion in detail
-
 Prospect Theory (Loss Aversion) criticizes Expected Utility Theory by introducing the thought that Expected Utility Theory is insufficient explaining the decision making behavior of economic agents who are under risk.
-In Expected Utility Theory outcomes are weighted by their probabilities but Prospect Theory discusses that people give more weight to the outcomes that they know for sure will happen.
+In Expected Utility Theory outcomes are weighted by their probabilities but Prospect Theory discusses that people dynamically give more or less weight to the outcomes depending on if it is a loss or a gain.
 This is called *certainty effect* [@kahneman1979].
-
-Humans tend to care about losses more than same amount of gains.
-Losing 100\$ is psychologically much more impactful than finding 100\$.
-This behavior is best explained in "loss aversion" from behavioral economics.
-[@kahneman1979; @schindler2017].
-Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].
+The Certainty Effect causes people to behave differently whether they are going to lose or gain something.
+In the positive domain, people will prefer a small amount of a certain gain over a big gain which is merely probable (risk averse).
+On the contrary, in the negative domain, people will have a preference towards a big loss which is merely probable over a small certain loss (risk seeking).
+
+Since the cognitive abilities of humans are limited they tend to focus on what is crucial to them.
+Therefore, in the information processing context and because of the existence of the negativity bias, it could be expected that people process negative cues more thoroughly than positive ones.
+Furthermore, people may develop much more advanced memory about negative entities.
+This can also cause high awareness to negative information [@baumeister2001; @taylor1991].
 

### 2022-09-15 Paper.Rmd
elaborate on eda and robustness

@@
 
-In this section both dependent and independent variables are going to be introduced.
+Exploratory Data Analysis(EDA) has no set of procedures to be followed.
+The way EDA is conducted almost always depends on the context of the research.
+@jebb2017 discusses that EDA encourages scientific replication if done properly.
+As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value.
+I also think that readers or fellow researchers might build a better intiution about the discussion and what goes into the model in this study.
+
 The goal of this section is not "confirmatory" whatsoever.
-As a researcher, I believe sharing the data that I used in the study transparently increases the research's reproducibility value.
-
-In this section there will be univariate visualizations of all variables and bivariate visualizations of independent variables against the dependent variable.
-
--   elaborate more on the importance of EDA here
+Both dependent and independent variables are going to be introduced with an emphasis on their quantitative features such as their distributions and potential transformations which can be applied to the variables in question.
+In addition to this, bivariate relations between independent and dependent variables will be plotted in order to get an initial idea about the potential effects along with similar findings from the literature.
+Thus, in a sense, EDA in this section doesn't carry out the purpose of discovery, rather it merely puts the data on the spot for the sake of transparency.
 
@@
 The most helpful review interval seems to be lying between 70% to 80%.
+
+On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard error will be calculated correctly or not in a regression method.
+@li2012 found out that given a relatively high sample size (\>3000) linear regression techniques produces sound estimates of coefficients.
+Since the sample size for search goods is over 8000 it might be assumed that the use of linear regression methods is acceptable.
 

### 2022-09-20 Paper.Rmd
some minor changes

@@
 Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].
+Although very rare, a negative relationship between Review Length and Perceived Helpfulness was also reported [@chatterjee2020; @yang2019].
 
@@
 
-## Some other theory
-
 # The Data and Research Methodology
@@
 Therefore, search goods data was collected from BestBuy.
-
--   mention that channels can change the way we perceive search and experience goods.
 
@@
 As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value.
-I also think that readers or fellow researchers might build a better intiution about the discussion and what goes into the model in this study.
+I also think that readers or fellow researchers might build a better intuition about the discussion and what goes into the model in this study.
 
@@
 
-"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 over 5 Helpful votes or 80 over 100 Helpful votes [@mudambi2010; @choi2020].
+"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].
 
@@
 In order to decrease the uncertainty, search costs must be reduced.
-In \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods.
+In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods.
 Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014].
@@
 Since there are less objectivity, a helpful review to one person might not be helpful to another.
-However, since there are other ways to objectively evaluate a movie, a weaker positive linear relationship is expected.
+However, since there are other ways to objectively evaluate a movie such as quality of its effects or its budget and how well this budget is utilized, a weaker positive linear relationship is expected.
 Therefore it is hypothesized that:
@@
 
-As it was mentioned in \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses.
+As it was mentioned in Section \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses.
 Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses.
@@
 
-Hyphothesis 1 proposed a U-Shape for the relationship between Review Extremity and Perceived Helpfulness.
+Hypothesis 1 proposed a U-Shape for the relationship between Review Extremity and Perceived Helpfulness.
 For Search Goods this is true because the linear Rating Extremity coefficient (-0.061, p \< 0.01) has a negative sign and the quadratic Rating Extremity coefficient (0.036, p \< 0.001) has a positive sign.

### 2022-09-22 Paper.Rmd
started discussion

@@
 For instance a bad design in a laptop might cause fans to make much more noise than they should normally do.
-This information along with a very low rating may signal there are some inherent problems with that particular product, making the feedback more helpful.
-On the other hand, for Experience Goods and in this specific case movies, opinions for a given product might be much more subjective.
-For example, a reviewer might find a movie "childish" and give it one star, the other might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness.
+This information along with a very low rating may signal that there are some inherent problems with the particular product, making the feedback more helpful.
+On the other hand, for Experience Goods and in the specific case of movies, opinions for a given product might be much more subjective.
+For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness.
 Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989].
@@
 This means that for positive extreme reviews relatively shorter texts are more helpful.
-Logarithmic form also proves that words in a review shows diminishing returns to helpfulness.
+Logarithmic form also proves that additional words in a review shows diminishing returns to helpfulness.
 Experience Goods somewhat deviates from the results of Search Goods.
@@
 For both good types the interaction effects are significantly negative (-0.043, p \< 0.001 ; -0.015, p \< 0.001).
-This means that as Review Extremity increases longer reviews become less helpful, supporting the idea of people spending more time evaluating negative information because it takes more time to read a longer review.
+This means that as Review Rating increases longer reviews become less helpful, supporting the idea of people spending more time evaluating negative information because it takes more time to read a longer review.
 However, there are nuances too.
-For Search Goods, the effect of the Review Length is always positive whether or not Review Extremity is low or high.
-On the contrary, for Experience Goods, after some point of Review Extremity longer reviews become "unhelpful" because the sign of the Review Length turns to negative.
+For Search Goods, the effect of the Review Length is always positive whether or not Review Rating is low or high.
+On the contrary, for Experience Goods, after some point of Review Rating longer reviews become "unhelpful" because the sign of the Review Length turns to negative.
 In this case Hypothesis 3 is supported wholly for Search Goods and somewhat supported for Experience Goods.
@@
 
+The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970.
+It shouldn't be ignored that this contrast is only relevant for the case of electronics versus movies since the available data only included these products.
+Electronics such as laptops or phones carry very strong search attributes whereas movies can be classified as "pure experience" goods which can be considered as a special case [@liu2014].
+
+Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods.
+The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average.
+Additionally, Perceived Helpfulness has a higher responsiveness to Review Length when a review has a low rating which means that people care more about negative cues than positive cues.
+
+-   talk about positive sentiments and ratings and compare them
+
+```{=html}
+<!-- -->
+```
+-   mention the search goods as well.
+
+One reason why the statistical results for search goods came out just as expected can be accredited to their objective features.
+Properties of electronics are easily evaluated prior purchase.
+This means that it is comparatively easier to collect information on search goods than experience goods.
+Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals.
+Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on camera.
+Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.
+
+-   talk about the limitations as we go
+
+# Conclusion
+
 \*\*WORK IN PROGRESS\*\*
@@
 
-# Conclusion
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
 # References

### 2022-09-23 Paper.Rmd
discussion is comin

@@
 The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average.
-Additionally, Perceived Helpfulness has a higher responsiveness to Review Length when a review has a low rating which means that people care more about negative cues than positive cues.
-
--   talk about positive sentiments and ratings and compare them
-
-```{=html}
-<!-- -->
-```
--   mention the search goods as well.
+Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating.
+This means that people care more about negative cues than positive cues probably because they want to cut down potential certain losses.
+A similar result was reflected by the negative coefficient of the proportion of positive words in a review.
+This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers.
+Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014].
+An explanation to this could be that certain brands or products might be favored by some customers and these customers might selectively tend towards positively rated reviews and find them helpful just because they love the brand [@zhu2021].
+The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this.
+A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded.
+Since a preference towards a brand is subjective it might be speculated that a strong brand could embed experience attributes into search goods.
+A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good.
+That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable is the product image that was created by Apple.
+
+-   you can discuss about the fluidity of search and exp attributes
+
+A similar strong support for Negativity Bias can't be observed in the case of movies.
+Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating.
+According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough.
+This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there.
+However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens.
+This means that potential buyers require more elaboration when a review is rated low.
+For experience goods, high rated reviews become more helpful on the average when reviews are short.
+This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021].
+Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.
+
+Various reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods.
+
+-   subjectivity, emolex, heterogeneous opinions, row 10, show other works which are in line with your results,
 
@@
 -   talk about the limitations as we go
+-   talk about whatever we speculate we are omitting the readers buying motivation
 

### 2022-09-25 Paper.Rmd
brain fry

@@
 
+-   show other works which are in line with your results,
+
 The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970.
@@
 Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating.
-This means that people care more about negative cues than positive cues probably because they want to cut down potential certain losses.
+This means that people care more about negative cues than positive cues probably because they want to cut down potential sure losses.
 A similar result was reflected by the negative coefficient of the proportion of positive words in a review.
@@
 A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good.
-That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable is the product image that was created by Apple.
+That is although an MP3 player such as iPod has many objective search attributes such as storage capacity and battery life, what makes this particular product preferable most of the time is the product image that was created by Apple.
+
+The rationality why the statistical results for search goods came out just as expected can be accredited to their objective features.
+Properties of electronics are easily evaluated prior purchase.
+This means that it is comparatively easier to collect information on search goods than experience goods.
+Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals.
+Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on a camera.
+Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.
 
@@
 According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough.
-This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there.
+This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there so no matter the Review Length is U-Shaped function is observed.
 However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens.
@@
 
-Various reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods.
-
--   subjectivity, emolex, heterogeneous opinions, row 10, show other works which are in line with your results,
-
-One reason why the statistical results for search goods came out just as expected can be accredited to their objective features.
-Properties of electronics are easily evaluated prior purchase.
-This means that it is comparatively easier to collect information on search goods than experience goods.
-Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals.
-Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on camera.
-Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.
+A number of reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods.
+The expectation was observing a negative significant coefficient for proportion of positive words and a positive significant coefficient for proportion of negative words.
+At the very least it can be said that the existence of positive words in a movie review doesn't offer a diagnostic value according to regression results.
+Thus, it is hard to say there is a strong deviation from Hypothesis 6.
+On the contrast, Hypothesis 5 for experience goods wasn't supported at all.
+
+One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews wasn't suitable for movie reviews.
+For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word.
+One or more movies in the sample include movies where "Nicholas *Cage*" had the starring role.
+There are also "*Marvel* Cinematic Universe" movies present in the data.
+Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon.
+To test this problem words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types.
+Neither coefficient signs nor coefficient significances were changed.
+However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly.
+Further filtering wasn't pursued because of potential dangers of hypothesis fishing.
+(The results in Table \@ref(tab:Reg-Results) are the results with the filter.)
+
+-   talk about the correlation table where rating and sentiment has the expected correlations
+
+Another reason may arise from the subjective nature of the experience attributes of the movies.
+Negative words, in the case of electronics, may have narrower range of meanings because what they try to convey directly relates the to quality of the good itself.
+The quality of the good is easily accessible because of the fact that electronics have dominant search attributes.
+Thus, negative words probably translates as potential monetary risks rather than affecting emotions.
+A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility.
+Furthermore, electronics are usually bought to be used for a comparatively long period of time.
+A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important.
+Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future.
+On the other hand, the monetary risks associated with a bad movie are relatively lower.
+Consumers can go to cinema, buy a DVD or access the movie as a part of their subscription plan on platforms such as Netflix.
+Subscription or ticket fees aren't the only cost for the consumer.
+In order to consume the product the consumer must spend the time that is equal to the duration of the movie.
+Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time.
+Additionally, laptops, phones and televisions could be considered as tools to consume products such as software and media whereas movies themselves can be considered as consumed after they were watched for the first time.
+Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device.
+Therefore, negative words in a movie review may not alert the consumer for potential monetary losses.
+Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.
+
+-   subjectivity, emolex, heterogeneous opinions, row 10,
 

### 2022-09-27 Paper.Rmd
it never ends

@@
 Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating.
-This means that people care more about negative cues than positive cues probably because they want to cut down potential sure losses.
+This means that people focus more on negative cues than positive cues probably because they want to cut down potential sure losses.
 A similar result was reflected by the negative coefficient of the proportion of positive words in a review.
@@
 A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded.
-Since a preference towards a brand is subjective it might be speculated that a strong brand could embed experience attributes into search goods.
+Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods.
 A similar notion was discussed by @mudambi2010 where they classified Apple iPod as an experience good.
@@
 
+-   more elab is needed here
+
+```{=html}
+<!-- -->
+```
 -   you can discuss about the fluidity of search and exp attributes
@@
 
--   subjectivity, emolex, heterogeneous opinions, row 10,
-
--   talk about the limitations as we go
--   talk about whatever we speculate we are omitting the readers buying motivation
+-   heterogeneous opinions, row 10,
+
+Unexpected and different results are common in the literature of Review Helpfulness [@fan2021].
+This paper and the rest of the literature suffers from certain biases that the data imposes.
+Many other limitations may arise from potential omitted variables.
+
+Firstly, as @mudambi2010 pointed out that potential selection bias exist in the data.
+It is not possible to know how many people actually read a particular review.
+Additionally, there is a strong possibility that as a review gets more votes this is going to draw more attention to the particular review.
+This can cause a positive feedback loop and this feedback loop can increase the chances that an observation making into the sample which leads to a selection bias.
+To fight with this, researchers usually resorted to setting a threshold of total votes where reviews with small amount of votes were filtered out of the sample.
+Furthermore, a multi-level regression model was developed by @kuan2015 in order to overcome the selection bias.
+In the first level of the regression the researchers modeled the binary case of wheter a review gets voted or not.
+After what makes a review voted was established, they progressed to the next stage of modelling the review helpfulness.
+Along with the multi-level model results they also shared OLS results where non-voted reviews were filtered from the data.
+Most of the significance and coefficient signs weren't different but coefficients differed in magnitude.
+
+Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature.
+Let alone different methodologies, even the utilizations of similar variables were contrasting.
+For instance, review extremity was employed in three different ways by researchers.
+This paper and some others use review ratings as it is.
+Another group of studies took the differences of review ratings from the mean rating of a given product.
+This is usually called Review Inconsistency.
+The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5).
+In some studies these dummy variables were extended to negative and positive extreme dummies as well.
+The differences isn't limited to Review Rating.
+The usages the dependent variable, Perceived Helpfulness, diverged as well.
+In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression.
+Furthermore, some studies converted the percentage of the helpfulness into a binary problem where over 50% helpfulness score was considered as a helpful review.
+As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well.
+All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.
+
+-   talk about the limitations as we go, selection bias and omitted variables, different utilizations of variables,
+
+-   talk about whatever we speculate we are omitting the readers buying motivation, their trust towards strangers, search/exp classification is too simple,
 

### 2022-09-29 Paper.Rmd
this is torture at this point

@@
 In other words, there are limited ways to construct a review because search attributes are more objective.
-Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length.
+Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have.
 However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer.
@@
 This means that it is comparatively easier to collect information on search goods than experience goods.
-Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals.
+Other than online consumer reviews on a retailer's website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals.
 Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on a camera.
@@
 -   more elab is needed here
-
-```{=html}
-<!-- -->
-```
 -   you can discuss about the fluidity of search and exp attributes
@@
 According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough.
-This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there so no matter the Review Length is U-Shaped function is observed.
+This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients so no matter the Review Length is U-Shaped function is observed.
 However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens.
@@
 Another reason may arise from the subjective nature of the experience attributes of the movies.
-Negative words, in the case of electronics, may have narrower range of meanings because what they try to convey directly relates the to quality of the good itself.
+Negative words, in the case of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself.
 The quality of the good is easily accessible because of the fact that electronics have dominant search attributes.
@@
 Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time.
-Additionally, laptops, phones and televisions could be considered as tools to consume products such as software and media whereas movies themselves can be considered as consumed after they were watched for the first time.
 Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device.
@@
 Furthermore, a multi-level regression model was developed by @kuan2015 in order to overcome the selection bias.
-In the first level of the regression the researchers modeled the binary case of wheter a review gets voted or not.
+In the first level of the regression the researchers modeled the binary case of whether a review gets voted or not.
 After what makes a review voted was established, they progressed to the next stage of modelling the review helpfulness.
@@
 Another group of studies took the differences of review ratings from the mean rating of a given product.
-This is usually called Review Inconsistency.
+The resulting variable is usually called Review Inconsistency.
 The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5).
@@
 In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression.
-Furthermore, some studies converted the percentage of the helpfulness into a binary problem where over 50% helpfulness score was considered as a helpful review.
+Furthermore, some studies converted the percentage of the helpfulness into a binary problem where reviews with over 50% helpfulness score was considered as a helpful review.
 As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well.
@@
 
--   talk about the limitations as we go, selection bias and omitted variables, different utilizations of variables,
-
--   talk about whatever we speculate we are omitting the readers buying motivation, their trust towards strangers, search/exp classification is too simple,
+Potential omitted variables such as consumer's buying motivation or their trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021.
+A person who is more agreeable high likely will find many more reviews helpful on the average.
+Additionally, buying motivation might play an important role in explaining the review helpfulness.
+Above, it was speculated that some consumers might have tendency towards certain brands or products.
+Favored brands might not be the only factor that affects the consumer motivation.
+For instance, a consumer with limited amount of budget may find positive reviews of products that have suitable prices helpful.
+Thus the product price relative to the consumer's budget can also be used as an indicator.
+
+-   talk about review and reviewer related determinant, search/exp classification is too simple,
 

### 2022-09-30 Paper.Rmd
first pass is complete!

@@
 Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating.
-This means that people focus more on negative cues than positive cues probably because they want to cut down potential sure losses.
+This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher.
+This way they are able to cut down potential sure losses.
 A similar result was reflected by the negative coefficient of the proportion of positive words in a review.
-This shows that reviews with positive sentiments doesn't have a strong diagnostic value for consumers.
+This shows that reviews with positive sentiments don't offer diagnostic value for consumers.
 Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014].
@@
 -   more elab is needed here
--   you can discuss about the fluidity of search and exp attributes
+-   you can discuss about the fluidity of search and exp attributes, tv is an experience goods in the original work
 
@@
 According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough.
-This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients so no matter the Review Length is U-Shaped function is observed.
+A similar situation is the case for search goods as well but the interaction term doesn't interfere with the signs of the other coefficients so no matter the Review Length is a U-Shaped function is observed for search goods.
 However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens.
@@
 On the other hand, the monetary risks associated with a bad movie are relatively lower.
-Consumers can go to cinema, buy a DVD or access the movie as a part of their subscription plan on platforms such as Netflix.
+Consumers can go to cinema, buy a DVD, rent the movie on YouTube or access the movie as a part of their subscription plan on platforms such as Netflix.
 Subscription or ticket fees aren't the only cost for the consumer.
@@
 
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
-
-\*\*WORK IN PROGRESS\*\*
+This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty.
+Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of a consumer.
+Results showed similarities from the existing Review Helpfulness literature.
+However, once again it should be noted that the literature has many conflicting results.
+
+This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB.
+In addition, to my knowledge, this the first study which analyzed the linear interaction between Review Length and Review Rating in terms of Negativity Bias Theorem.
+
+Goods with very strong search or experience attributes were chosen in order to compare the information gathering process in the clearest way possible.
+The results proves the fact that information gathering is easier for search goods than experience goods.
+This means that consumers face less uncertainty against search goods.
+The results are only generalizable to laptops, phones, televisions and movies since different goods have different mix of search and experience attributes.
+
+There are some implications for future studies.
+Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text.
+One advantage of deep learning method over a lexicon is its versatility.
+A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is.
+Secondly, future studies should consider collecting data from different regions and cultures.
+There might be some differences on how consumers process and react to the information in order to deal with uncertainty.
+Lastly, researchers can dig deeper into search and experience goods paradigm.
+It is well established in the literature that product type affects the information gathering process.
+However, there might be differences within product types depending on their search and experience attributes.
+An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature.
 

### 2022-10-04 Paper.Rmd
2nd draft complete

@@
 
--   show other works which are in line with your results,
-
 The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970.
@@
 This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher.
-This way they are able to cut down potential sure losses.
+This way consumers are able to cut down potential sure losses.
 A similar result was reflected by the negative coefficient of the proportion of positive words in a review.
@@
 Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.
-
--   more elab is needed here
--   you can discuss about the fluidity of search and exp attributes, tv is an experience goods in the original work
 
@@
 (The results in Table \@ref(tab:Reg-Results) are the results with the filter.)
-
--   talk about the correlation table where rating and sentiment has the expected correlations
 
@@
 
--   heterogeneous opinions, row 10,
-
 Unexpected and different results are common in the literature of Review Helpfulness [@fan2021].
@@
 
--   talk about review and reviewer related determinant, search/exp classification is too simple,
-
 # Conclusion
@@
 A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is.
-Secondly, future studies should consider collecting data from different regions and cultures.
+Next, future studies should consider collecting data from different regions and cultures.
 There might be some differences on how consumers process and react to the information in order to deal with uncertainty.
-Lastly, researchers can dig deeper into search and experience goods paradigm.
+Additionally, researchers can dig deeper into search and experience goods paradigm.
 It is well established in the literature that product type affects the information gathering process.
@@
 An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature.
+Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works.
+Reviews and how helpful these reviews are perceived from potential buyers is relatively a new topic.
+In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data.
+This increases the value of EDA as well.
 

### 2022-10-05 Paper.Rmd
2nd draft minor fix

@@
 This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty.
-Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of a consumer.
+Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of an average consumer.
 Results showed similarities from the existing Review Helpfulness literature.
@@
 One advantage of deep learning method over a lexicon is its versatility.
-A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicons a negative word is a negative word no matter the context is.
+A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is.
 Next, future studies should consider collecting data from different regions and cultures.
@@
 Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works.
-Reviews and how helpful these reviews are perceived from potential buyers is relatively a new topic.
+Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic.
 In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data.

### 2022-10-31 Paper.Rmd
a big leap on formatting

@@
 ---
+documentclass: report
 title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
 bibliography: references.bib
+csl: apa.csl
 link-citations: yes
@@
     includes:
-      in_header: non-float-fig.tex
+      in_header: [non-float-fig.tex, custom.tex]
     toc_depth: 4
+geometry: left=40mm, right=20mm, top=30mm, bottom=30mm
+fontsize: 12pt
+papersize: A4
+linestretch: 1.25
+fontfamily: times
 ---
@@
 
+\newpage
+
 # Introduction
@@
 
+\newpage
+
 # Literature Review
@@
 This means that studies are rather unorganized and researchers are usually inclining towards their own domain of expertise when it comes to explaining review helpfulness.
+
+\newpage
 
@@
 This can also cause high awareness to negative information [@baumeister2001; @taylor1991].
+
+\newpage
 
@@
 
+\newpage
+
 # Results
@@
 ```{r Reg-Results, results='asis'}
+
 stargazer(list("Search Tobit" = search_tobit,
@@
           type = "latex",
+          notes.align = "l",
           header = FALSE,
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 # Conclusion
@@
 
+\newpage
+
 # References

### 2022-10-31 Paper.Rmd
formatting done

@@
 papersize: A4
-linestretch: 1.25
+linestretch: 1.5
 fontfamily: times
@@
 
-# Introduction
+# Introduction {-}
 

### 2022-11-01 Paper.Rmd
fix notations

--- 2022-10-31 Paper.Rmd
@@
 documentclass: report
-title: 'Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?'
+title: 'Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?'
 bibliography: references.bib
@@
 
-# Introduction
+# Introduction {.unnumbered}
 
@@
 Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
-On the other hand, quality of Experience goods can't be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).
+On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).
 
@@
 
-Since OCR don't share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
+Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
 On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button.
@@
 The first group is reviewer-related predictors.
-Variables within this group try to understand the relationship between reviewer status and perceived helpfulness(reviewer expertise, number of past reviews etc.).
+Variables within this group try to understand the relationship between reviewer status (reviewer expertise, number of past reviews etc.) and perceived helpfulness.
 [@sun2019; @ghose2011].
@@
 They are usually different than Review Extremity.
-In most cases Review Extremity and Review Sentiment (Valence) don't match [@zhang2011].
+In most cases Review Extremity and Review Sentiment (Valence) do not match [@zhang2011].
 @baek2012 and @kuan2015 discovered a positive relationship between the proportion of negative words and perceived helpfulness.
@@
 
-Any website which offers online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data from either websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data.
+Any website which offer online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data either from websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data.
 They have their respective APIs and on top of that, it is relatively easier to scrape both websites.
@@
 IMDB is a home for both critic and user reviews of Movies and TV Shows.
-In some other studies local equivalents of Amazon was used as well.
+In some other studies local equivalents of Amazon were used as well.
 [@sun2019].
@@
 Depending on its dominant attributes the good can be classified as Search or Experience.
-@darby1973 extended Search and Experience goods framework with Credence goods where consumers can't evaluate the good even after the consumption.
-Though, Credence goods won't be discussed any further in this study.
+@darby1973 extended Search and Experience goods framework with Credence goods where consumers can not evaluate the good even after the consumption.
+Though, Credence goods will not be discussed any further in this study.
 
@@
 Someone else's hair in one's meal has the potential of ruining the whole meal.
-On the contrary a plate of hair won't turn to a delicious meal just because there is a slice of a delicious pizza on top of the hair.
+On the contrary a plate of hair will not turn to a delicious meal just because there is a slice of a delicious pizza on top of the hair.
 @rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects.
@@
 Loss Aversion [@kahneman1979; @tversky1991] is the phenomenon where the Negative Potency can be observed the best.
-People risk more/less when they are losing/gaining something.
+People risk more (less) when they are losing (gaining) something.
 This behavior can be explained by the Endowment Effect [@kahneman1990].
 Endowment effect occurs because people usually over-estimate the value of their belongings, for example a pencil.
-However, they would have under-valued the same pencil if the item didn't belong to them.
+However, they would have under-valued the same pencil if the item did not belong to them.
 The reason to this behavior is that the dis-utility of losing that pencil is greater than the utility of acquiring the same pencil.
@@
 In other words, negative things cause more negativity as the time goes on.
+At the very least, the effects of negativeness are a lot more long-standing than effects of positiveness.
 
@@
 This is apparent in religions.
-For most of the religions being a good and pious person takes time, demands utmost care.
+For the most of the religions being a good and pious person takes time, demands utmost care.
 However, tainting this image is very easy with certain actions such as murder or pre-martial intercourse.
@@
 
-The data was scraped with a custom web scraper which was constructed with Selenium Framework for Pyhton 3 [@python3].
+The data was scraped with a custom web scraper which was constructed with Selenium Framework for Python 3 [@python3].
 The scraper got the customer reviews from IMDB and BestBuy.
@@
 Specifically, 201,113 reviews for TVs, 130,270 for Laptops and 51,974 for Phones.
-However, in the data there are many reviews that were never voted.
-To make sure that I am analyzing reviews that were actually read by people, I set a threshold for Total Reviews as five.
+However, in the data there are many reviews that were never got voted and probably they were never read because they got lost in the crowd of other reviews.
+To make sure that the analysis sample contains only the reviews which were actually read by potential buyers, a threshold of 5 was set for Total Votes.
 In other words, reviews that had less than 5 Total Votes were removed from the analysis data [@choi2020; @baek2012].
@@
 It should be noted that `r round(15024 / 31863, digits = 2) * 100` percent of the reviews had total votes of 5 or greater for experience goods, whereas only `r round(8042 / 383357, digits = 2)* 100` percent of the search goods were voted at least 5 times.
-Most of the search product reviews aren't getting voted and even possible that they aren't getting read at all.
+Most of the search product reviews are not getting voted and even possible that they are not getting read at all.
 This might support the idea that people form more homogeneous opinions about search goods [@hong2014].
-Once a helpful review is written most of the other reviews become redundant since other reviews most likely conveys similar information.
+Once a helpful review is written most of the other reviews become redundant since other reviews most likely convey similar information.
 On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times.
@@
 
-Exploratory Data Analysis(EDA) has no set of procedures to be followed.
+Exploratory Data Analysis (EDA) has no set of procedures to be followed.
 The way EDA is conducted almost always depends on the context of the research.
@@
 In addition to this, bivariate relations between independent and dependent variables will be plotted in order to get an initial idea about the potential effects along with similar findings from the literature.
-Thus, in a sense, EDA in this section doesn't carry out the purpose of discovery, rather it merely puts the data on the spot for the sake of transparency.
+Thus, in a sense, EDA in this section does not carry out the purpose of discovery, rather it merely puts the data on the spot for the sake of transparency.
 
@@
   scale_x_continuous(n.breaks = 10)+
-  labs(y = NULL)
+  labs(y = "Count")
 
@@
 This time helpfulness ratio is sort of normally distributed.
-There aren't very helpful reviews.
+There are not very helpful reviews.
 The most helpful review interval seems to be lying between 70% to 80%.
 
-On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard error will be calculated correctly or not in a regression method.
+On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard errors will be calculated correctly or not in a regression method.
 @li2012 found out that given a relatively high sample size (\>3000) linear regression techniques produces sound estimates of coefficients.
@@
 Thus, one good review is enough to reveal the quality of a product.
-I think this is why we see such a big spike at 100% on Figure \@ref(fig:IV-Hist-Search).
-In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), we see that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%.
+This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search).
+In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%.
 This might be because evaluation process of movies is rather subjective.
@@
 On Figure \@ref(fig:Search-Rating) (B) and Figure \@ref(fig:Experience-Rating) (B) the bivariate relationship between perceived helpfulness and review extremity can be seen.
-Again, as a researcher, I must emphasize that this analysis is not confirmatory.
+Once again, it must be emphasized that this analysis is not confirmatory.
 On figures, we can observe "U" type of relationship for both Search and Experience goods, though the non-linearity seems to be stronger with Search goods.
@@
 
-The exponential distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A).
+The exponential-like distribution of the number of words can be observed for both good types on Figure \@ref(fig:Search-Length) (A) and Figure \@ref(fig:Experience-Length) (A).
 This means that reviews become less prevalent as they get longer.
@@
 1.  The first review date for a particular brand and model of a product (Movie, Phone, Laptop, TV) was taken.
-2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and model resulting an integer variable representing days.
+2.  The first dates for particular products then subtracted from other reviews' dates under the respective brand and the model resulting an integer variable representing days.
 3.  Bigger numbers represent more recent reviews.
@@
 On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen.
-On plots, x-axis labels were given in the logarithm of base 10 so 1.00 on the x-axis implies that 10% of the review was negative words.
-It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods don't have any negative words in them.
+On plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words.
+It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods do not have any negative words in them.
 For experience goods this number is `r round(mean(movies_data$negative == 0), digits = 2)` percent.
@@
 In this case, however, reviews of both good types have more positive words in them proportionally when compared to negative words.
-`r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods don't have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods.
+`r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods do not have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods.
 Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).
@@
 As the proportion increases so does the number of words.
-That's why aforementioned figures show similar relationships between variables.
+That is why aforementioned figures show similar relationships between variables.
 On higher dimensions these relationships might be different.
@@
 
-"Total Votes" is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].
+Total Votes is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].
 
@@
 Before progressing to the modelling section, it would be a good practice to check the correlations between independent and control variables in order not to cause any multi-colinearity problems.
-As it can be seen on Figure \@ref(fig:Correlations) there aren't any major correlations between independent and control variables for both good types.
-
-The relatively high positive/negative correlation between the Review Rating and Positive/Negative word proportions might give a hint about the usefulness of the lexicon.
+As it can be seen on Figure \@ref(fig:Correlations) there are not any major correlations between independent and control variables for both good types.
+
+The relatively high positive / negative correlation between the Review Rating and Positive / Negative word proportions might give a hint about the usefulness of the lexicon.
 As the Review Rating gets higher the review contains more positive words and, on the other hand, low rated reviews have more negative words in them.
@@
 @korfiatis2012 found that neutral rated reviews (3 out of 5 stars) imply indifference to readers.
-This means that prior information of the potential buyer can't be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006].
+This means that prior information of the potential buyer can not be influenced by these neutral reviews and likely to be found less helpful compared to extreme reviews (1 or 5 stars) [@wang2018; @liu2014; @cao2011; @ghose2006].
 As the reviews get more extremely rated they might strengthen or sway prior information that a potential consumer has, making them more helpful.
@@
 For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness.
-Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations aren't impactful on the decision making process [@hoch1989].
+Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations are not impactful on the decision making process [@hoch1989].
 In other words, prior expectations play a bigger role in decision making process for experience goods.
@@
 
-In order to decrease the uncertainty, search costs must be reduced.
+In order to decrease the uncertainty in the most optimal way, search costs must be reduced.
 In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods.
@@
 Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have.
-However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer.
-Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015].
+However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer.
+Because of this, there might be diminishing marginal returns to Review Length.
+After some point more information can cause confusion and may render the review unfocused [@schindler2012; @huang2015].
 On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014].
@@
 Since there are less objectivity, a helpful review to one person might not be helpful to another.
-However, since there are other ways to objectively evaluate a movie such as quality of its effects or its budget and how well this budget is utilized, a weaker positive linear relationship is expected.
+This might decrease the average responsivess of the Perceived Helpfulness to the Review Length.
+However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected.
 Therefore it is hypothesized that:
@@
 It is known that Review Rating is the satisfaction level of a customer towards a product.
-However, Review Rating itself isn't enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product.
+However, Review Rating itself is not enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product.
 The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review.
@@
 Censored data arises when there exist lower (censored from below) or upper (censored from above) or both lower and upper boundaries for the dependent variable.
-This type of data is fairly prevalent in Economics.
+This type of data is fairly prevalent in economics.
 For instance, in consumer economics there is no such thing as "negative consumption" or in labor economics there is no such thing as "negative work hours".
 Furthermore, there might be cases where some really high values could be recorded as "50,000 or more" because of the data collection design.
-Ordinary Least Squares can't take account of the censored observations in the data because it extrapolates lower and upper ends when it fits the model and this leads biased estimations.
+Ordinary Least Squares can not take account of the censored observations in the data because it extrapolates lower and upper ends when it fits the model and this leads biased estimations.
 
@@
 For Experience Goods, on the other hand, both linear (0.026, p \< 0.001) and quadratic (0.006, p \< 0.001) Review Extremity terms are positive.
-A U-Shaped function can't be observed.
+A U-Shaped function can not be observed.
 However, the significant interaction effect between Review Length and Review Extremity (-0.015, p \< 0.001) suggests that for longer reviews the linear term turns to negative.
@@
 The results show a clear contrast between the objective nature of search goods versus the subjective nature of experience goods which once again validates the notion of Search and Experience goods classification that was developed by @nelson1970.
-It shouldn't be ignored that this contrast is only relevant for the case of electronics versus movies since the available data only included these products.
+It should not be ignored that this contrast is only relevant for the case of electronics versus movies since the available data only included these products.
 Electronics such as laptops or phones carry very strong search attributes whereas movies can be classified as "pure experience" goods which can be considered as a special case [@liu2014].
@@
 A similar result was reflected by the negative coefficient of the proportion of positive words in a review.
-This shows that reviews with positive sentiments don't offer diagnostic value for consumers.
+This shows that reviews with positive sentiments do not offer diagnostic value for consumers.
 Nonetheless, the U-Shape of the Review Rating variable also suggests positivity bias [@hoorens2014].
@@
 The reason why there is a divergence between the "positively rated review" and "a review with positive sentiment" might be explained by this.
-A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer doesn't really care about what is written in the review, he might skim through positive reviews until he feels persuaded.
+A consumer who has brand or product inclinations wants to be persuaded to have the product so this particular consumer does not really care about what is written in the review, he might skim through positive reviews until he feels persuaded.
 Since a preference towards a brand is subjective it might be speculated that a strong brand image could embed experience attributes into search goods.
@@
 
-A similar strong support for Negativity Bias can't be observed in the case of movies.
+A similar strong support for Negativity Bias can not be observed in the case of movies.
 Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating.
 According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough.
-A similar situation is the case for search goods as well but the interaction term doesn't interfere with the signs of the other coefficients so no matter the Review Length is a U-Shaped function is observed for search goods.
+A similar situation is the case for search goods as well but the interaction term does not interfere with the signs of the other coefficients so no matter the Review Length is a U-Shaped function is observed for search goods.
 However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens.
@@
 
-A number of reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 didn't hold for experience goods.
+A number of reasons could be speculated about why the Hypothesis 5 and Hypothesis 6 did not hold for experience goods.
 The expectation was observing a negative significant coefficient for proportion of positive words and a positive significant coefficient for proportion of negative words.
-At the very least it can be said that the existence of positive words in a movie review doesn't offer a diagnostic value according to regression results.
+At the very least it can be said that the existence of positive words in a movie review does not offer a diagnostic value according to regression results.
 Thus, it is hard to say there is a strong deviation from Hypothesis 6.
-On the contrast, Hypothesis 5 for experience goods wasn't supported at all.
-
-One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews wasn't suitable for movie reviews.
+On the contrast, Hypothesis 5 for experience goods was not supported at all.
+
+One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for movie reviews.
 For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word.
@@
 However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly.
-Further filtering wasn't pursued because of potential dangers of hypothesis fishing.
+Further filtering was not pursued because of potential dangers of hypothesis fishing.
 (The results in Table \@ref(tab:Reg-Results) are the results with the filter.)
@@
 Consumers can go to cinema, buy a DVD, rent the movie on YouTube or access the movie as a part of their subscription plan on platforms such as Netflix.
-Subscription or ticket fees aren't the only cost for the consumer.
+Subscription or ticket fees are not the only cost for the consumer.
 In order to consume the product the consumer must spend the time that is equal to the duration of the movie.
-Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time.
+Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she does not waste any more time.
 Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device.
@@
 Along with the multi-level model results they also shared OLS results where non-voted reviews were filtered from the data.
-Most of the significance and coefficient signs weren't different but coefficients differed in magnitude.
+Most of the significance and coefficient signs were not different but coefficients differed in magnitude.
 
@@
 In some studies these dummy variables were extended to negative and positive extreme dummies as well.
-The differences isn't limited to Review Rating.
+The differences is not limited to Review Rating.
 The usages the dependent variable, Perceived Helpfulness, diverged as well.
@@
 This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty.
-Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as an theoretical engine to explain the information gathering process of an average consumer.
+Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer.
 Results showed similarities from the existing Review Helpfulness literature.
@@
 
-# References
+# Bibliography

### 2022-11-01 Paper.Rmd
minor format adjustments

@@
   scale_x_continuous(n.breaks = 10)+
-  labs(y = NULL)
+  labs(y = "Count")
 ```
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(method = "loess", color = "steelblue")+
+  geom_smooth(method = "loess", color = "steelblue", size = 1.7)+
   labs(x = "Review Rating")
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
+  geom_smooth(color = "steelblue", size = 1.7)+
   scale_x_continuous(n.breaks = 10)+
@@
   scale_x_continuous(n.breaks = 8)+
-  labs(y = NULL, x = "Number of the Words")
+  labs(y = "Count", x = "Number of the Words")
 
@@
   scale_x_log10(n.break = 8)+
-  labs(y = NULL, x = "log10(Number of the Words)")
+  labs(y = "Count", x = "log10(Number of the Words)")
 
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
+  geom_smooth(color = "steelblue", size = 1.7)+
   scale_x_continuous(n.breaks = 8)+
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
+  geom_smooth(color = "steelblue", size = 1.7)+
   scale_x_log10(n.breaks = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
-  scale_x_continuous(n.breaks = 8)+
-  labs(y = NULL, x = "Number of the Words")
+  scale_x_continuous(n.breaks = 7)+
+  labs(y = "Count", x = "Number of the Words")
 
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
-  scale_x_log10(n.break = 8)+
-  labs(y = NULL, x = "log10(Number of the Words)")
+  scale_x_log10(n.break = 7)+
+  labs(y = "Count", x = "log10(Number of the Words)")
 
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
-  scale_x_continuous(n.breaks = 8)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous(n.breaks = 7)+
   labs(x = "Number of the Words")
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
-  scale_x_log10(n.breaks = 8)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_log10(n.breaks = 7)+
   labs(x = "log10(Number of the Words)")
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
-  scale_x_continuous(n.breaks = 8)+
-  labs(y = NULL, x = "Freshness of Review")
+  scale_x_continuous(n.breaks = 7)+
+  labs(y = "Count", x = "Freshness of Review")
 
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
-  scale_x_log10(n.break = 8)+
-  labs(y = NULL, x = "log10(Freshness of Review + 1)")
+  scale_x_log10(n.break = 7)+
+  labs(y = "Count", x = "log10(Freshness of Review + 1)")
 
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
-  scale_x_continuous(n.breaks = 8)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous(n.breaks = 7)+
   labs(x = "Freshness of Review")
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
-  scale_x_log10(n.breaks = 8)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_log10(n.breaks = 7)+
   labs(x = "log10(Freshness of Review + 1)")
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
-  scale_x_continuous(n.breaks = 8)+
-  labs(y = NULL, x = "Freshness of Review")
+  scale_x_continuous(n.breaks = 6)+
+  labs(y = "Count", x = "Freshness of Review")
 
@@
   ggplot(aes(Freshness + 1))+
-  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
-  scale_x_log10(n.break = 8)+
-  labs(y = NULL, x = "log10(Freshness of Review + 1)")
+  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
+  scale_x_log10(n.break = 6)+
+  labs(y = "Count", x = "log10(Freshness of Review + 1)")
 
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
-  scale_x_continuous(n.breaks = 8)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous(n.breaks = 6)+
   labs(x = "Freshness of Review")
@@
   geom_point(alpha = 0.1)+
-  geom_smooth(color = "steelblue")+
-  scale_x_log10(n.breaks = 8)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_log10(n.breaks = 6)+
   labs(x = "log10(Freshness of Review + 1)")
@@
   scale_x_continuous(n.breaks = 8)+
-  labs(y = NULL, x = NULL)
+  labs(y = "Count", x = "Log10(Proportion of Positive Words)")
 
@@
 
-Total Votes is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].
+The number of Total Votes is going to be used as a control variable since 80% Perceived Helpfulness can arise from both 4 Helpful votes over 5 Total votes or 80 Helpful votes over 100 Total votes [@mudambi2010; @liu2014; @choi2020].
+
+From Figures \@ref(fig:Search-Total) (B) and \@ref(fig:Experience-Total) (B) it can be observed that logarithmic transformation scales the variable in a better way for both good types.
+This is also good for linear models.
+Distributions for both good types are looking similar.
+There is a little difference though.
+Movies got voted many more times than search goods.
+This makes sense because relatively older movies are present in the data.
+In the case of electronics, it is hard to find reviews for older devices because they are not sold anymore so it is impossible to vote on them.
+This explains why there are so few amount of highly voted reviews for search goods.
+
+```{r Search-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Search Goods and respective logarithmic transformations (B), (D)"}
+p1 <- search_goods %>% 
+  ggplot(aes(Total_Vote))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 7)+
+  labs(y = "Count", x = "Total Vote")
+
+p1_log <- search_goods %>% 
+  ggplot(aes(Total_Vote))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  scale_x_log10(n.break = 7)+
+  labs(y = "Count", x = "log10(Total Vote)")
+
+p2 <- search_goods %>% 
+  ggplot(aes(Total_Vote, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous(n.breaks = 7)+
+  labs(x = "Total Vote")
+
+p2_log <- search_goods %>% 
+  ggplot(aes(Total_Vote, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_log10(n.breaks = 7)+
+  labs(x = "log10(Total Vote)")
+
+plots <- (p1 + p1_log) / (p2 + p2_log)
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+
+```
+
+On Figures \@ref(fig:Search-Total) (C) and (D) the smoother line may look like a straight horizontal line because the plot is small but there exist a weak negative slope.
+This might indicate two things.
+There is no association between these two variables or there is a negative relationship.
+
+Figure \@ref(fig:Experience-Total) (C) and (D) show a different story. Figures might indicate that there is a positive relationship between these two variables.
+
+Nonetheless, it should be noted that the variable Total Votes is the denominator part of the dependent variable Perceived Helpfulness so any interpretations to these plots should be done with care.
+
+```{r Experience-Total, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Total Votes for Experience Goods and respective logarithmic transformations (B), (D)"}
+p1 <- movies_data %>% 
+  ggplot(aes(Total_Vote))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  scale_x_continuous(n.breaks = 7)+
+  labs(y = "Count", x = "Total Vote")
+
+p1_log <- movies_data %>% 
+  ggplot(aes(Total_Vote))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
+  scale_x_log10(n.break = 6)+
+  labs(y = "Count", x = "log10(Total Vote)")
+
+p2 <- movies_data %>% 
+  ggplot(aes(Total_Vote, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous(n.breaks = 7)+
+  labs(x = "Total Vote")
+
+p2_log <- movies_data %>% 
+  ggplot(aes(Total_Vote, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_log10(n.breaks = 6)+
+  labs(x = "log10(Total Vote)")
+
+plots <- (p1 + p1_log) / (p2 + p2_log)
+
+plots + plot_annotation(
+  tag_levels = "A"
+)
+
+```
 
@@
 
-Tobit regression results are presented at Table \@ref(tab:Reg-Results) alongside with OLS results as a benchmark [@mudambi2010; @kuan2015; @choi2020].
+Tobit regression results are presented at Table \@ref(tab:Reg-Results-Tobit) alongside with OLS results as a benchmark at Table \@ref(tab:Reg-Results-OLS) [@mudambi2010; @kuan2015; @choi2020].
 
@@
 
-```{r Reg-Results, results='asis'}
+```{r Reg-Results-Tobit, results='asis'}
 
 stargazer(list("Search Tobit" = search_tobit,
-               "Experience Tobit" = experience_tobit,
-               "Search Linear" = search_lm,
+               "Experience Tobit" = experience_tobit),
+          type = "latex",
+          notes.align = "l",
+          header = FALSE,
+          model.numbers = FALSE,
+          column.labels = c("Search", "Experience"),
+          covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
+                               "log10(Total Vote)", "log10(Freshness + 1)",
+                               "Positive Proportion",  
+                               "Negative Proportion", "Rating x Review Length"),
+          star.cutoffs = c(0.05, 0.01, 0.001),
+          label = "tab:Reg-Results-Tobit",
+          title = "Tobit Regression Results")
+```
+
+```{r Reg-Results-OLS, results='asis'}
+
+stargazer(list("Search Linear" = search_lm,
                "Experience Linear" = experience_lm),
@@
           model.numbers = FALSE,
-          column.labels = c("Search", "Experience", "Search", "Experience"),
+          column.labels = c("Search", "Experience"),
           covariate.labels = c("Rating", "Rating Squared", "log10(Review Length)",
@@
           star.cutoffs = c(0.05, 0.01, 0.001),
-          label = "tab:Reg-Results")
+          label = "tab:Reg-Results-OLS",
+          title = "OLS Regression Results")
 ```
@@
 Further filtering was not pursued because of potential dangers of hypothesis fishing.
-(The results in Table \@ref(tab:Reg-Results) are the results with the filter.)
+(The results in Tables \@ref(tab:Reg-Results-Tobit) and \@ref(tab:Reg-Results-OLS) are the results with the filter.)
 

### 2022-11-02 Paper.Rmd
numerous additions
good usage of comments very nice bruh

@@
 Electronic shopping brought many advantages both for sellers and buyers.
-One of the positive perks is Online Customer Reviews (OCR).
-Online Customer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010].
+One of the positive perks is Online Consumer Reviews (OCR).
+Online Consumer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010].
 OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].
@@
 
-The research on Online Customer Reviews could be considered to have two main branches.
+The research on Online Consumer Reviews could be considered to have two main branches.
 One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012].
@@
 
-Online Customer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited.
+Online Consumer Reviews from IMDB were collected as an experience goods data since movies can be considered as pure-experience goods and their search attributes are very limited.
 It is nearly impossible to evaluate a movie before watching it.
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Helpfulness)), size = 1, alpha = 0.6)+
+  annotate(geom = "label",
+           x = mean(search_goods$Helpfulness), y = Inf,
+           label = paste("Mean:", round(mean(search_goods$Helpfulness), digits = 2)),
+           vjust = 1, hjust = 1, size = 5)+
   scale_x_continuous(n.breaks = 10)+
@@
 ```{r IV-Hist-Exp, fig.cap="Distribution of the Helpfulness of Experience Goods"}
+
 movies_data %>% 
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Helpfulness)), size = 1, alpha = 0.6)+
+  annotate(geom = "label",
+           x = mean(movies_data$Helpfulness), y = Inf,
+           label = paste("Mean:", round(mean(movies_data$Helpfulness), digits = 2)),
+           vjust = 1, hjust = 1, size = 5)+
   scale_x_continuous(n.breaks = 10)+
@@
   geom_bar(fill = "steelblue")+
+  geom_vline(aes(xintercept = mean(Rating)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Rating), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Rating), digits = 2)),
+           vjust = 1, hjust = 1, size = 4.5)+
   labs(y = "Count", x = "Review Rating")
@@
   geom_bar(fill = "steelblue")+
+  geom_vline(aes(xintercept = mean(Rating)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Rating), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Rating), digits = 2)),
+           vjust = 1, hjust = 1, size = 4.5)+
   scale_x_continuous(n.breaks = 10)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Word_Count), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Word_Count), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Word_Count), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Word_Count), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_log10(n.break = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Word_Count), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Word_Count), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  geom_vline(aes(xintercept = mean(Word_Count)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Word_Count), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Word_Count), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_log10(n.break = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Freshness), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Freshness), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_log10(n.break = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Freshness), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Freshness), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 6)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
+  geom_vline(aes(xintercept = mean(Freshness)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Freshness), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Freshness), digits = 0)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_log10(n.break = 6)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(negative)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$negative), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$negative), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(negative)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$negative), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$negative), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(positive)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$positive), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$positive), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(positive)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$positive), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$positive), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 8)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Total_Vote), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Total_Vote), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 10)+
+  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(search_goods$Total_Vote), y = Inf, 
+           label = paste("Mean:", round(mean(search_goods$Total_Vote), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_log10(n.break = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Total_Vote), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Total_Vote), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_continuous(n.breaks = 7)+
@@
   geom_histogram(color = "white", fill = "steelblue", boundary = 1)+
+  geom_vline(aes(xintercept = mean(Total_Vote)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = mean(movies_data$Total_Vote), y = Inf, 
+           label = paste("Mean:", round(mean(movies_data$Total_Vote), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
   scale_x_log10(n.break = 6)+
@@
 
-This study collected Online Customer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty.
+This study collected Online Consumer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty.
 Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer.
@@
 An objective way to identify and index experience and search attributes may also shed some light to the conflicting results in the literature.
-Lastly, since Online Customer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works.
+Lastly, since Online Consumer Reviews data is ever growing more researchers should incorporate Exploratory Data Analysis into their works.
 Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic.
-In addition, new ways to analyze text data are being developed so Online Customer Reviews offer a great potential for new discoveries from the data.
+In addition, new ways to analyze text data are being developed so Online Consumer Reviews offer a great potential for new discoveries from the data.
 This increases the value of EDA as well.

### 2022-11-03 Paper.Rmd
extend intro, lit_rev, theory

@@
 The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021].
-Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of customer reviews.
+Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of consumer reviews.
 Additionally, not all reviews have the same informativeness level [@pan2011].
-Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews can only increase the search cost.
+Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews without getting useful information can only increase the search cost.
 To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].
+
+Having a good understanding of how consumers handle information and how their behaviors change with respect to information they are exposed to might even unearth newer tools to increase the social welfare because it would lead to decreased level of information asymmetry.
+The decreased information asymmetry might produce two benefits.
+First, consumers can learn to evaluate the quality of the products before purchase much more efficiently.
+This leaves less room for any dis-utility that can arise from purchasing a sub-par quality product.
+The second, the increased knowledge of the consumers towards certain products may even facilitate competition among firms.
+This competition may lead increased quality of the products as well as decreased prices in a given market.
+This is why understanding the determinants of a helpful review is important because it might reveal new insights on consumer behavior and these new insights could be used in favor of both consumers are producers.
 
@@
 Because of this reason, more empirical studies on perceived helpfulness are required.
-This paper aims to add one more perspective to the growing literature of customer reviews and review helpfulness.
+This paper aims to add one more perspective to the growing literature of customer reviews and review helpfulness by employing a unique data set as well as questioning the subject with the intuition of economics.
+Furthermore, this paper tries to show that unstructured data (e.g., text, image, etc.) is viable for economic research.
+With unstructured data, economics may be able to explore new venues.
 
@@
 On the contrast, positive reviews with fewer words were deemed more helpful by readers on the average.
+In addition, the sentiment of a review has also a significant effect on the helpfulness of a review.
 These effects were further moderated by product types, namely, Search and Experience goods.
@@
 In the next section, the literature on the subject of Review Helpfulness is going to be presented.
-In the third section, the related theories which would make the understanding of the consumer behavior and review helpfulness will be laid out.
+In the second section, the related theories which would help with the understanding of the consumer behavior and review helpfulness will be laid out.
 Next, the data and the research methodology are going to be introduced.
-The results will be shared in the fifth section.
-In the last section the results are going to be discussed and the study is going to be concluded.
+The results will be shared in the fourth section.
+In the last section the results are going to be discussed and then the study is going to be concluded.
 
@@
 
+Since there are many conflicting results in the literature of review helpfulness additional empirical contributions are important.
+As well as adding new empirical findings to the literature, this study tries to extend the potential predictors with the interaction term between review length and review rating to test for the existence of the Negativity Bias.
+Furthermore, some under-utilized predictors from the literature such as the proportion of negative words and the proportion of positive words are also used to test Negativity Bias and Loss Aversion.
+
 \newpage
@@
 This is true for cheap goods especially.
-For instance, in order to find out the best chocolate in the market it's best for the consumer to buy every other brand available and taste them.
+For instance, in order to find out the best chocolate in the market it is best for the consumer to buy every other brand available and taste them.
 Thus, consumers will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
@@
 Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones.
-Someone else's hair in one's meal has the potential of ruining the whole meal.
-On the contrary a plate of hair will not turn to a delicious meal just because there is a slice of a delicious pizza on top of the hair.
+In @rozin2001 's words Negativity Bias can be best exemplified such as following:
+
+> *"Brief contact with a cockroach will usually render a delicious meal inedible.
+The inverse phenomenon rendering a pile of cockroaches on a platter edible by contact with one's favorite food-is unheard of.
+More modestly, consider a dish of a food that you are inclined to dislike: lima beans, fish, or whatever.
+What could you touch to that food to make it desirable to eat- that is, what is the anti-cockroach?
+Nothing!
+And the cockroach is far from unique: there is a wide variety of animals (e.g., worms, caterpillars, slugs, spiders) that share the cockroach potency, along with a variety of microbially or toxin-contaminated objects.
+One of the best generic descriptions of this relative power of negative contamination is embedded in an age old Russian adage: 'A spoonful of tar can spoil a barrel of honey, but a spoonful of honey does nothing for a barrel of tar.'"*
+
 @rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects.
@@
 This means that negative entities have higher weight than positive entities.
-This is apparent in religions.
-For the most of the religions being a good and pious person takes time, demands utmost care.
-However, tainting this image is very easy with certain actions such as murder or pre-martial intercourse.
+@rozin2001 also puts forwards as an example:
+
+> *''The image that comes to mind from the physical domain is that of a single cancerous growth or germ that radiates itself through and ultimately consumes a perfectly healthy body.
+The image that comes to mind from the moral domain is that of a single vice corrupting and perverting and bringing the moral downfall of an otherwise perfectly good person.''*
 

### 2022-11-05 Paper.Rmd
extend conclusion/EDA

@@
 > *"Brief contact with a cockroach will usually render a delicious meal inedible.
-The inverse phenomenon rendering a pile of cockroaches on a platter edible by contact with one's favorite food-is unheard of.
+The inverse phenomenon rendering a pile of cockroaches on a platter edible by contact with one's favorite food is unheard of.
 More modestly, consider a dish of a food that you are inclined to dislike: lima beans, fish, or whatever.
-What could you touch to that food to make it desirable to eat- that is, what is the anti-cockroach?
+What could you touch to that food to make it desirable to eat that is, what is the anti-cockroach?
 Nothing!
@@
 
-The ratio of helpfulness is derived from the formula above. Below on Figure \@ref(fig:IV-Hist-Search) the distribution of the helpfulness for search goods can be observed.
+The ratio of helpfulness is derived from the formula above.
+Below on Figure \@ref(fig:IV-Hist-Search) the distribution of the helpfulness for search goods can be observed along with the sample mean value which is represented as a vertical line.
 
@@
 
+Black vertical lines show the mean ratings for both product types.
+It is nice to see that averages are close to the neutral rating of 3.
+With this it can be made sure that reviews do not appeal to positive or negative side only.
+
 Because the data was taken from two different websites (BestBuy and IMDB), there are two different scales.
@@
 For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).
+As it can be observed from the vertical mean lines the reviews of the experience goods tend to be longer than the reviews of the search goods.
 
@@
 Interestingly, even after 3 years from the release date some products are still getting reviewed from customers.
+Vertical mean lines indicate that the products in the experience goods sample are older than the products in the search goods sample because the margin between the first review for a given product and last review for a given product is wider.
 
@@
 On plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words.
+For example in this case the mean negative proportion rate is 2,3% ($10^{0.37}$) for search goods and 3,7% ($10^{0.57}$) for experience goods.
 It should be noted that `r round(mean(search_goods$negative == 0), digits = 2)` percent of the reviews for search goods do not have any negative words in them.
@@
 `r round(mean(search_goods$positive == 0), digits = 2)` percent of the reviews of search goods do not have any positive words in them and this number is only `r round(mean(movies_data$positive == 0), digits = 2)` for experience goods.
+Mean proportion values are 4,4% ($10^{0.64}$) and 5,2% ($10^{0.72}$) for search and experience goods respectively.
 Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).
@@
 
-This study collected Online Consumer Reviews data from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty.
+Online Consumer Reviews data were collected from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty in this study.
 Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer.
@@
 This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB.
-In addition, to my knowledge, this the first study which analyzed the linear interaction between Review Length and Review Rating in terms of Negativity Bias Theorem.
+In addition, to my knowledge, this the first study which analyzed the linear continuous interaction between Review Length and Review Rating in terms of Negativity Bias Theorem.
+Additionally, there is a lack of emphasis on the sentiment analysis in the existing literature.
+By employing positive and negative sentiments in terms of Negativity Bias and Prospect Theory this study shows the viability of the sentiment analysis in this context.
 
@@
 The results are only generalizable to laptops, phones, televisions and movies since different goods have different mix of search and experience attributes.
+
+Findings show the importance of information sharing for an average online consumer at least for the search goods.
+Since helpful reviews aid consumers deal with their uncertainty by helping them acquire information concerning the quality of a given product, attendance to information sharing either by writing reviews or voting if the reviews are helpful or not is strongly advised.
+Search goods results at Table \@ref(tab:Reg-Results-Tobit) can be used as a guide for writing a review.
+The guidelines can be listed such as this:
+
+1.  Reviewers should only write a review when their opinions of a given product is rather extreme.
+2.
+Reviewers should share all the information and the experience they accumulated about the product without making it too long because it was observed that helpfulness shows diminishing returns to additional words.
+The review should be clear and to the point.
+3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong with the given product.
+4.
+When reviewers are reviewing a product which they are extremely unhappy about they should give more details and elaborate, on the opposite, when they are content they should write relatively shorter reviews.
+5.  Since recent reviews were found to be more helpful on the average, sharing updated information, i.e, writing new reviews is important and encouraged.
+
+With this way consumers would be able to purchase the best good available in the market with respect to their budgets, i.e., maximizing their utilities.
+This collective behavior may even impact social welfare positively since economic agents are making much more informed decisions.
+Unfortunately, similar implications can not be made for experience goods, specifically for movies, since the realized results were mostly different that what was hypothesized.
+Thus, this study can not offer any suggestions for movie reviews.
 

### 2022-11-05 Paper.Rmd
minor fixes

@@
 Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] .
-Search goods, by nature, have traits that can be observed objectively before buying (GHz of a CPU of a Laptop).
-On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (One needs to watch a movie in order to understand if it is a good movie or not.).
+Search goods, by nature, have traits that can be observed objectively before buying (e.g., GHz of a CPU of a Laptop).
+On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (e.g., One needs to watch a movie in order to understand if it is a good movie or not.).
 
@@
 Any website which offer online reviews for products could be used as a data source (Yelp, Booking, BestBuy, eBay) in the literature of review helpfulness but the majority of the aforementioned studies used the data either from websites Amazon or Internet Movie Database (IMDB) because these websites offer relatively easier ways to get the needed data.
-They have their respective APIs and on top of that, it is relatively easier to scrape both websites.
+They have their respective APIs (Application Programming Interface) and on top of that, it is relatively easier to scrape both websites.
 Additionally, both websites offer product reviews for a numerous different types of products.
@@
 It is nearly impossible to evaluate a movie before watching it.
-Furthermore, evaluations for a movie can both have subjective (personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (writing, production quality etc.).
+Furthermore, evaluations for a movie can both have subjective (e.g., personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (e.g., writing, production quality etc.).
 There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].
@@
 @jebb2017 discusses that EDA encourages scientific replication if done properly.
-As a researcher, I believe the same notion that transparently sharing the data that I used in the study increases the research's reproducibility value.
-I also think that readers or fellow researchers might build a better intuition about the discussion and what goes into the model in this study.
+This section is going to be constructed with two notions in mind:
+
+1.  Transparent data sharing for the sake of increased reproducibility value
+
+2.  Helping readers build a better intuition about the model and its components through transparency
 
@@
 This might be because evaluation process of movies is rather subjective.
-One person might not like Spider-Man: Homecoming and another would love it.
+For instance, one person might not like Spider-Man: Homecoming and another would love it.
 This might depend on how a person idealizes the Spider-Man or Peter Parker image in her mind which is completely subjective.
@@
 Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have.
-However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer.
+However, since the attributes of electronics are objectively identifiable and limited (e.g., storage space of a phone, RAM of a laptop, color depth of a TV etc.) there are not much to review for a reviewer.
 Because of this, there might be diminishing marginal returns to Review Length.
@@
 Since there are less objectivity, a helpful review to one person might not be helpful to another.
-This might decrease the average responsivess of the Perceived Helpfulness to the Review Length.
+This might decrease the average responsiveness of the Perceived Helpfulness to the Review Length.
 However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected.

### 2022-11-07 Paper.Rmd
many fixes :(

@@
 csl: apa.csl
+toc: no
 link-citations: yes
@@
 Online Consumer Reviews come in the form of electronic word-of-mouth [@dellarocas2003] and can be defined as "*peer-generated product evaluations posted on company or third party websites*" [@mudambi2010].
-OCR have an effect on product sales as well as consumer decision making [@duan2008; @lee2011; @dellarocas2007].
-
-OCR help customers by decreasing their search costs.
-Customers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product.
-This information acquiring process is costly.
-Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970] .
+OCR were found to have an effect on product sales as well as consumer decision making process.
+[@duan2008; @lee2011; @dellarocas2007].
+
+OCR help customers by decreasing their search costs because it is easier for the consumer to skim through many reviews on the internet than finding and asking people who actually bought the product in question.
+Consumers try to get information on the product they are going to buy so that they can decrease the uncertainty about that particular product.
+This information acquiring process (search) is costly.
+Furthermore, this information gathering process might be more or less costly depending on the product type, namely Search and Experience goods [@nelson1970].
 Search goods, by nature, have traits that can be observed objectively before buying (e.g., GHz of a CPU of a Laptop).
-On the other hand, quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (e.g., One needs to watch a movie in order to understand if it is a good movie or not.).
+On the other hand, the quality of Experience goods can not be evaluated before buying and evaluations could be very subjective (e.g., One needs to watch a movie in order to understand if it is a good movie or not.
+Also a movie being good or bad might depend on who watched it because people have different tastes.).
 
@@
 The vast amount of product reviews might increase the information overload on the customer [@sun2019; @fan2021].
-Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousand of consumer reviews.
-Additionally, not all reviews have the same informativeness level [@pan2011].
-Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews without getting useful information can only increase the search cost.
-To make the understanding of a "helpful review" more clear it can be defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].
-
-Having a good understanding of how consumers handle information and how their behaviors change with respect to information they are exposed to might even unearth newer tools to increase the social welfare because it would lead to decreased level of information asymmetry.
+Unfortunately, this information overload can make the search process even costlier because it is really time consuming to evaluate thousands of consumer reviews.
+Besides, not all reviews have the same informativeness level [@pan2011].
+Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews without getting useful information can only increase the search costs.
+On top of this, the overload of useless information might impair the decision making ability of the potential buyer.
+To make the understanding of a "helpful review" more clear it can be strictly defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].
+
+Having a good understanding of how consumers handle information and how their behaviors change with respect to information they are exposed to might even unearth newer tools to increase the social welfare because it would lead to a decreased level of information asymmetry between consumers and producers.
 The decreased information asymmetry might produce two benefits.
@@
 Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
-On some websites, this feature is implemented in a way that helpful / unhelpful buttons are present and on some other websites, there is only a helpful button.
-In this study, the data was acquired from websites which support helpful / unhelpful system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].
+On some websites, this feature is implemented in a way that *helpful* / *unhelpful* buttons are present and on some other websites, there is only a *helpful* button.
+In this study, the data was acquired from websites which support *helpful* / *unhelpful* system since it was found that helpfulness as a percentage (helpful votes over total votes) creates more powerful results than considering only helpful votes as a count variable [@ahmad2015].
 
 The research on perceived helpfulness is still growing.
-In Social and Behavioral Sciences, it is common to have conflicting papers and results in the literature [@hunter1991].
+In Social and Behavioral Sciences, it is common to have conflicting studies and results in the literature [@hunter1991].
 In this case, the study on perceived helpfulness is not an exception.
 Because of this reason, more empirical studies on perceived helpfulness are required.
-This paper aims to add one more perspective to the growing literature of customer reviews and review helpfulness by employing a unique data set as well as questioning the subject with the intuition of economics.
-Furthermore, this paper tries to show that unstructured data (e.g., text, image, etc.) is viable for economic research.
+This study aims to add one more perspective to the growing literature of customer reviews and review helpfulness by employing a unique data set as well as questioning the subject with the intuition of economics.
+Furthermore, this study tries to show that unstructured data (e.g., text, image, etc.) is a viable option for economic research.
 With unstructured data, economics may be able to explore new venues.
@@
 The results will be shared in the fourth section.
-In the last section the results are going to be discussed and then the study is going to be concluded.
+In the fifth section the results are going to be discussed and then the study is going to be concluded in the last section.
 
@@
 
-The research on Online Consumer Reviews could be considered to have two main branches.
+The research on Online Consumer Reviews can be considered to have two main branches.
 One branch is heavily marketing oriented and tries to understand the effects of OCR on sales [@ghose2011; @ögüt2012].
@@
 The boundary between these two branches are somewhat blurry and the same independent variables were used to explain both helpfulness and sales.
-Furthermore, @topaloglu2019 found that helpfulness have a moderating effect on sales.
-Many other papers used perceived helpfulness to explain sales as well [@ghose2011; @lee2018].
+Furthermore, @topaloglu2019 found that review helpfulness have a moderating effect on sales.
+Many other papers used the perceived helpfulness to explain sales as well [@ghose2011; @lee2018].
 Thus, these two branches are inter-connected with each other.
-This paper tries to understand behavioral aspect of the review helpfulness rather than its effects on sales.
-
-Many independent variables and their relationship between perceived helpfulness were examined by researchers.
+Contrary to sales oriented papers which were mentioned above, this study tries to understand behavioral aspects of the review helpfulness rather than its effects on sales.
+
+Many different independent variables and their relationship between perceived helpfulness were examined by researchers.
 @hong2017 groups these independent variables into two chunks.
@@
 [@sun2019; @ghose2011].
-The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc [@mudambi2010; @ghose2011; @ren2019; @eslami2018].
+The second group tries to understand the review-related relationships such as review length, review extremity, discrete review emotion etc.
+[@mudambi2010; @ghose2011; @ren2019; @eslami2018].
 @ghose2011 showed that review-related predictors have stronger prediction power than reviewer-related ones.
+It should be noted that these two groups are not mutually exclusive and can be employed in the same study.
 The choice of the variables is heavily dependent on the data itself.
-In my paper, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.
-
-Review Length (Depth) could be considered as one of the most important independent variable explaining perceived helpfulness.
+In this particular study, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.
+Reviewer-related variables could not be employed because IMDB and BestBuy use different conventions to identify their users(reviewers).
+
+Review Length (Depth) could be considered as one of the most important independent variable explaining the perceived helpfulness.
 It might be implemented in different ways but for the majority of the studies it is the word count in a given review.
-For most of the researchers, longer reviews contain more information about the product.
+For the most of the researchers, longer reviews contain more information about the product.
 As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020].
-However, other group of researchers found out that there was a threshold on review length, meaning longer reviews might have useless information in them[@schindler2012; @huang2015].
+However, other group of researchers found out that there was a threshold on review length, meaning unnecessarily long reviews might have useless information in them[@schindler2012; @huang2015].
 Another group indicates the word count of the review shows diminishing returns to helpfulness, supporting the threshold idea [@baek2012; @kuan2015; @eslami2018].
@@
 A number of researchers found out that there is a non-linear relationship between review extremity and perceived helpfulness.
-Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews[@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006].
+Specifically, a U-Shaped function which means that reviews that are on the extremes (either very negative or very positive) are more helpful than neutral reviews [@mudambi2010; @cao2011; @liu2014; @wang2018; @ghose2006].
 In other studies, linear positive relationship was found.
 In other words, positively rated reviews are more useful [@pan2011; @schindler2012; @korfiatis2012; @lee2016; @choi2020].
-There are also results that support negative linear relationship[@chua2014] and no effect at all[@hong2017].
+There are also results that support negative linear relationship [@chua2014] and no effect at all [@hong2017].
 
 Review Age is an indicator of how long the time passed after a review published on a web site.
-On some papers the opposite of Review Age, Review Freshness (Recency) could be employed as well.
+In some papers the opposite of Review Age, Review Freshness (Recency) could be employed as well.
 Different effects on perceived helpfulness were also observed by researchers.
-Some researchers discussed that a timely review is very important at conveying the true information about a certain product [@liu2014; @li2019; @zhou2019].
-Others discussed that some web sites promotes newer reviews and because of that more recent reviews are more helpful [@lee2014; @choi2020; @wu2021].
+Some researchers discussed that a timely review is very important at conveying the true information about a certain product, making older reviews more helpful [@liu2014; @li2019; @zhou2019].
+Others discussed that some web sites promote newer reviews and recent information is much more valuable than old information.
+Because of these more recent reviews can be considered as more helpful [@lee2014; @choi2020; @wu2021].
 
@@
 These metrics can measure the sentiment of the review itself.
-They are usually different than Review Extremity.
+They are usually different than Review Extremity (Review Rating).
 In most cases Review Extremity and Review Sentiment (Valence) do not match [@zhang2011].
@@
 Furthermore, Ordinary Least Squares was employed in a hierarchical manner as well [@baek2012].
-Some other studies employed Multi-Level Regression models in order to deal with potential biases [@ghose2011; @wu2021; @kuan2015].
+Some other studies employed Multi-Level Regression model in order to deal with the potential selection bias which is present in the data [@ghose2011; @wu2021; @kuan2015].
 In a rare case Ordinal Logistic Regression was one of the methods that was used to explain the determinants of the review helpfulness [@cao2011].
@@
 Since there are many conflicting results in the literature of review helpfulness additional empirical contributions are important.
-As well as adding new empirical findings to the literature, this study tries to extend the potential predictors with the interaction term between review length and review rating to test for the existence of the Negativity Bias.
+As well as adding new empirical findings to the literature, this study tries to extend the potential predictors with the continuous interaction term between review length and review rating to test for the existence of the Negativity Bias.
 Furthermore, some under-utilized predictors from the literature such as the proportion of negative words and the proportion of positive words are also used to test Negativity Bias and Loss Aversion.
@@
 Relaxing the assumption that consumers have perfect information about the products on the market raises the problem of information acquisition for consumers.
-Getting the complete information about products is important because economic agents want to maximize their utility by finding the best good on the market.
+Getting the complete information about products is important because economic agents want to maximize their utility by finding the best good with respect to their budget constraints on the market.
 The complete information is the information about both the prices and quality levels of the goods which are available on the market.
-Acquiring the information of the quality of a product is harder than getting the information about its price.
-To explain, a consumer can check the price list of laptops and have an idea about maximum and minimum prices but getting the information about a laptop's technical components or a brand's support for its products is a lot more effort taking and costly.
+Acquiring the information about the quality of a product is harder than getting the information about its price.
+To explain, a consumer can check the price list of laptops and have an idea about the maximum and the minimum prices but getting the information about a laptop's technical components or a brand's support for its products is a lot more effort taking and costly.
 
@@
 For instance, in order to find out the best chocolate in the market it is best for the consumer to buy every other brand available and taste them.
-Thus, consumers will always prefer sampling or trial use given the fact that the cost of the sampling or trial is lower than the cost of the search.
+Thus, consumers will always prefer sampling or trial use (experiencing the product) given the fact that the cost of the sampling or trial is lower than the cost of the search.
 This is why search is costlier for Experience goods.
@@
 @nelson1970 also states that consumers can use other consumers' experiences in their search processes.
-The information about a certain good is usually acquired in the form of "word-of"mouth" in this kind of search process.
+The information about a certain good is usually acquired in the form of "word-of-mouth" in this kind of search process.
 This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search".
+For instance buying a laptop and trying to figure out if it is the best laptop for a certain task may even require buying additional laptops because of the need for comparison.
+This is the way of "experiencing" the good and this would be very costly.
+On the other hand, the potential buyer may want to hear from people who do the similar tasks with their laptops and try to sort out the best possible laptop model for her own task.
+This way she gets information about the product without having to "experience" it and this approach is way cheaper.
+
 @klein1998 discusses that experience sharing becomes easier with the increasing usage of the internet.
@@
 The increasing use of internet decreases the search costs.
-Because of the decreased search costs, the consumer may undertake more search processes and this might change how people perceive good types, in other words, internet and virtual experience sharing can convert some Experience goods to Search goods [@klein1998].
+Because of the decreased search costs, the consumer may undertake more search processes and this might change how people perceive the good types, in other words, internet and virtual experience sharing can convert some Experience goods to Search goods [@klein1998].
 
@@
 Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones.
-In @rozin2001 's words Negativity Bias can be best exemplified such as following:
+In @rozin2001's words Negativity Bias can be best exemplified such as the following:
 
@@
 Nothing!
-And the cockroach is far from unique: there is a wide variety of animals (e.g., worms, caterpillars, slugs, spiders) that share the cockroach potency, along with a variety of microbially or toxin-contaminated objects.
+.
+.
+.
 One of the best generic descriptions of this relative power of negative contamination is embedded in an age old Russian adage: 'A spoonful of tar can spoil a barrel of honey, but a spoonful of honey does nothing for a barrel of tar.'"*
@@
 In other words, negative events are much more impactful than their exact positive counterparts.
-For instance, losing 100\$ could have a harder psychological effect on a person than that particular person is gaining 100\$.
+For instance, losing 300\$ could have a harder psychological effect on a person than that particular person is gaining 300\$.
 Loss Aversion [@kahneman1979; @tversky1991] is the phenomenon where the Negative Potency can be observed the best.
@@
 In other words, negative things cause more negativity as the time goes on.
-At the very least, the effects of negativeness are a lot more long-standing than effects of positiveness.
+At the very least, the effects of the negativeness are a lot more long-standing than effects of the positiveness.
 
@@
 
-> *''The image that comes to mind from the physical domain is that of a single cancerous growth or germ that radiates itself through and ultimately consumes a perfectly healthy body.
-The image that comes to mind from the moral domain is that of a single vice corrupting and perverting and bringing the moral downfall of an otherwise perfectly good person.''*
+> *"The image that comes to mind from the physical domain is that of a single cancerous growth or germ that radiates itself through and ultimately consumes a perfectly healthy body.
+The image that comes to mind from the moral domain is that of a single vice corrupting and perverting and bringing the moral downfall of an otherwise perfectly good person."*
 
 **Greater Negative Differentiation** discusses the possibility that human cognition is fine-tuned to negative entities because being aware of negative stimuli might correlate with survival in the process of the evolution.
-As a consequence, the vocabulary that reflects and describes the state of negativeness is much more wider than its counterpart positiveness.
+As a consequence, the vocabulary that reflects and describes the state of the negativeness is much more wider than its counterpart the positiveness.
 [@peeters1971].
@@
 The data was scraped with a custom web scraper which was constructed with Selenium Framework for Python 3 [@python3].
-The scraper got the customer reviews from IMDB and BestBuy.
+The scraper aqcuired the customer reviews from IMDB and BestBuy.
 The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America.
@@
 Furthermore, evaluations for a movie can both have subjective (e.g., personal attachment to the protagonist, atmosphere of the movie etc.) and objective aspects (e.g., writing, production quality etc.).
-There are also numerous studies that analyzed movies as experience goods[@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].
+There are also numerous studies that analyzed movies as experience goods [@nelson1970; @liu2014; @ghose2006; @baek2012; @lee2016].
 
@@
 Additionally, in the literature, TVs, Laptops and Phones were used as search goods [@mudambi2010; @sun2019; @baek2012; @ren2019].
-Therefore, search goods data was collected from BestBuy.
+Therefore, search goods data was collected from BestBuy as it was a very suitable candidate for this research.
 
@@
 Once a helpful review is written most of the other reviews become redundant since other reviews most likely convey similar information.
-On the contrary, more attendance to reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times.
+On the contrary, more attendance to the reviews can be observed for experience goods (movies) since nearly half of them were voted at least five times.
 This might be because people form heterogeneous opinions about experience goods [@hong2014].
@@
 The goal of this section is not "confirmatory" whatsoever.
-Both dependent and independent variables are going to be introduced with an emphasis on their quantitative features such as their distributions and potential transformations which can be applied to the variables in question.
+Both dependent and independent variables are going to be introduced with an emphasis on their quantitative features such as their distributions and potential transformations which can be applied to the variable in question.
 In addition to this, bivariate relations between independent and dependent variables will be plotted in order to get an initial idea about the potential effects along with similar findings from the literature.
@@
 
-As it can be seen the distribution is rather skewed.
+As it can be seen the distribution is very skewed.
 Looks like in the electronics case, readers find some reviews very helpful.
@@
 
-On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard errors will be calculated correctly or not in a regression method.
-@li2012 found out that given a relatively high sample size (\>3000) linear regression techniques produces sound estimates of coefficients.
+On a small note, the way the dependent variable was distributed for search goods may raise some questions about whether the standard errors will be calculated correctly or not in a linear regression method.
+@li2012 found out that given a relatively high sample size (N \> 3000) linear regression techniques produces sound estimates of coefficients.
 Since the sample size for search goods is over 8000 it might be assumed that the use of linear regression methods is acceptable.
@@
 
-@hong2014 states that consumers likely to form homogeneous opinions about search goods [@sun2019].
-On the contrary, the same paper suggests that consumers' opinions are more heterogeneous on experience goods.
+@hong2014 states that consumers likely to form uniform opinions about search goods [@sun2019].
+On the contrary, the same paper suggests that consumers' opinions are more diversified on experience goods.
 Intuitively, what these histograms show is the same.
@@
 It is nice to see that averages are close to the neutral rating of 3.
-With this it can be made sure that reviews do not appeal to positive or negative side only.
+With this it can be made sure that the sample reviews do not address to positive or negative side only.
 
@@
 This means that reviews become less prevalent as they get longer.
-This might suggest logarithmic transformation can increase the model fit.
+This might suggest that logarithmic transformation can increase the model fit.
 For the transformed distributions see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B).
@@
 With this in mind, logarithmic transformation might make more sense (see Figure \@ref(fig:Search-Length) (D)) for modelling purposes.
-For Experience goods, on the other hand, there seems to be a weak negative relationship or no relationship at all (see Figure \@ref(fig:Experience-Length) (C) and (D)).
+For Experience goods, on the other hand, there seems to be a weak negative relationship or no relationship at all [@chatterjee2020; @yang2019] (see Figure \@ref(fig:Experience-Length) (C) and (D)).
 
@@
 ### Control Variables
+
+#### Total Votes
 
@@
 On the other hand, for Experience Goods and in the specific case of movies, opinions for a given product might be much more subjective.
-For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give 5 stars, making the helpfulness subjective and decreasing its usefulness.
+For example, a reviewer might find a movie "childish" and give it one star, another reviewer might find the movie "light-hearted and colorful" and give the movie 5 stars, making the helpfulness subjective and decreasing its usefulness.
 Furthermore, for experience goods, it was found that opposite extremes to a potential buyer's prior expectations are not impactful on the decision making process [@hoch1989].
@@
 In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods.
-Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014].
-This might mean that information cues are much more uniform for Search Goods.
-[@huang2015; @baek2012].
+Furthermore, people tend to have similar opinions about Search Goods [@hong2014].
+This might mean that information cues are much more uniform for Search Goods [@huang2015; @baek2012].
 In other words, there are limited ways to construct a review because search attributes are more objective.
@@
 
-***H2**: There is a positive relationship between logarithm of Review Length and Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.
+***H2**: There is a positive relationship between the logarithm of the Review Length and the Perceived Helpfulness. This effect is stronger for Search Goods than Experience Goods*.
 
@@
 Since people take more time to evaluate negative reviews, this may indicate that the effect of Review Length is stronger when Review Rating is low.
-And when a review is longer it is evaluated as more helpful for negatively rated reviews than positively rated reviews.
+And when a review is longer it is perceived as more helpful for negatively rated reviews than positively rated reviews.
 In this case, it is hypothesized that:
@@
 However, this time reviewers might need to take their time to digest and evaluate the movie.
-A review which is carefully constructed may be posted later making it more recent compared to a review which was hastily written.
+A review which is carefully constructed may be posted late, making it more recent compared to a review which was hastily written.
 Furthermore, some popular movies which are considered as classics may attract reviews even way later than they were first released.
@@
 
-***H5**: There is a positive relationship between the Proportion of Negative Words and Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
-***H6**: There is a negative relationship between the Proportion of Positive Words and Perceived Helpfulness for both product types.*
+***H5**: There is a positive relationship between the Proportion of Negative Words and the Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
+***H6**: There is a negative relationship between the Proportion of Positive Words and the Perceived Helpfulness for both product types.*
 
@@
 
-One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for movie reviews.
+One reason of this might be that the NRC Word-Emotion Association Lexicon which was used to mine the negative words in the reviews was not suitable for the movie reviews.
 For instance, the word "*cage"* is a negative word in the lexicon and "*marvel*" is a positive word.
@@
 Another reason may arise from the subjective nature of the experience attributes of the movies.
-Negative words, in the case of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself.
+Negative words, in the context of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself.
 The quality of the good is easily accessible because of the fact that electronics have dominant search attributes.
@@
 
+-   read the paragraph below again. my brain is fucked.
+
+There are still points to be made about the results of the movies.
+In the Section \@ref(search-and-experience-goods-classification) it was mentioned that consumers choose from two different strategies when they want to acquire information about a particular product.
+They might choose to experience the good or they can undertake search.
+It was pointed out by @nelson1970 that word-of-mouth type of information is viable when it is much more costlier to "experience" the good than undertaking a search process.
+It is probable that, in the case of movies, watching the movie (experiencing it) isn't that much costlier or maybe less costlier than gathering information about that particular movie and then making a decision on watching it.
+Thus, "search" might not be justifiable for movies.
+This might explain the unexpected results.
+Especially for the effect of the Review Length.
+
 Unexpected and different results are common in the literature of Review Helpfulness [@fan2021].
-This paper and the rest of the literature suffers from certain biases that the data imposes.
+This work and the rest of the literature suffer from certain biases that the data imposes.
 Many other limitations may arise from potential omitted variables.
 
-Firstly, as @mudambi2010 pointed out that potential selection bias exist in the data.
+Firstly, as @mudambi2010 pointed out that potential selection bias exists in the data.
 It is not possible to know how many people actually read a particular review.
@@
 For instance, review extremity was employed in three different ways by researchers.
-This paper and some others use review ratings as it is.
+This study and some others use the review ratings as it is.
 Another group of studies took the differences of review ratings from the mean rating of a given product.
@@
 
-Potential omitted variables such as consumer's buying motivation or their trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021.
-A person who is more agreeable high likely will find many more reviews helpful on the average.
+Potential omitted variables such as consumers' buying motivation or their trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021.
+A person who is more agreeable will high likely find many more reviews helpful on the average.
 Additionally, buying motivation might play an important role in explaining the review helpfulness.
@@
 
-Online Consumer Reviews data were collected from two different sources (IMDB and BestBuy) and analyzed the data within the context of consumer uncertainty in this study.
+Online Consumer Reviews data were collected from two different sources (IMDB and BestBuy) and analyzed within the context of consumer uncertainty in this study.
 Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer.
@@
 This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB.
-In addition, to my knowledge, this the first study which analyzed the linear continuous interaction between Review Length and Review Rating in terms of Negativity Bias Theorem.
+In addition, to my knowledge, this is the first study which analyzed the linear continuous interaction between the Review Length and the Review Rating in terms of Negativity Bias Theorem.
 Additionally, there is a lack of emphasis on the sentiment analysis in the existing literature.
@@
 Findings show the importance of information sharing for an average online consumer at least for the search goods.
-Since helpful reviews aid consumers deal with their uncertainty by helping them acquire information concerning the quality of a given product, attendance to information sharing either by writing reviews or voting if the reviews are helpful or not is strongly advised.
+Since helpful reviews aid consumers deal with their uncertainties by helping them acquire information concerning the quality of a given product, attendance to information sharing either by writing reviews or voting if the reviews are helpful or not is strongly advised.
 Search goods results at Table \@ref(tab:Reg-Results-Tobit) can be used as a guide for writing a review.
@@
 The review should be clear and to the point.
-3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong with the given product.
+3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong or lacking with the given product.
 4.
@@
 
-There are some implications for future studies.
+There are some implications for the future studies.
 Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text.
@@
 Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic.
-In addition, new ways to analyze text data are being developed so Online Consumer Reviews offer a great potential for new discoveries from the data.
-This increases the value of EDA as well.
+In addition, new ways to analyze the text data are being developed so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains.
+This increases the value of the Exploratory Data Analysis as well.
 

### 2022-11-08 Paper.Rmd
end of the third draft

@@
 theme_set(theme_bw(base_size = 12))
+theme_update(axis.title = element_text(size = 13),
+             axis.text = element_text(size = 12))
 
@@
 Online shopping has becoming more and more prevalent in average consumer's daily life.
-Electronic shopping brought many advantages both for sellers and buyers.
+Electronic shopping brought many advantages to both sellers and buyers.
 One of the positive perks is Online Consumer Reviews (OCR).
@@
 Therefore, answering the question of "what makes a helpful review?" is very important because reading more and more reviews without getting useful information can only increase the search costs.
-On top of this, the overload of useless information might impair the decision making ability of the potential buyer.
+On top of this, the overload of useless information might impair the decision making ability of the potential buyer, leading to a sub-optimal choice.
 To make the understanding of a "helpful review" more clear it can be strictly defined as "*a peer-generated product evaluation that facilitates the consumer's purchase decision process*" [@mudambi2010].
@@
 This competition may lead increased quality of the products as well as decreased prices in a given market.
-This is why understanding the determinants of a helpful review is important because it might reveal new insights on consumer behavior and these new insights could be used in favor of both consumers are producers.
+This is why understanding the determinants of a helpful review is important because it might reveal new insights on consumer behavior and these new insights could be used in favor of both consumers and producers.
 
@@
 On the contrast, positive reviews with fewer words were deemed more helpful by readers on the average.
-In addition, the sentiment of a review has also a significant effect on the helpfulness of a review.
-These effects were further moderated by product types, namely, Search and Experience goods.
+In addition, the sentiment of a review also has a significant effect on the helpfulness of a review.
+These effects were further moderated by product types, particularly, Search and Experience goods.
 
@@
 Predictive methods such as Neural Networks were used to understand the components of a helpful review as well [@lee2014].
-One paper attacked the problem of the review helpfulness with three methods, namely, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].
+One paper attacked the problem of the review helpfulness with three methods, specifically, Partial Least Squares - Structural Equation Modelling, ANOVA Analysis and Artificial Neural Networks [@eslami2018].
 
@@
 The information about a certain good is usually acquired in the form of "word-of-mouth" in this kind of search process.
-This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search".
+This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search", i.e., sampling the product is very costly.
 For instance buying a laptop and trying to figure out if it is the best laptop for a certain task may even require buying additional laptops because of the need for comparison.
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous(n.breaks = 7)+
   labs(y = "Count", x = "Number of the Words")
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous(n.breaks = 7)+
   labs(x = "Number of the Words")
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_continuous(n.breaks = 7)+
+  scale_x_continuous(n.breaks = 6)+
   labs(y = "Count", x = "Freshness of Review")
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_log10(n.break = 7)+
+  scale_x_log10(n.break = 6)+
   labs(y = "Count", x = "log10(Freshness of Review + 1)")
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_continuous(n.breaks = 7)+
+  scale_x_continuous(n.breaks = 6)+
   labs(x = "Freshness of Review")
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_log10(n.breaks = 7)+
+  scale_x_log10(n.breaks = 6)+
   labs(x = "log10(Freshness of Review + 1)")
@@
 The expectation was observing a negative significant coefficient for proportion of positive words and a positive significant coefficient for proportion of negative words.
-At the very least it can be said that the existence of positive words in a movie review does not offer a diagnostic value according to regression results.
+At the very least it can be said that the existence of positive words in a movie review does not offer a significant information value according to regression results.
 Thus, it is hard to say there is a strong deviation from Hypothesis 6.
@@
 Cases like these may create noise for the variable and the model because aforementioned words were used frequently and outside of the context of the lexicon.
-To test this problem words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types.
+To test this problem, negative and positive words such as "*cage, john, climax, force, king, mad, fury, hardy, margin, harry, marvel, stark, iron, vulture, green, goblin, bale*" were filtered out of the lexicon for both good types.
 Neither coefficient signs nor coefficient significances were changed.
-However, it should be pointed out that the coefficient of negative words for experience goods was weakened slightly.
+However, it should be pointed out that the magnitude of the coefficient of negative words for experience goods was weakened slightly.
 Further filtering was not pursued because of potential dangers of hypothesis fishing.
@@
 Another reason may arise from the subjective nature of the experience attributes of the movies.
-Negative words, in the context of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself.
+Negative words, in the context of electronics, may have a narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself.
 The quality of the good is easily accessible because of the fact that electronics have dominant search attributes.
@@
 
--   read the paragraph below again. my brain is fucked.
-
 There are still points to be made about the results of the movies.
 In the Section \@ref(search-and-experience-goods-classification) it was mentioned that consumers choose from two different strategies when they want to acquire information about a particular product.
-They might choose to experience the good or they can undertake search.
+They might choose to experience the good or they can undertake search in order to collect information.
 It was pointed out by @nelson1970 that word-of-mouth type of information is viable when it is much more costlier to "experience" the good than undertaking a search process.
 It is probable that, in the case of movies, watching the movie (experiencing it) isn't that much costlier or maybe less costlier than gathering information about that particular movie and then making a decision on watching it.
-Thus, "search" might not be justifiable for movies.
-This might explain the unexpected results.
-Especially for the effect of the Review Length.
+Thus, "search" might not be very justifiable for movies.
+This might explain why electronic word-of-mouth (Review Length) showed rather weaker and erratic (positive for lower ratings, negative for higher ratings) results.
 
@@
 In some studies these dummy variables were extended to negative and positive extreme dummies as well.
-The differences is not limited to Review Rating.
+The differences are not limited to Review Rating.
 The usages the dependent variable, Perceived Helpfulness, diverged as well.
@@
 
-Potential omitted variables such as consumers' buying motivation or their trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021.
+Potential omitted variables such as consumer's buying motivation or his/her trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021.
 A person who is more agreeable will high likely find many more reviews helpful on the average.
@@
 Goods with very strong search or experience attributes were chosen in order to compare the information gathering process in the clearest way possible.
-The results proves the fact that information gathering is easier for search goods than experience goods.
+The results prove the fact that information gathering is easier for search goods than experience goods.
 This means that consumers face less uncertainty against search goods.
@@
 The review should be clear and to the point.
-3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong or lacking with the given product.
+3.  Reviewers should not refrain from using negative words as long as it objectively identifies something wrong or lacking with the product which is being reviewed.
 4.
@@
 Reviews and how helpful these reviews are perceived by potential buyers is relatively a new topic.
-In addition, new ways to analyze the text data are being developed so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains.
+In addition, new ways to analyze text data are being developed since the area of Natural Language Processing is quite hot so Online Consumer Reviews offer a great potential for new discoveries from the data for different domains.
 This increases the value of the Exploratory Data Analysis as well.

### 2022-12-17 Paper.Rmd
final draft complete

@@
 documentclass: report
-title: 'Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes them helpful?'
 bibliography: references.bib
 csl: apa.csl
+lof: no
+lot: no
 toc: no
@@
 
+#title: 'Dealing with Consumer Uncertainty: Online Consumer Reviews and What makes #them helpful?'
+
 theme_set(theme_bw(base_size = 12))
@@
 # Introduction {.unnumbered}
+
+\setcounter{page}{1}
 
@@
 
-Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousand of reviews.
+Since OCR do not share the same level of informativeness and usefulness [@pan2011], most of the electronic retail websites implemented a very well known "helpfulness" feature to their customer review systems in order to help their customers navigate through thousands of reviews.
 On some websites, this feature is implemented in a way that *helpful* / *unhelpful* buttons are present and on some other websites, there is only a *helpful* button.
@@
 In this particular study, only review-related predictors were examined because the data which is available for this study only allows for review-related variables.
-Reviewer-related variables could not be employed because IMDB and BestBuy use different conventions to identify their users(reviewers).
+Reviewer-related variables could not be employed because IMDB and BestBuy use different conventions to identify their users (reviewers).
 
@@
 For the most of the researchers, longer reviews contain more information about the product.
-As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort [@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020].
+As the potential buyer gets more information from a single review, he decreases his search costs with minimum effort so the amount of information (words) that a review contains becomes very important.
+[@mudambi2010; @hong2017; @liu2014; @wang2018; @korfiatis2012; @lee2016; @lee2014; @choi2020].
 However, other group of researchers found out that there was a threshold on review length, meaning unnecessarily long reviews might have useless information in them[@schindler2012; @huang2015].
@@
 Many different types of research methodologies were employed in the literature of the Review Helpfulness.
-To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014].
+To my knowledge the most common empirical analysis method that was used in the literature was Tobit Regression because of the limited and the censored nature of the Reviews Helpfulness [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019; @chua2014].
 Some of these studies also shared Ordinary Least Squares results alongside with the Tobit Regression results for the purpose of benchmarking [@mudambi2010; @kuan2015; @choi2020].
@@
 Getting the complete information about products is important because economic agents want to maximize their utility by finding the best good with respect to their budget constraints on the market.
-The complete information is the information about both the prices and quality levels of the goods which are available on the market.
+The complete information is the information about both the prices and the quality levels of the goods which are available on the market.
 Acquiring the information about the quality of a product is harder than getting the information about its price.
-To explain, a consumer can check the price list of laptops and have an idea about the maximum and the minimum prices but getting the information about a laptop's technical components or a brand's support for its products is a lot more effort taking and costly.
+To explain, a consumer can check the price list of laptops and have an idea about the maximum and the minimum prices but getting the information about a laptop's technical components or a brand's technical support for its products is a lot more effort taking and costly.
 
@@
 Depending on its dominant attributes the good can be classified as Search or Experience.
+Thus, search and experience classification is not usually a clear cut one, rather it could be considered as a spectrum.
 @darby1973 extended Search and Experience goods framework with Credence goods where consumers can not evaluate the good even after the consumption.
@@
 @nelson1970 also states that consumers can use other consumers' experiences in their search processes.
-The information about a certain good is usually acquired in the form of "word-of-mouth" in this kind of search process.
+The information about a certain good is usually acquired in the form of "word-of-mouth" with this kind of search process.
 This type of search is viable when getting the information about a certain product is much more costly by "experience" compared to by "search", i.e., sampling the product is very costly.
@@
 The data was scraped with a custom web scraper which was constructed with Selenium Framework for Python 3 [@python3].
-The scraper aqcuired the customer reviews from IMDB and BestBuy.
+The scraper acquired the customer reviews from IMDB and BestBuy.
 The former is the biggest platform for Movies and TV Shows, the latter is one of the biggest electronic retailers in United States of America.
@@
 
+\newpage
+
 ## Exploratory Data Analysis
@@
 This might be the reason why such a big spike at 100% was observed on Figure \@ref(fig:IV-Hist-Search).
-In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the distribution of the perceived helpfulness distributed around 50%.
+In the movies (experience good) case on Figure \@ref(fig:IV-Hist-Exp), it can be seen that readers usually disagree with each other because the observations of the perceived helpfulness distributed around 50%.
 This might be because evaluation process of movies is rather subjective.
@@
 On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts.
-Furthermore, these plots kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)).
-In a sense, both negative and positive proportions imply number of words.
+Furthermore, these plots are kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)).
+In a sense, both negative and positive proportions imply the number of words.
 As the proportion increases so does the number of words.
@@
 This might decrease the average responsiveness of the Perceived Helpfulness to the Review Length.
-However, since there are other ways to objectively evaluate a movie such as quality of its effects, its budget and how well this budget is utilized, a weaker positive linear relationship is expected.
+However, since there are other ways to objectively evaluate a movie such as the quality of its effects, movie's budget and how well this budget was utilized, a weaker positive linear relationship is expected.
 Therefore it is hypothesized that:
@@
 However, Review Rating itself is not enough to convey the information about how a customer expresses her satisfaction / dissatisfaction towards a product.
-The way a customer expresses her opinion on a product might have an effect on the perceived helpfulness of a review.
+The way a customer expresses her opinion about a product might have an effect on the perceived helpfulness of a review.
 Reviews with negative sentiments may bring out the risks associated with the purchase better than reviews with positive sentiments.
@@
 For instance, potentially more voted reviews could attract more readers or readers could be drawn to reviews which have certain ratings.
-Lastly, there are many studies from the literature that used Tobit Regression as their research method [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].
+Lastly, there are many studies from the literature that used Tobit Regression as their research methods [@mudambi2010; @korfiatis2012; @huang2015; @choi2020; @ren2019].
 
@@
 This means that for positive extreme reviews relatively shorter texts are more helpful.
-Logarithmic form also proves that additional words in a review shows diminishing returns to helpfulness.
+Logarithmic form also proves that an additional word in a review shows diminishing returns to helpfulness.
 Experience Goods somewhat deviates from the results of Search Goods.
@@
 Additionally, Perceived Helpfulness has higher responsiveness to Review Length when a review has a low rating.
-This means that people focus more on negative cues than positive cues because the marginal value of additional negative information is higher.
+This means that people focus more on negative cues than positive cues because the marginal value of an additional negative information is higher.
 This way consumers are able to cut down potential sure losses.
@@
 The differences are not limited to Review Rating.
-The usages the dependent variable, Perceived Helpfulness, diverged as well.
+The way the dependent variable was used, Perceived Helpfulness, diverged too.
 In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression.
@@
 This collective behavior may even impact social welfare positively since economic agents are making much more informed decisions.
-Unfortunately, similar implications can not be made for experience goods, specifically for movies, since the realized results were mostly different that what was hypothesized.
+Unfortunately, similar implications can not be made for experience goods, specifically for movies, since the realized results were mostly different than what was hypothesized.
 Thus, this study can not offer any suggestions for movie reviews.
@@
 Firstly, aside from lexicon based sentiment analysis it is also possible to utilize deep learning methods to mine opinions from a text.
-One advantage of deep learning method over a lexicon is its versatility.
+One advantage of the deep learning method over a lexicon is its versatility.
 A negative word can change from one context to another and training a deep learning method is more robust to this type of contextual changes whereas with lexicon based methods a negative word is a negative word no matter the context is.

### 2022-12-27 Paper.Rmd
little fixes after aprpoval

@@
 
+The existence of the Negativity Bias and how the potential effects of Negativity Bias on Review Helpfulness could be moderated by either Search And Experience goods will be the main focus of this study.
+A lesser degree of Negativity Bias is expected for Experience Goods.
+Additionally, the amount of information that a review has and its connection to Review Helpfulness with respect to Review Ratings will be analyzed.
+Next, the diagnostic values of the negative and positive sentiments are going to be discussed.
+Because of the Negativity Bias, a positive relationship between Negative Sentiments and Review Helpfulness is expected.
+Lastly, the relationship between the Review Helpfulness and the timeline of a review will be inquired.
+
 This study uses secondary data.
@@
 
-## Negativity Bias Theorem and Loss Aversion
-
-Negativity Bias Theorem argues that humans or even animals have tendencies to be more aware of negative entities than positive ones.
+## Negativity Bias and Loss Aversion
+
+Negativity Bias argues that humans or even animals have tendencies to be more aware of negative entities than positive ones.
 In @rozin2001's words Negativity Bias can be best exemplified such as the following:
@@
 
-@rozin2001 explains the Negativity Bias Theorem by describing it with four main aspects.
+@rozin2001 explains the Negativity Bias by describing it with four main aspects.
 Namely, Negative Potency, Steeper Negative Gradients, Negative Dominance and Negative Differentiation [@rozin2001; @sen2007; @eslami2018].
-Loss Aversion has a strong connection to Negativity Bias Theorem since negative cues might be used as an early warning against potential losses [@herr1991].
+Loss Aversion has a strong connection to Negativity Bias since negative cues might be used as an early warning against potential losses [@herr1991].
 
@@
 On Figure \@ref(fig:Search-Neg) (A) and Figure \@ref(fig:Experience-Neg) (A) the distributions of the variable for both good types can be seen.
-On plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words.
+On logarithmic transformed plots, X-axis labels were given in the logarithm of base 10 so 1.00 on the X-axis implies that 10% of the review was negative words.
 For example in this case the mean negative proportion rate is 2,3% ($10^{0.37}$) for search goods and 3,7% ($10^{0.57}$) for experience goods.
@@
 
-On Figure \@ref(fig:Search-Neg) (B), non-linear relationship between perceived helpfulness and the proportion of negative words can be observed for search goods.
+On Figure \@ref(fig:Search-Neg) (D), non-linear relationship between perceived helpfulness and the logarithm of the proportion of negative words can be observed for search goods.
 This might suggest that too much negative information might fall into slander rather than informing the customer about the potential risks of the product.
-On the other hand, somewhat weak negative linear relationship between perceived helpfulness and proportion of negative words can be seen for experience goods on Figure \@ref(fig:Experience-Neg) (B).
-
-```{r Search-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Search Goods"}
+On the other hand, somewhat weak negative linear relationship between perceived helpfulness and proportion of negative words can be seen for experience goods on Figure \@ref(fig:Experience-Neg) (D).
+
+```{r Search-Neg, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Proportion of Negative Words for Search Goods and their respective logaritmic transformations (B), (D)"}
 p1 <- search_goods %>% 
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Count", x = "Log10(Proportion of Negative Words)")
+
+p3 <- search_goods %>% 
+  mutate(negative = 10^(negative)) %>% 
+  ggplot(aes(negative))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(negative)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = 10^mean(search_goods$negative), y = Inf, 
+           label = paste("Mean:", round(10^mean(search_goods$negative), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
+  scale_x_continuous()+
+  labs(y = "Count", x = "Proportion of Negative Words")
 
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")
 
-plots <- p1 + p2
+p4 <- search_goods %>% 
+  mutate(negative = 10^negative) %>% 
+  ggplot(aes(negative, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous()+
+  coord_cartesian(ylim = c(-0.1,1))+
+  labs(y = "Helpfulness", x = "Proportion of Negative Words")
+
+plots <- (p3 + p1) / (p4 + p2)
 
@@
 
-```{r Experience-Neg, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Negative Words for Experience Goods"}
+```{r Experience-Neg, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Proportion of Negative Words for Experience Goods and their respective logarithmic transformations (B), (D)"}
 p1 <- movies_data %>% 
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Count", x = "Log10(Proportion of Negative Words)")
+
+p3 <- movies_data %>% 
+  mutate(negative = 10^negative) %>% 
+  ggplot(aes(negative))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(negative)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = 10^mean(movies_data$negative), y = Inf, 
+           label = paste("Mean:", round(10^mean(movies_data$negative), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
+  scale_x_continuous()+
+  labs(y = "Count", x = "Proportion of Negative Words")
 
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Helpfulness", x = "Log10(Proportion of Negative Words)")
 
-plots <- p1 + p2
+p4 <- movies_data %>% 
+  mutate(negative = 10^negative) %>% 
+  ggplot(aes(negative, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous()+
+  labs(y = "Helpfulness", x = "Proportion of Negative Words")
+
+plots <- (p3 + p1) / (p4 + p2)
 
@@
 Mean proportion values are 4,4% ($10^{0.64}$) and 5,2% ($10^{0.72}$) for search and experience goods respectively.
-Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (A) and Figure \@ref(fig:Experience-Pos) (A)).
+Except for zero values both distributions are looking quite normal (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)).
 
@@
 
-On scatter plots (see Figure \@ref(fig:Search-Pos) (B) and Figure \@ref(fig:Experience-Pos) (B)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts.
+On scatter plots (see Figure \@ref(fig:Search-Pos) (D) and Figure \@ref(fig:Experience-Pos) (D)), relationships between perceived helpfulness and proportion of positive words are looking very similar to their negative counterparts.
 Furthermore, these plots are kind of similar to perceived helpfulness versus number of words plots (see Figure \@ref(fig:Search-Length) (B) and Figure \@ref(fig:Experience-Length) (B)).
@@
 
-```{r Search-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Search Goods"}
+```{r Search-Pos, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Proportion of Positive Words for Search Goods and their respective logarithmic tansformations(B), (D)"}
 p1 <- search_goods %>% 
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Count", x = "Log10(Proportion of Positive Words)")
+
+p3 <- search_goods %>% 
+  mutate(positive = 10^positive) %>% 
+  ggplot(aes(positive))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(positive)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = 10^mean(search_goods$positive), y = Inf, 
+           label = paste("Mean:", round(10^mean(search_goods$positive), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
+  scale_x_continuous()+
+  labs(y = "Count", x = "Proportion of Positive Words")
 
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")
 
-plots <- p1 + p2
+p4 <- search_goods %>% 
+  mutate(positive = 10^positive) %>% 
+  ggplot(aes(positive, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous()+
+  coord_cartesian(ylim = c(0,1))+
+  labs(y = "Helpfulness", x = "Proportion of Positive Words")
+
+plots <- (p3 + p1) / (p4 + p2)
 
@@
 
-```{r Experience-Pos, fig.cap="The Distribution(A) and the Scatter Plot(B) of Proportion of Positive Words for Experience Goods"}
+```{r Experience-Pos, fig.height=6, fig.cap="The Distribution(A) and the Scatter Plot(C) of Proportion of Positive Words for Experience Goods and their respective logarithmic transformations (B),(D)"}
 p1 <- movies_data %>% 
@@
            vjust = 1, hjust = 0, size = 4.5)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Count", x = "Log10(Proportion of Positive Words)")
+
+p3 <- movies_data %>% 
+  mutate(positive = 10^positive) %>% 
+  ggplot(aes(positive))+
+  geom_histogram(color = "white", fill = "steelblue", boundary = 0)+
+  geom_vline(aes(xintercept = mean(positive)), size = 1, alpha = 0.6)+
+  annotate(geom = "label", x = 10^mean(movies_data$positive), y = Inf, 
+           label = paste("Mean:", round(10^mean(movies_data$positive), digits = 2)),
+           vjust = 1, hjust = 0, size = 4.5)+
+  scale_x_continuous()+
+  labs(y = "Count", x = "Proportion of Positive Words")
 
@@
   geom_smooth(color = "steelblue", size = 1.7)+
-  scale_x_continuous(n.breaks = 8)+
+  scale_x_continuous()+
   labs(y = "Helpfulness", x = "Log10(Proportion of Positive Words)")
 
-plots <- p1 + p2
+p4 <- movies_data %>% 
+  mutate(positive = 10^positive) %>% 
+  ggplot(aes(positive, Helpfulness))+
+  geom_point(alpha = 0.1)+
+  geom_smooth(color = "steelblue", size = 1.7)+
+  scale_x_continuous()+
+  labs(y = "Helpfulness", x = "Proportion of Positive Words")
+
+plots <- (p3 + p1) / (p4 + p2)
 
@@
 
-As it was mentioned in Section \@ref(negativity-bias-theorem-and-loss-aversion), people tend to try to minimize their losses.
+As it was mentioned in Section \@ref(negativity-bias-and-loss-aversion), people tend to try to minimize their losses.
 Because of this, negative cues draw more attention than positive ones since negative cues may imply potential losses.
@@
 
-Negativity Bias Theorem and Prospect Theory had a strong support in the case of search goods.
+Negativity Bias and Prospect Theory had a strong support in the case of search goods.
 The regression results showed that the reviews which had low ratings and/or reviews which had more negative words in them were found to be more helpful on the average.
@@
 Online Consumer Reviews data were collected from two different sources (IMDB and BestBuy) and analyzed within the context of consumer uncertainty in this study.
-Negativity Bias Theorem, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer.
+Negativity Bias, Prospect Theory and Search / Experience goods paradigm from information economics were used as theoretical engines to explain the information gathering process of an average consumer.
 Results showed similarities from the existing Review Helpfulness literature.
@@
 This study contributes to the literature as an additional empirical work with a unique BestBuy review data and a unique combination of movie reviews from IMDB.
-In addition, to my knowledge, this is the first study which analyzed the linear continuous interaction between the Review Length and the Review Rating in terms of Negativity Bias Theorem.
+In addition, to my knowledge, this is the first study which analyzed the linear continuous interaction between the Review Length and the Review Rating in terms of Negativity Bias.
 Additionally, there is a lack of emphasis on the sentiment analysis in the existing literature.

### 2022-12-29 Paper.Rmd
i am hoping this is the last

@@
 Because of the Negativity Bias, a positive relationship between Negative Sentiments and Review Helpfulness is expected.
-Lastly, the relationship between the Review Helpfulness and the timeline of a review will be inquired.
+Lastly, the positive relationship between the Review Helpfulness and the timeline of a review will be inquired because an updated and new information might be more helpful than an old information.
 
@@
 
-***H5**: There is a positive relationship between the Proportion of Negative Words and the Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*\
+***H5**: There is a positive relationship between the Proportion of Negative Words and the Perceived Helpfulness. This effect is stronger / weaker for Search/Experience goods.*
+
+@kuan2015 discussed that since the majority of the reviews are positive these positive reviews lose their diagnostic values for a given product.
+Compared to negative information which may lay out potential risks for the product in a much more objective sense, positive information might be found more subjective and lay out a more ambiguous information about the product which may confuse potential consumers.
+Therefore, it is hypothesized that:
+
+\
 ***H6**: There is a negative relationship between the Proportion of Positive Words and the Perceived Helpfulness for both product types.*
@@
 Tobit regression results are presented at Table \@ref(tab:Reg-Results-Tobit) alongside with OLS results as a benchmark at Table \@ref(tab:Reg-Results-OLS) [@mudambi2010; @kuan2015; @choi2020].
+Both Tobit regression results and OLS results have the same signs and significances which might indicate that the results are somewhat robust.
+For Search goods, the magnitudes of the coefficients are usually higher .
+This is quite expected since Search good data has more censored observations compared to Experience goods data.
 

### 2023-01-31 Paper.Rmd
jury adjustments completed

@@
 
+Readers may be curious about the existence of negation words such as "not", "no", etc..
+Additionally, reviewers might also be sarcastic when writing their reviews and they might say thing like "This product was so good that I could not believe it!".
+@Tidytext discusses that both negation and sarcasm were used in a lesser degree in the English language.
+Therefore, given the enough sample size non-negated words and non-sarcastic use of the language get dominated by the normal use of the words.
+
 ### Control Variables
